### 2015-05-25 paper.tex
Uploading the initial files to github repository

\documentclass[11pt,twoside]{rmta2010esp}% For English, use rmta2010eng.cls instead of rmta2010esp.cls
%\pagestyle{myheadings} 
\usepackage[english, spanish]{babel}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc} % En caso de usar tildes, ñ y otros caracteres especiales

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
\fancyhead[LO]{{\sc combining neural networks and geostatistics for landslide hazard assessment of san salvador department, el salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de página, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}

\DeclareGraphicsExtensions{.bmp,.png,.pdf,.jpg,.eps}

\renewcommand{\refname}{References}

\begin{document}

\selectlanguage{spanish}
\title{Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Department, El Salvador 
\newline
\newline
Combinando redes neuronales y geoestadística para evaluación de deslizamientos de tierra en San Salvador,Departamento de El Salvador}

\author[1]{Ricardo Ríos \thanks{ricardo.rios.sv@gmail.com}}
\author[2]{Carlos Gámez \thanks{gamez9e@yahoo.com}}
\affil[1]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
\affil[2]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}

\maketitle

\selectlanguage{spanish}
\begin{resumen}
Esta contribución describe como se obtuvo un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador. El análisis inicio con la obtención de una foto área del SNET-MARN con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento. En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica. Redes Neuronales Artificiales(RNA) fueron usadas para la evaluación de la susceptibilidad a deslizamiento de tierra, logrando que más del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo. Regresión Logística fue usada como base de comparación, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificación abajo del 70\%. Para completar el análisis se realizo la interpolación de puntos usando el método krigging proveniente del enfoque geoestadístico. Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y técnicas geoestadísticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
\end{resumen}

\PC deslizamiento de tierra, evaluación de riesgo, San Salvador, El Salvador, RNA, geoestadística.

\begin{abstract}
This contribution describes how we obtained a landslide hazard
assessment model for San Salvador, department in El Salvador. The analysis started with an aerial photointerpretation from  SNET-MARN ((Servicio Nacional de Estudios Territoriales - Ministerio de Medio Ambiente y Recursos Naturales)  with a total amount of 939407 georeferenced points to produce a landslide inventory. In this
landslide assessment we have used 4792 events previously photo-interpretaded
and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance. Artificial
Neural Networks (ANNs) were applied for the assessment of susceptibility to
landslides, achieving more than 80\% of landslide were properly classified using
in-sample and out of sample criteria. Logistic regression was used as base of
comparison, obtaining this model a performance lower than ANNs with a percentage of correct classification under 70\%. To complete the analysis we have
performed interpolation of the points using kriging method from geostatistical
approach. Finally, the results show that is possible to derive a landslide hazard map, making use of a combination of ANNs and geostatistical techniques
wherewith the present study can help landslide mitigation in El Salvador.
\end{abstract}

\KW landslide, hazard assessment, San Salvador, El Salvador, ANN, geostatistics.

\AMS 62P12.% Mathematical Subject Classification, http://www.ams.org/mathscinet/msc/msc2010.html.

\selectlanguage{english}

\section{Introduction}
\label{sec:intr}
El Salvador, one of the smallest and most crowded nations in Central America, extends about 240 kilometers westward from the 
Gulf of Fonseca to the border with Guatemala. This country is very vulnerable to landslide due to social, political and economic factors.
In the year of 2001, El Salvador was struck by two devastating earthquakes within a month. One of the most spectacular aspects featuring 
heavily in the first earthquake was the damage inflicted by landslides. Among them, Las Colinas landslide was the most tragic.
A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of a mountain ridge rising south behind Las Colinas area 
of Nueva San Salvador (Santa Tecla), and flushed many houses and therefore more than 500 lives to death.

Due to the above it is necessary to implement mechanisms that allow us to quantify the hazard of a given
geographic area to landslides, usually this is done with development of susceptibility maps which present in a graphical way
the zones more susceptible to landslides and represent a practical tool for urban planning.

%% write about how to perform your neural network and geostatistic analysis

%The data was collected from aerial images, topographical and geologic maps which provide a base for  the application of landslide susceptibility methodologies and the development of geostatistics models. From aerial photographs, different regions of landslide occurrences were classified. The topographical and geologic maps provided information about causal factors. 
%
%
%Artificial neural networks (ANNs) are computational models inspired by biology (in particular the brain) that are capable of machine learning and pattern recognition. They are usually presented as systems of interconnected ``neurons'' that can compute values from inputs by feeding information through the network (\citet{wiki:001}). Recently ANNs have been applied successfully to the assessment of landslide susceptibility. 
%
In this paper we propose an ANN model which enable to estimate the susceptibility to landslide in the georeferenced points belong to the Metropolitan Area of San Salvador (MASS) and later a map of susceptibility was generated by means of kriging method from geostatistical.

%\citet{Melchiorre2011410} determined landslide susceptibility for the Guantanamo Province %in Cuba by using ANN models.

%%% I must citet the paper of Enrique Castellanos

\section{Brief State of Art}
\label{sec:brief}
Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} )
%, fuzzy set theory (\citet{Kanungo2006347} and \citet{Guettouche20133163}) 
and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374} and \cite{Ermini2005327}).

Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.

\section{Landslide inventory and data sources of input variables}
\label{sec:landsinvet}
The Landslide inventory was developed from photographic analysis on the study area, using 
aerial photo from SNET-MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.

 \begin{center}
  \begin{figure}[H]
   \centering
   \includegraphics[scale=0.40]{img01}
   \caption{\small{Aerial photo of MASS}}
   \label{fig:img01}
  \end{figure}
 \end{center}

Once that the white areas were georeferenced, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence. In addition to the landslide information the following data sources of input variables was given by SNET-MARN: 
\begin{enumerate}
\item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.

\item {\bf Slope:} derived from digital elevation model MARN-SNET

\item {\bf Geology:} Description of the geology of the area from the map German Geological Mission (scale 1:100,000).

\item {\bf Rainfall intensity:} Maximum rainfall recorded in the geographical area.

\item {\bf Peak ground accelaration:} Maximum ground acceleration expressed in Gal for a return period of 500 years, this is the least that has detailed information. This information was obtained from RSIS II project.

\item {\bf Road distance:} Distance in kilometers to the nearest road.

\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from German Geological Mission (scale 1:100,000).

\end{enumerate}

%%% We must comment page 12 - 14 from my Master Thesis 
%%% Valorizar si lo de Redes Neuronales y Predicción Espacial lo ponemos en métodos y materiales

\section{Artificial Neural Network model for discrete choice}
The logistic regression is a special case of neural network whose output variable is
discrete, logistic regression represents a neural network with 
a neuron in the hidden layer. The following adaptation of a multilayeredfeedforward artificial neural network known as  
MLP (Multilayer Perceptron) may be used for modeling binary classification model, where $x's$ are the observed values in the input variables, $w's$ and $\lambda's$ are the parameters of the model, $ p_{i} $ is the predicting probability for a network with $ k^{*} $ input characteristics and $ j^{*} $ neurons:

\begin{equation}
n_{j,i} = w_{j,0} + \sum_{k=1}^{k^{*}} w_{j,k}x_{k,i}
\end{equation}

\begin{equation}
N_{j,i} = \frac{1}{1+\exp^{-n_{j,i}}}
\end{equation}

\begin{equation}
p_{i} = \sum_{j=1}^{j^{*}} \lambda_{j} N_{j,i}
\end{equation}

\begin{equation}
\sum_{j=1}^{j^{*}} \lambda_{j} = 1 , \lambda_{j} \ge 0
\end{equation}

In the context of the research problem $p_{i} $ and the number $ k^{*} $ represent 
probability of landslide ocurrence and the number of input variables or causes associated with landslide ocurrence respectively.

The method used for estimating the parameters of the model was an Hybrid Method: First of all Genetic Algorithms were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied again to obtain a new local minimun.

\section{Spatial Prediction}
In standard statistical problems, correlation can be estimated from a scatterplot, when several data pairs ${x, y}$ are available. The spatial correlation between two observations of a variable $z(s)$ at locations $s_{1}$ and $s_{2}$ cannot be estimated, as only a single pair is available. To estimate spatial correlation
from observational data, we therefore need to make stationarity assumptions
before we can make any progress. One commonly used form of stationarity
is intrinsic stationarity, which assumes that the process that generated the
samples is a random function $Z(s)$ composed of a mean and residual:

\begin{equation}
Z(s) = \mu + \delta(s)
\end{equation}

with a constant mean

\begin{equation}
E\left(Z(s)\right) = \mu
\end{equation}

and a variogram defined as

\begin{equation}
\lambda(h) = \frac{1}{2}E\left(Z(s) - Z(s+h)\right)^{2}
\end{equation}

\subsection*{Ordinary kriging in terms of the covariance function}
The predictor assumption is 
\begin{equation}
\hat{Z(s_{0})} = \sum_{i=1}^{n} w_{i}Z(s_{i})
\end{equation}

It is a weighted average of the sample values, and $ \sum_{i=1}^{n} w_{i} = 1 $ to ensure unbiasedness. The $w_{i}$'s are the weights that will be estimated.

Kriging minimizes the mean squared error of prediction

\begin{equation}
min \ \sigma_{e}^{2} = E\left[Z(s_{0}) - \hat{Z(s_{0})}\right]^{2}
\end{equation}

\section{Results}
%\subsection*{Data Partition}
The data were randomly divided into three sub-samples, the first was used for the
estimation of the parameters of the neural network (training set), the second was used for
choosing the model with more generalization capability (validation set) and the last was
used to evaluate how well the model generalize outside of the data set used for estimation (test set).

To determine the number of neurons in the hidden layer was used the method of trial and error, starting with few neurons and increasing progressively the number of neurons in the hidden layer. Table \ref{annresults}
summarizes how well the models fit on the training, validation and test sets.

\begin{table}[H]
\caption{Summary of classification accuracy on the training, validation and test sets for neural network models  }
\label{annresults}
\centering
\begin{tabular}{ | c | c | c | c | }
\hline
\multicolumn{4}{| c |}{Percentage score} \\
\hline
Número de neuronas &    Train set    &   Validation set &  Test set \\
\hline
2  &  0.7011 & 0.7020 & 0.7124 \\
\hline
3 &  0.7206 & 0.7072 & 0.7401 \\
\hline 
4 &  0.7425 & 0.7197 & 0.7458 \\
\hline
5 &  0.7601 & 0.7604 & 0.7740 \\
\hline
6 &  0.7823 & 0.7704 & 0.7604 \\
\hline
7 &  0.7853  & 0.7704 &  0.7763 \\
\hline
8 &  0.7942 & 0.7865 & 0.7878  \\
\hline
9 & 0.8009 & 0.7871 & 0.7901  \\
\hline
10 & 0.8321 & 0.8132 & 0.8009  \\
\hline
11 & 0.8194 & 0.7792 & 0.7542 \\
\hline
12  &  0.8230 & 0.8006 & 0.8159 \\
\hline
13 & 0.8408 &  0.8006 & 0.8031 \\
\hline
14  &  0.8373 & 0.8017 & 0.8127 \\
\hline
15 &  0.8517 & 0.8210 & 0.8247 \\ 
\hline
16  &  0.8246 & 0.8017 & 0.8028 \\ 
\hline
17  &  0.8543 & 0.8283 & 0.8246 \\ 
\hline
18   &  0.8467 & 0.8022 & 0.8418 \\ 
\hline
19  &  0.8341  & 0.7991 & 0.8274 \\
\hline
\end{tabular}
\end{table}

The model with 17 neurons in the hidden layer was chosen, after that a logistic regression model was fitted as a basis of comparison. Table \ref{logisticresults} presents the logistic regression fits, clearly the logistic regression's performance was lower than the worst neural network model.

\begin{table}[H]
\caption{Summary of classification accuracy on the training, validation and test sets for logistic regression}
\label{logisticresults}
\centering
\begin{tabular}{ | c | c | c | c | }
\hline
\multicolumn{4}{| c |}{Percentage score} \\
\hline
Model &    Train set    &   Validation set &  Test set \\
\hline
logistic regression  &  0.6710  & 0.6748   & 0.663 \\
\hline
\end{tabular}
\end{table}

To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging and validation of this results. 
First of all one thousand data were used for the map generation process leaving the others for validation of the model. The Exploratory analysis showed the presence of spatial correlation in the data, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect. As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it presented a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively. The map of landslide hazards is showed in the figure \ref{fig:img02}.

 \begin{center}
  \begin{figure}[H]
   \centering
   \includegraphics[scale=0.40]{img02}
   \caption{\small{Map of landslide hazards}}
   \label{fig:img02}
  \end{figure}
 \end{center}

\section{Discussion and conclusions}
A landslide hazard assessment study was carried out in Metropolitan Area of San Salvador (MASS). The study started with the construction of a landslide inventory and analysis of the causal factors related to the occurrences of landslide. The problem of modelling landslide generated by different causes is very complex and for this reason the study proved the efficacy of the neural network model with a percentage of correct classification around 80\% against other models such as logistic regression with a percentage of correct classification under 70\%.

In the process of estimating the weights of the model an heuristic technique was used to obtain a better solution after that a local search was used. It is better than use only backpropagation algorithm or another local search method to estimate weights since that when these are used there is a strong danger of getting stuck in a local minimum rather than a global minimum for a vector of weights.

The problem with the neural network approach is that is difficult to estimate the weights of the model due to intensive computation involved in the present study the estimation of a neural network model takes between 4 and 10 hours for this reason we could not assess the statistical significance of the input variables in the neural network processes using boostrapping. For all of the above parallel computing must be used rather than serial computing in estimating weights of neural networks models.

The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying krigin method. The map of landslide hazard \ref{fig:img02} was generated by krigin method and can be used by non-experts in the landslide phenomenon for many purposes such as territorial planning, prevention and mitigation of natural dissasters and so on.

Other important variables could not be obtained such as landslide types (Rockfalls, Topples, Slides, etc) and temporal information which can improve the predictive ability of the model.

\section{Acknowledgment}   
The authors are indebted to M.SC. Giovanni Molina from SNET who provided the data and useful information about landslide modelling techniques.

\begin{thebibliography}{99}

%\bibitem[Carrara(1983)]{Carrara1983403}
\bibitem{Carrara1983403}
Alberto Carrara.
\newblock Multivariate models for landslide hazard evaluation.
\newblock \emph{Journal of the International Association for Mathematical
  Geology}, 15\penalty0 (3):\penalty0 403--426, 1983.
\newblock ISSN 0020-5958.
%\newblock \doi{10.1007/BF01031290}.
\newblock URL \url{http://dx.doi.org/10.1007/BF01031290}.

%\bibitem[Capparelli and P.~Versace(2013)]{hessd-10-12643-2013}
\bibitem{hessd-10-12643-2013}
G.~Capparelli and P.~P.~Versace.
\newblock Landslide susceptibility from mathematical model in sarno area.
\newblock \emph{Hydrology and Earth System Sciences Discussions}, 10\penalty0
  (10):\penalty0 12643--12662, 2013.
%\newblock \doi{10.5194/hessd-10-12643-2013}.
\newblock URL
  \url{http://www.hydrol-earth-syst-sci-discuss.net/10/12643/2013/}.

%\bibitem[Pradhan et~al.(2010)Pradhan, Oh, and
%  Buchroithner]{doi:10.1080/19475705.2010.498151}
\bibitem{doi:10.1080/19475705.2010.498151}
Biswajeet Pradhan, Hyun-Joo Oh, and Manfred Buchroithner.
\newblock Weights-of-evidence model applied to landslide susceptibility mapping
  in a tropical hilly area.
\newblock \emph{Geomatics, Natural Hazards and Risk}, 1\penalty0 (3):\penalty0
  199--223, 2010.
%\newblock \doi{10.1080/19475705.2010.498151}.
\newblock URL
  \url{http://www.tandfonline.com/doi/abs/10.1080/19475705.2010.498151}.

%\bibitem[Neuhäuser et~al.(2012)Neuhäuser, Damm, and Terhorst]{Neu2012511}
\bibitem{Neu2012511}
Bettina Neuhäuser, Bodo Damm, and Birgit Terhorst.
\newblock Gis-based assessment of landslide susceptibility on the base of the
  weights-of-evidence model.
\newblock \emph{Landslides}, 9\penalty0 (4):\penalty0 511--528, 2012.
\newblock ISSN 1612-510X.
%\newblock \doi{10.1007/s10346-011-0305-5}.
\newblock URL \url{http://dx.doi.org/10.1007/s10346-011-0305-5}.

%\bibitem[Bernknopf and Shapiro(1988)]{Bern198839}
\bibitem{Bern198839}
Campbell R.H. Brookshire~D.S. Bernknopf, R.L. and C.D Shapiro.
\newblock A probabilistic approach to landslide hazard mapping in cincinnati,
  ohio, with application for economic evaluation.
\newblock \emph{Bulletin of the Association of Engineering Geologists},
  XXV\penalty0 (1):\penalty0 39--56, 1988.

%\bibitem[Chung and Fabbri(2003)]{Chung2003451}
\bibitem{Chung2003451}
Chang-JoF. Chung and AndreaG. Fabbri.
\newblock Validation of spatial prediction models for landslide hazard mapping.
\newblock \emph{Natural Hazards}, 30\penalty0 (3):\penalty0 451--472, 2003.
\newblock ISSN 0921-030X.
%\newblock \doi{10.1023/B:NHAZ.0000007172.62651.2b}.
\newblock URL \url{http://dx.doi.org/10.1023/B\%3ANHAZ.0000007172.62651.2b}.

%\bibitem[Lee et~al.(2004)Lee, Choi, and Min]{doi:10.1080/01431160310001618734}
\bibitem{doi:10.1080/01431160310001618734}
S.~Lee, J.~Choi, and K.~Min.
\newblock Probabilistic landslide hazard mapping using gis and remote sensing
  data at boun, korea.
\newblock \emph{International Journal of Remote Sensing}, 25\penalty0
  (11):\penalty0 2037--2052, 2004.
%\newblock \doi{10.1080/01431160310001618734}.
\newblock URL
  \url{http://www.tandfonline.com/doi/abs/10.1080/01431160310001618734}.

%\bibitem[Melchiorre et~al.(2011)Melchiorre, Abella, van Westen, and
%  Matteucci]{Melchiorre2011410}
\bibitem{Melchiorre2011410}
C.~Melchiorre, E.A.~Castellanos Abella, C.J. van Westen, and M.~Matteucci.
\newblock Evaluation of prediction capability, robustness, and sensitivity in
  non-linear landslide susceptibility models, guantánamo, cuba.
\newblock \emph{Computers {\&} Geosciences}, 37\penalty0 (4):\penalty0 410 --
  425, 2011.
\newblock ISSN 0098-3004.
%\newblock \doi{http://dx.doi.org/10.1016/j.cageo.2010.10.004}.
\newblock URL
  \url{http://www.sciencedirect.com/science/article/pii/S0098300410003286}.

%\bibitem[Zeng-wang(2001)]{Zeng2001374}
\bibitem{Zeng2001374}
Xu~Zeng-wang.
\newblock Gis and ann model for landslide susceptibility mapping.
\newblock \emph{Journal of Geographical Sciences}, 11\penalty0 (3):\penalty0
  374--381, 2001.
\newblock ISSN 1009-637X.
%\newblock \doi{10.1007/BF02892323}.
\newblock URL \url{http://dx.doi.org/10.1007/BF02892323}.

%\bibitem[Erm(2005)]{Ermini2005327}
\bibitem{Ermini2005327}
Artificial neural networks applied to landslide susceptibility assessment.
\newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.

\end{thebibliography}

\end{document}

### 2015-05-25 paper.tex

@@
 and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374} and \cite{Ermini2005327}).
+
+There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})
 
@@
 
+\bibitem{Yesilnacar2005251}
+E. Yesilnacar and T. Topal.
+\newblock Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey).
+\newblock \emph{Engineering Geology}, 79\penalty0
+  (11):\penalty0 251-266, 2005.
+\newblock ISSN 0013-7952,
+%\newblock \doi{10.1080/01431160310001618734}.
+\newblock URL
+  \url{http://www.sciencedirect.com/science/article/pii/S0013795205000384}.
+
 \end{thebibliography}

### 2015-05-31 paper.tex
Update paper.tex
31 may 2015 9:30

@@
 \fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
-\fancyhead[LO]{{\sc combining neural networks and geostatistics for landslide hazard assessment of san salvador department, el salvador } \hfill \thepage}
+\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
 \fancyfoot{}
@@
 \selectlanguage{spanish}
-\title{Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Department, El Salvador 
+\title{Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador 
 \newline
 \newline
-Combinando redes neuronales y geoestadística para evaluación de deslizamientos de tierra en San Salvador,Departamento de El Salvador}
+Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador}
 
-\author[1]{Ricardo Ríos \thanks{ricardo.rios.sv@gmail.com}}
-\author[2]{Carlos Gámez \thanks{gamez9e@yahoo.com}}
-\affil[1]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
-\affil[2]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
+\author[1]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com }}
+\author[2]{Giovanni Molina \thanks{giova.molina@gmail.com}}
+\author[3]{Ricardo Ríos \thanks{ricardo.sv@gmail.com}}
+
+\affil[1]{National Institute of Health, Ministry of Health of El Salvador, El Salvador.}
+\affil[2]{Ministry of Environment and Natural Resources of El Salvador.}
+\affil[3]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
 
@@
 \label{sec:brief}
-Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} )
+Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
+
+According to
+
+Recently 
 %, fuzzy set theory (\citet{Kanungo2006347} and \citet{Guettouche20133163}) 
-and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374} and \cite{Ermini2005327}).
+and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251}.
 
-There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})
+%There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})
 
-Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
+%Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
 

### 2015-05-31 paper.tex
31 May 2015 9:50
31 May 2014 11:30

@@
 \fancyhead{}
-\fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
+\fancyhead[RE]{\thepage \hfill {\sc a. rib\'{o} -- g. molina -- r. r\'{i}os  }}
 \fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
@@
 \fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
-\paginas{1}{10} % Numeros de página, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
+\paginas{1}{10} % Numeros de pgina, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
 \usepackage{amsmath}
@@
 
+%\newpage
+
 \selectlanguage{spanish}
@@
 Esta contribución describe como se obtuvo un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador.
-El análisis inicio con la obtención de una foto área del SNET-MARN con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
+El análisis inicio con la obtención de una foto área del MARN () con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
 En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica.
@@
 
-\PC deslizamiento de tierra, evaluación de riesgo, San Salvador, El Salvador, RNA, geoestadística.
+\PC deslizamiento de tierra, evaluación de riesgo, El Salvador, RNA, geoestadística.
 
@@
 assessment model for San Salvador, department in El Salvador.
-The analysis started with an aerial photointerpretation from  SNET-MARN ((Servicio Nacional de Estudios Territoriales - Ministerio de Medio Ambiente y Recursos Naturales)  with a total amount of 939407 georeferenced points to produce a landslide inventory.
+The analysis started with an aerial photointerpretation from  MARN (Ministry of Environment and Natural Resources of El Salvador)  with a total amount of 939407 georeferenced points to produce a landslide inventory.
 In this
@@
 
-\KW landslide, hazard assessment, San Salvador, El Salvador, ANN, geostatistics.
+\KW landslide, hazard assessment, El Salvador, ANN, geostatistics.
 
@@
 The Landslide inventory was developed from photographic analysis on the study area, using 
-aerial photo from SNET-MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
+aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
 
@@
 Once that the white areas were georeferenced, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence.
-In addition to the landslide information the following data sources of input variables was given by SNET-MARN:
+In addition to the landslide information the following data sources of input variables was given by MARN:
 \begin{enumerate}
@@
 
-\item {\bf Slope:} derived from digital elevation model MARN-SNET
+\item {\bf Slope:} derived from digital elevation model MARN
 
@@
 
-The method used for estimating the parameters of the model was an Hybrid Method: First of all Genetic Algorithms were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied again to obtain a new local minimun.
+The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software specifically developed for this purpose, was used to obtain
+a good estimation of the parameters of the model.
+
+The R package can be accessed from the following web address:
+
+ were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied on the previous  to obtain a new local minimun.
 
@@
 \section{Acknowledgment}   
-The authors are indebted to M.SC. Giovanni Molina from SNET who provided the data and useful information about landslide modelling techniques.
+The authors are indebted to M.SC. Giovanni Molina from MARN who provided the data and useful information about landslide modelling techniques.
 
@@
 \newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.
+\newblock ISSN 0169-555X
+%\newblock \doi{http://dx.doi.org/10.1016/j.geomorph.2004.09.025}.
+\newblock URL \url{http://www.sciencedirect.com/science/article/pii/S0169555X04002272}.
 
@@
 
+\bibitem{McNelis2005}
+Paul D. McNelis
+\newblock Estimation of a Network with Evolutionary Computation
+\newblock \emph{Academic Press},
+  (11):\penalty0 59-84, 2005.
+\newblock ISBN 9780124859678,
+%\newblock \doi{http://dx.doi.org/10.1016/B978-012485967-8.50003-8}.
+\newblock URL
+  \url{http://www.sciencedirect.com/science/article/pii/B9780124859678500038}.
+
 \end{thebibliography}

### 2015-05-31 resources/neurogen/R/classnet.r
31 May 2015 11:45

@@ -1,0 +1,214 @@
+classnet<-function(assetx,coldep,percent,errpercent,errweight,limit,info,gendum=1,maxgen,helge=0,visual=TRUE, beta0init ) 
+{   
+
+   if (length(info)<3)
+   {
+      stop('El valor de info debe ser un arreglo conteniendo el numero de entradas, el numero de neuronas en la capa de salida y el numero de variables de salida.'); 
+   }
+   
+   if (gendum!=1) 
+   {
+      stop('El valor de gendum debe ser uno.'); 
+   }
+   
+   if ( helge!=0 && helge!=1 && helge!=2 )
+   {
+      stop('El valor de helge debe estar entre cero y dos.');    
+   }
+               
+   assign("nneuron1", info[2], envir= .NeurogenEvalEnv );   
+   nneuron1 <- get("nneuron1", envir= .NeurogenEvalEnv );      
+   assign("toler", errpercent, envir= .NeurogenEvalEnv );                  
+   assign("limit", limit, envir=.NeurogenEvalEnv );      
+   limit <- get("limit", envir=.NeurogenEvalEnv );                
+   
+   if (visual)
+   {
+      assign("INTERVISION", as.integer(1), envir=.NeurogenEvalEnv );         
+   }
+   
+   else 
+   {
+      assign("INTERVISION", as.integer(0), envir=.NeurogenEvalEnv );               
+   }
+         
+   popsize <- 100;          
+   rr <- nrow(assetx); 
+   cc <- ncol(assetx);            
+   y <- array(data=assetx[,coldep], dim=c(rr, 1));
+   
+   if (coldep==1)
+   {
+      x <- array(data=assetx[,2:cc], dim=c(rr,(cc-1))) ;         
+   }
+
+   else if (coldep==cc) 
+   {
+      x <- array(data=assetx[,1:(coldep-1)], dim=c(rr, cc-1));   
+   }
+            
+   else 
+   {
+      x <- cbind(assetx[,1:(coldep-1)], assetx[,(coldep+1):cc]);   
+   }
+                     
+   nrow <- nrow(x); 
+   ncol <- ncol(x);    
+   nrowy <- nrow(y); 
+   ncoly <- ncol(y);        
+   nrow1 <- round(percent * nrow);
+   nrow11 <- nrow1 + 1;             
+   rx <- nrow(x); 
+   cx <- ncol(x);
+   ry <- nrow(y); 
[…]

### 2015-05-31 resources/neurogen/R/classnetfun.r

@@ -1,0 +1,78 @@
+classnetfun<-function(beta) 
+{         
+   nneuron1 <- get("nneuron1", envir=.NeurogenEvalEnv );      
+   limit <- get("limit", envir= .NeurogenEvalEnv );             
+   P <- get("P", envir= .NeurogenEvalEnv );       
+   T <- get("T", envir=.NeurogenEvalEnv );             
+   
+   rp <- nrow(P); 
+   cp <- ncol(P);    
+   x <- P; 
+      
+   nn1 <- array(dim=c(rp,nneuron1));
+   nn2 <- array(dim=c(rp,nneuron1)); 
+     
+   for (j in 1:nneuron1)
+   {
+      nn1[ ,j] <- x %*% t( array( data=beta[(1+(j-1)*cp):(j*cp)], dim=c(1, (j*cp)-(1+(j-1)*cp)+1 ) ) ) + beta[nneuron1*cp+j];
+
+   }    
+
+   for (j in 1:nneuron1)
+   {
+      nn2[ ,j] <- 1 /(1 + exp(-nn1[,j]));  
+   }
+     
+   yhat <- ( nn2[ ,1:nneuron1] %*% t( array(data = beta[(nneuron1*cp+nneuron1+1):(nneuron1*cp+2*nneuron1)], dim=c(1,(nneuron1*cp+2*nneuron1)-(nneuron1*cp+nneuron1+1) + 1 ) ) ) );
+   yhat <- yhat +  beta[nneuron1*cp+2*nneuron1+1]   ;    
+   yhat <- 1 /(1 + exp(-yhat));        
+   TT <- T;
+   y <- T;
+   A3 <- yhat;
+   lik <- y * log(yhat) + (1-y) * log(1-yhat);
+   LIK3 <- -sum(lik);
+     
+   xmean = array(data=apply(P, 2, mean),  dim=c(1,cp) );  
+   BETA <- array(data=beta[(nneuron1*cp+nneuron1+1):(nneuron1*cp+2*nneuron1)], dim=c(1, (nneuron1*cp+2*nneuron1)-(nneuron1*cp+nneuron1+1)+1 ) );                                                                                                        
+   GAMMA <- array( data = beta[(1:(nneuron1*cp))], dim=c(1, ((nneuron1*cp)-1+1) ) ) ;
[…]

### 2015-05-31 resources/neurogen/R/gen.r

@@ -1,0 +1,7 @@
+gen<-function(beta0, popsize, maxgen)
+{      
+   returned_data = .Call('gen', beta0, as.integer(popsize), as.integer(maxgen), PACKAGE = "neurogen" );    
+
+   return(returned_data); 
+}
+

### 2015-05-31 resources/neurogen/R/predictclassnet.r

@@ -1,0 +1,49 @@
+predictclassnet<-function(assetx,info,helge,beta) 
+{   
+   nneuron1 <- info[2];         
+   rp <- nrow(assetx); 
+   cp <- ncol(assetx);      
+   x <- array(data=assetx, dim=c(rp,cp) ) ;
+   
+   if (helge$helge == 0) 
+   {
+      
+   } 
+   
+   if (helge$helge == 1) 
+   {   
+      for ( i in 1:cp ) 
+      {
+         x[,i] <-(x[,i]-(helge$minimos[,i]))/((helge$maximos[,i])-(helge$minimos[,i]));   
+      }               
+   } 
+      
+   if (helge$helge == 2) 
+   {     
+      for ( i in 1:cp ) 
+      {
+         x[,i] <- (x[,i] - (helge$medias[,i])) / (helge$desv[,i]);   
+      }                        
+   } 
+               
+   nn1 <- array(dim=c(rp,nneuron1));      
+   nn2 <- array(dim=c(rp,nneuron1)); 
+   
+   for (j in 1:nneuron1)
+   {
+      nn1[ ,j] <- x %*% t( array( data=beta[(1+(j-1)*cp):(j*cp)], dim=c(1, (j*cp)-(1+(j-1)*cp)+1 ) ) ) + beta[nneuron1*cp+j];
+   }    
+
+   for (j in 1:nneuron1)
+   {
+      nn2[ ,j] <- 1 /(1 + exp(-nn1[,j]));
+   }
+  
+   yhat <- ( nn2[ ,1:nneuron1] %*% t( array(data = beta[(nneuron1*cp+nneuron1+1):(nneuron1*cp+2*nneuron1)], dim=c(1,(nneuron1*cp+2*nneuron1)-(nneuron1*cp+nneuron1+1) + 1 ) ) ) );  
+   yhat <- yhat +  beta[nneuron1*cp+2*nneuron1+1]   ;    
+   yhat <- 1 /(1 + exp(-yhat));
+   A3 <- yhat;   
+            
+   return(list( PROB=A3));   
+}
+

### 2015-05-31 resources/neurogen/R/zzz.r

@@ -1,0 +1,36 @@
+.NeurogenEvalEnv <- new.env(); 
+assign("nneuron1", NULL, envir=.NeurogenEvalEnv);
+assign("limit", NULL, envir=.NeurogenEvalEnv);
+assign("P", NULL, envir=.NeurogenEvalEnv);
+assign("T", NULL, envir=.NeurogenEvalEnv);
+assign("toler", NULL, envir=.NeurogenEvalEnv);
+assign("INTERVISION", NULL, envir=.NeurogenEvalEnv);
+
+.onLoad <- function(lib, pkg)
+{
+    library.dynam( "neurogen", pkg, lib )    
+    environment(.NeurogenEvalEnv) <- asNamespace("neurogen")
+    .Call("R_initNeurogen", .NeurogenEvalEnv, PACKAGE="neurogen")
+    .neurogen.loaded <<- TRUE
+}
+
+.onUnload <- function(libpath)
+{
+    if (.neurogen.loaded) 
+    {
+        .Call("R_killNeurogen", PACKAGE="neurogen")
+    }
+    
+    library.dynam.unload("neurogen", libpath)
+}
+
+
+
+
+cat("Universidad de El Salvador ", "\n" ); 
+cat("Facultad de Ciencias Naturales y Matematica ", "\n" ); 
+cat("Escuela de Matematica ", "\n");
+cat("Paquete: Neurogen ", "\n"); 
+cat("Version: 1.0 ", "\n");  
+cat("Descripcion: Redes Neuronales con algoritmos geneticos ", "\n"); 
+cat("Licencia: GPL ", "\n"); 

### 2015-05-31 resources/neurogen/src/gen.c

@@ -1,0 +1,632 @@
+#include <R.h>
+#include <Rdefines.h>
+#include <Rinternals.h>
+#include <math.h> 
+
+typedef struct vector_struct
+{	   
+   float *www; 	
+   float sse;    
+}vector; 
+
+
+int quicksort(vector www[], vector tempwww, int ini,int fin, int nparm)
+{      
+   int _ini_,_fin_,pos,band;
+   int popsize;
+   int k; 
+        
+   popsize = fin;       
+   _ini_=ini;
+   _fin_=fin;
+   pos=ini;
+   band=1;
+                          
+   while (band==1)
+   {
+      band=0;
+            
+      while((www[pos].sse<=www[_fin_].sse)&&(pos!=_fin_))            
+      {
+         _fin_--;
+      }
+                  
+      if (pos!=_fin_)
+      {         
+         tempwww.sse = www[pos].sse; 
+
+         for (k=0; k<nparm; k++)
+            tempwww.www[k] = www[pos].www[k];                                               
+         
+         www[pos].sse = www[_fin_].sse; 
+         
+         for (k=0; k<nparm; k++)
+            www[pos].www[k] =  www[_fin_].www[k]; 
+                                                      
+         www[_fin_].sse = tempwww.sse; 
+         
+         for (k=0; k<nparm; k++)
+            www[_fin_].www[k] = tempwww.www[k]; 
+                           
+         pos=_fin_;
+         
+         while ( (www[pos].sse >= www[_ini_].sse)  &&(pos!=_ini_) )
+         {
+            _ini_++;
+         }
+         
+         
+         if(pos!=_ini_)
+         {
+            band=1;            
+            tempwww.sse = www[pos].sse; 
+
+            for (k=0; k<nparm; k++)
+               tempwww.www[k] = www[pos].www[k]; 
+                                                            
+            www[pos].sse = www[_fin_].sse; 
+         
+            for (k=0; k<nparm; k++)
+               www[pos].www[k] =  www[_fin_].www[k];             
+
+            www[_ini_].sse = tempwww.sse; 
+         
+            for (k=0; k<nparm; k++)
+               www[_ini_].www[k] = tempwww.www[k];                         
+            
+            pos=_ini_;
+         }
+                                         
+      }
+                                         
+   }
+         
+   
+   if ((pos-1)>ini)
+   {      
[…]

### 2015-05-31 resources/neurogen/src/neurogen.c

@@ -1,0 +1,14 @@
+#include "neurogen.h"
+
+SEXP R_initNeurogen(SEXP NeurogenEvalEnv) 
+{
+ 	
+    R_neurogenEvalEnv = NeurogenEvalEnv;
+
+    return R_NilValue;
+}
+
+SEXP R_killNeurogen() 
+{
+    return R_NilValue;
+}

### 2015-05-31 resources/neurogen/src/neurogen.h

@@ -1,0 +1,7 @@
+#include <Rinternals.h>
+#include <Rmath.h>
+
+SEXP R_neurogenEvalEnv;
+
+SEXP R_initNeurogen(SEXP NeurogenEvalEnv); 
+SEXP R_killNeurogen(); 

### 2015-05-31 resources/neurogen/src/register.c

@@ -1,0 +1,16 @@
+#include <R_ext/Rdynload.h>
+#include "neurogen.h"
+
+static const R_CallMethodDef callMethods[] = {
+    {"R_initNeurogen", (DL_FUNC) &R_initNeurogen, 1},
+    {"R_killNeurogen", (DL_FUNC) &R_killNeurogen, 0}, 
+    { NULL, NULL, 0 }    
+};
+
+
+void R_init_neurogen(DllInfo *dll) 
+{
+    R_useDynamicSymbols(dll, FALSE);              
+     
+    R_registerRoutines(dll, NULL, callMethods, NULL, NULL);
+}

### 2015-05-31 paper.tex
31 May 2014 12:00

@@
 \usepackage{authblk}
+\usepackage{hyperref}
 
@@
 
- were used to avoid getting stuck in a local rather than a global minimum of error function, after that a local search was applied on the previous  to obtain a new local minimun.
+\url{https://goo.gl/PHaaG2}
+
+Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim funcion of the R statistical software, to obtain a better estimation of the parameters of the model.
 

### 2015-05-31 paper.tex
31 May 2015 16:00

@@
 \begin{resumen}
-Esta contribución describe como se obtuvo un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador.
+Esta contribución describe la creación de un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador.
 El análisis inicio con la obtención de una foto área del MARN () con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
@@
 \begin{abstract}
-This contribution describes how we obtained a landslide hazard
+This contribution describes the creation of a landslide hazard
 assessment model for San Salvador, department in El Salvador.
@@
 
+Before estimating the parameters of the neural network model, it is necessary standardize the input variables.
+In particular for classification problems is more suitable to scale inputs to $[-1,1]$ rather than $[0,1]$ (\cite{FAQANN}).
+The following scaling was applied to each input variable:
+
+\begin{equation}
+x*_{k,i} = \frac{x_{k,i} - \mu }{\sigma}
+\end{equation}
+
+Where $ \mu $ and $\sigma$  is respectively the mean and the standard deviation for the ith input variable applied to the kth case.
+
 The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software specifically developed for this purpose, was used to obtain
@@
 \end{equation}
+
+In order to make spatial predictions using ordinary kriging, an R script was developed which can be accessed in the following web address:
 
@@
 To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging and validation of this results.
-First of all one thousand data were used for the map generation process leaving the others for validation of the model.
+
+In order to achieve the above steps a R scrit was developed which can be downloaded in the following address:
+
+First of all one thousand fifty georeferenced point with their probability of ocurrence which was calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the model.
 The Exploratory analysis showed the presence of spatial correlation in the data, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect.
-As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it presented a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
+
+As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it showed a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
+With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were imported to Geotiff raster format.
+
+% Falta poner que despues de pasarlo al geotiff se utilizo el software 
+% ILWIS o el que se tuvo que usar y que posteriormente se genero el 
+% map of landslide hazard mostrado en la figura
+
 The map of landslide hazards is showed in the figure \ref{fig:img02}.
@@
 
+\bibitem{FAQANN}
+Warren S. Sarle
+\newblock URL
+  \url{ftp://ftp.sas.com/pub/neural/FAQ.html#questions}.
+  \newblock Accessed 31 May, 2015
+
 \end{thebibliography}

### 2015-06-01 paper.tex
31 May 2015 21:45

@@
 Esta contribución describe la creación de un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador.
-El análisis inicio con la obtención de una foto área del MARN () con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
+El análisis inicio con la obtención de una foto área del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
 En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica.
@@
 
-According to
+It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} ) , neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251} and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
-Recently 
-%, fuzzy set theory (\citet{Kanungo2006347} and \citet{Guettouche20133163}) 
-and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251}.
+According to (\cite{van2006landslide}) the magnitude of a possible
+slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event.
+Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for applications where the complexity of the data detect complex nonlinear relationships, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
 
@@
 
-Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim funcion of the R statistical software, to obtain a better estimation of the parameters of the model.
+Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim function of the R statistical software, to obtain a better estimation of the parameters of the model.
 
@@
 % map of landslide hazard mostrado en la figura  
+% valorizar si se pone el codigo fuente
 
@@
 For all of the above parallel computing must be used rather than serial computing in estimating weights of neural networks models.
+
+%%%%  Mencionar abajo las limitaciones computacionales y 
+%%%% que no se pudo tomar una muestra mas grande que 1500 
+%%%% para el kriging relacionar con lo del big data que puede ser 
+%%%% linea de investigación
 
@@
   \url{ftp://ftp.sas.com/pub/neural/FAQ.html#questions}.
-  \newblock Accessed 31 May, 2015
+  \newblock Accessed 31 May, 2015.
+
+\bibitem{ballabio2012support}
+Ballabio, Cristiano and Sterlacchini, Simone
+\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
+\newblock \emph{Mathematical geosciences},
+  (11):\penalty0 1, 47--70, 2012.
+\newblock Springer.
+
+\bibitem{tien2012landslide}
+Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
+\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
+\newblock \emph{Mathematical Problems in Engineering},
+  (11):\penalty0 2012, 2012.
+\newblock Hindawi Publishing Corporation.
+
+\bibitem{akgun2012}
+Akgun, Aykut
+\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
+\newblock \emph{Landslides},
+  (11):\penalty0 9, 1, 93--106, 2012
+\newblock Springer.
+
+\bibitem{gaskill}
+Gaskill, Jacob and Zuber, Brian and Nordman, Erik
+\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
+\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
+\newblock URL
+  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
+
+\bibitem{van2006landslide}
+Van Westen, CJ and Van Asch, Th WJ and Soeters, R
+\newblock Landslide hazard and risk zonation why is it still so difficult?
+\newblock \emph{Bulletin of Engineering geology and the Environment}.
+(65):\penalty0 2, 167--184, 2006
+\newblock Springer.
 

### 2015-06-01 paper.tex
1 June 2015 9:30
Update paper.tex

@@
 slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event.
-Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for applications where the complexity of the data detect complex nonlinear relationships, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
+Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for detect complex non-linear relationships in large datasets, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
 

### 2015-06-03 paper.tex

@@
 \begin{resumen}
-Esta contribución describe la creación de un modelo de evaluación de deslizamiento de tierra para San Salvador, departamento de El Salvador.
+Esta contribución describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para San Salvador, departamento de El Salvador.
 El análisis inicio con la obtención de una foto área del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.

### 2015-06-03 paper.tex
02 June 2015 20:33

@@
 Esta contribución describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para San Salvador, departamento de El Salvador.
-El análisis inicio con la obtención de una foto área del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
-En esta evaluación de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfología, geología, precipitaciones máximas, aceleraciones sísmicas, pendiente del terreno, distancia a carretera y falla geológica.
-Redes Neuronales Artificiales(RNA) fueron usadas para la evaluación de la susceptibilidad a deslizamiento de tierra, logrando que más del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo.
-Regresión Logística fue usada como base de comparación, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificación abajo del 70\%.
-Para completar el análisis se realizo la interpolación de puntos usando el método krigging proveniente del enfoque geoestadístico.
-Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y técnicas geoestadísticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
+El an\'{a}lisis inicio con la obtenci\'{o}n de una foto área del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
+En esta evaluaci\'{o}n de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
+Redes Neuronales Artificiales(RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo.
+Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificaci\'{o}n abajo del 70\%.
+Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo krigging proveniente del enfoque geoestad\'{i}stico.
+Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
 \end{resumen}

### 2015-06-03 paper.tex
02 June 2015 20:40

@@
 
-\author[1]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com }}
-\author[2]{Giovanni Molina \thanks{giova.molina@gmail.com}}
-\author[3]{Ricardo Ríos \thanks{ricardo.sv@gmail.com}}
+\author[1]{Ricardo Ríos \thanks{ricardo.sv@gmail.com}}
+\author[2]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com}}
+\author[3]{Roberto Mej\'{i}a \thanks{robertomejia1685@gmail.com}}
+\author[4]{Giovanni Molina \thanks{giova.molina@gmail.com}}
 
@@
 Esta contribución describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para San Salvador, departamento de El Salvador.
-El an\'{a}lisis inicio con la obtenci\'{o}n de una foto área del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
+El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
 En esta evaluaci\'{o}n de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.

### 2015-06-03 paper.tex
02 June 2015 21:05

@@
 \usepackage{fancyhdr}
-\usepackage[utf8]{inputenc} % En caso de usar tildes, ñ y otros caracteres especiales
+\usepackage[utf8]{inputenc} % En caso de usar tildes, y otros caracteres especiales
 
@@
 
-\author[1]{Ricardo Ríos \thanks{ricardo.sv@gmail.com}}
+\author[1]{Ricardo R\'{i}os \thanks{ricardo.sv@gmail.com}}
 \author[2]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com}}
@@
 
-\affil[1]{National Institute of Health, Ministry of Health of El Salvador, El Salvador.}
-\affil[2]{Ministry of Environment and Natural Resources of El Salvador.}
-\affil[3]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
+\affil[1]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
+\affil[2]{National Institute of Health, Ministry of Health of El Salvador, El Salvador.}
+\affil[3]{National Institute of Health, Ministry of Health of El Salvador, El Salvador.}
+\affil[4]{Ministry of Environment and Natural Resources of El Salvador.}
 
@@
 Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo krigging proveniente del enfoque geoestad\'{i}stico.
-Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigación puede ayudar a la mitigación de deslizamientos de tierra en El Salvador.
+Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigaci\'{o}n puede ayudar a la mitigaci\'{o}n de deslizamientos de tierra en El Salvador.
 \end{resumen}

### 2015-06-03 paper.tex
02 June 2015 9:00

@@
 En esta evaluaci\'{o}n de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
-Redes Neuronales Artificiales(RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo.
+Redes Neuronales Artificiales (RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo.
 Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificaci\'{o}n abajo del 70\%.
@@
 landslide assessment we have used 4792 events previously photo-interpretaded
-and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance. Artificial
-Neural Networks (ANNs) were applied for the assessment of susceptibility to
+and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance.
+Artificial Neural Networks (ANN) were applied for the assessment of susceptibility to
 landslides, achieving more than 80\% of landslide were properly classified using
@@
 \label{sec:intr}
-El Salvador, one of the smallest and most crowded nations in Central America, extends about 240 kilometers westward from the 
-Gulf of Fonseca to the border with Guatemala. This country is very vulnerable to landslide due to social, political and economic factors.
-In the year of 2001, El Salvador was struck by two devastating earthquakes within a month. One of the most spectacular aspects featuring 
-heavily in the first earthquake was the damage inflicted by landslides. Among them, Las Colinas landslide was the most tragic.
-A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of a mountain ridge rising south behind Las Colinas area 
-of Nueva San Salvador (Santa Tecla), and flushed many houses and therefore more than 500 lives to death.
+El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala.
+El Salvador borders an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
+Therefore El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
+There is two main sources of seismic activity, the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs (\cite{dewey}).
+Due this tectonic and volcanic activity El Salvador has rugged relief.
+The main ranges cross the country with a rough west-east trend, parallel to the coast, these are separated from each other by faults and grabens.
+These ranges present several highly active volcanoes.
+The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic crops are located in the northern ranges, in the border with Honduras (\cite{weber}).
+Some of the most recent volcanic layers are formed by poor consolidated ashes and tuffs highly erodible (\cite{bommer}).
 
-Due to the above it is necessary to implement mechanisms that allow us to quantify the hazard of a given
-geographic area to landslides, usually this is done with development of susceptibility maps which present in a graphical way
-the zones more susceptible to landslides and represent a practical tool for urban planning.
+Throughout the year the country experiences a tropical climate with two seasons, a dry season (November to April) and wet season (May - October).
+The climate of El Salvador is generally warm.
+In the dry season there is very less rainfall but during rainy seasons heavy showers take place.
+El Salvador's interior regions remain dry throughout the year.
+Periodically El Salvador is affected by tropical storms and occasionally by hurricanes.
 
-%% write about how to perform your neural network and geostatistic analysis
+Like in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poor consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
+This problem is exacerbated by the extreme deforestation and the consequent high level of rates of erosion.
+Poverty, overpopulation and uncontrolled urbanization that characterizes the Salvadoran human settlements converts El Salvador in a country with high landslide risks.
+One example of this high risk is the devastating effect of the Las Colinas landslide triggered by a major earthquake (Mw 7.6) occurred on January of the 13, 2001  in Santa Tecla, a major city located close to San Salvador  the Salvadoran capital (\cite{evans}).
+A huge amount of soil mass (about 200,000 m3) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
+Together with this event this earthquake triggered several landslides along the country, especially in the Metropolitan Area of San Salvador (MASS) (\cite{jibson}).
+Other example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 (\cite{crone}).
 
-%The data was collected from aerial images, topographical and geologic maps which provide a base for  the application of landslide susceptibility methodologies and the development of geostatistics models.
-From aerial photographs, different regions of landslide occurrences were classified.
-The topographical and geologic maps provided information about causal factors.
-%
-%
-%Artificial neural networks (ANNs) are computational models inspired by biology (in particular the brain) that are capable of machine learning and pattern recognition.
-They are usually presented as systems of interconnected ``neurons'' that can compute values from inputs by feeding information through the network (\citet{wiki:001}).
-Recently ANNs have been applied successfully to the assessment of landslide susceptibility.
-%
-In this paper we propose an ANN model which enable to estimate the susceptibility to landslide in the georeferenced points belong to the Metropolitan Area of San Salvador (MASS) and later a map of susceptibility was generated by means of kriging method from geostatistical.
+Due to the above it is necessary to implement mechanisms that allow us to quantify the hazard of a given geographic area to landslides, usually this is done with development of susceptibility maps which present in a graphical way the zones more susceptible to landslides and represent a practical tool for urban planning.
+It was proposed an Artificial Neural Network model (ANN) which are a family of statistical learning models inspired by biological neural networks.
+The model proposed is used to estimate the susceptibility to landslide.
+From the results obtained by the model, a map was derived using kriging which is a method of interpolation spatial from the geostatistical approach.
 
-%\citet{Melchiorre2011410} determined landslide susceptibility for the Guantanamo Province %in Cuba by using ANN models.
-
-%%% I must citet the paper of Enrique Castellanos
+ \begin{center}
+  \begin{figure}[H]
+   \centering
+   \includegraphics[scale=0.80]{MASS_mapa_1}
+   \caption{\small{Maps from El Salvador}}
+   \label{fig:mass01}
+  \end{figure}
+ \end{center}
 
@@
 
+\bibitem{bommer}
+Bommer J.J., Rodriguez C.E.
+\newblock Earthquake-induced landslides in Central Am\'{e}rica
+\newblock \emph{Engineering Geology}.
+(63):\penalty0 1889-220, 2002
+
+\bibitem{crone}
+Crone A.J., Baum R.L., Lidke D.J., Sather D.N.D., Bradley L.-A., Tarr A.C.
+\newblock Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features
+\newblock \emph{USGS Open File Repord 01-444. (2002)}
+
+\bibitem{dewey}
+Dewey J.W. White R.A., Hern\'{a}ndez D.A.
+\newblock Seismicity and tectonics of El Salvador
+\newblock \emph{Chapter 27 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 367-378. (2004)}
+
+\bibitem{evans}
+Evans S.G. Bent A.L.
+\newblock Las Colinas landslide, Santa Tecla:  A higly destructive flowslide triggered by January 13, 2001, El Salvador earthquake.
+\newblock \emph{Chapter 3 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 25-37. (2004)}
+
+\bibitem{jibson}
+Jibson R.W., Crone A.J., Harp E.L., Baum R.L., Major J.J., Pullinguer C.R., Escobar D., Martinez M., Smith M.E. 
+\newblock Landslides triggered by the 13 January and 13 February 2001, earthquakes.
+\newblock \emph{ Chapter 6 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 69-88. (2004)}
+
+\bibitem{weber}
+Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thorn\'{e} M.
+\newblock Mapa geol\'{o}gico de Republica de El Salvador
+\newblock escala 1 : 100 000 (6 sheets).
+\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany. }
+
 %\bibitem[Carrara(1983)]{Carrara1983403}

### 2015-06-04 paper.tex
03 June 2015 21:22

@@
 \author[1]{Ricardo R\'{i}os \thanks{ricardo.sv@gmail.com}}
-\author[2]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com}}
+\author[2]{Alexandre Rib\'{o} \thanks{alexandre4rt@gmail.com}}
 \author[3]{Roberto Mej\'{i}a \thanks{robertomejia1685@gmail.com}}
@@
 Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificaci\'{o}n abajo del 70\%.
-Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo krigging proveniente del enfoque geoestad\'{i}stico.
+Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo kriging proveniente del enfoque geoestad\'{i}stico.
 Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigaci\'{o}n puede ayudar a la mitigaci\'{o}n de deslizamientos de tierra en El Salvador.
@@
 \label{sec:intr}
-El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala.
+El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala see Fig.
+\ref{fig:mass01}.
 El Salvador borders an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
@@
  \begin{center}
-  \begin{figure}[H]
+%  \begin{figure}[H]
+  \begin{figure}
    \centering
-   \includegraphics[scale=0.80]{MASS_mapa_1}
+   \includegraphics[scale=0.75]{MASS_mapa_1}
    \caption{\small{Maps from El Salvador}}
@@
 \label{sec:landsinvet}
-The Landslide inventory was developed from photographic analysis on the study area, using 
-aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
+The Landslide inventory was developed by MARN and it was conducted in two stages.
+The first was carried out, based on fieldwork after the 2001 eartquakes in El Salvador.
+The last stage is complete with a visual inventory of places where there were landslides in visible satellite image IRSC (India) sensor of the same year.
 
- \begin{center}
-  \begin{figure}[H]
-   \centering
-   \includegraphics[scale=0.40]{img01}
-   \caption{\small{Aerial photo of MASS}}
-   \label{fig:img01}
-  \end{figure}
- \end{center}
+from photographic analysis on the study area, using aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
+
+% \begin{center}
+%  \begin{figure}[H]
+%   \centering
+%   \includegraphics[scale=0.40]{img01}
+%   \caption{\small{Aerial photo of MASS}}
+%   \label{fig:img01}
+%  \end{figure}
+% \end{center}
 
@@
 
-The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying krigin method.
-The map of landslide hazard \ref{fig:img02} was generated by krigin method and can be used by non-experts in the landslide phenomenon for many purposes such as territorial planning, prevention and mitigation of natural dissasters and so on.
+The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
+The map of landslide hazard \ref{fig:img02} was generated by kriging method and can be used by non-experts in the landslide phenomenon for many purposes such as territorial planning, prevention and mitigation of natural dissasters and so on.
 
@@
 
+\bibitem{dewey}
+Dewey J.W. White R.A., Hern\'{a}ndez D.A.
+\newblock Seismicity and tectonics of El Salvador
+\newblock \emph{Chapter 27 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 367-378. (2004)}
+
+\bibitem{weber}
+Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thorn\'{e} M.
+\newblock Mapa geol\'{o}gico de Republica de El Salvador
+\newblock escala 1 : 100 000 (6 sheets).
+\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany. }
+
 \bibitem{bommer}
@@
 (63):\penalty0 1889-220, 2002
-
-\bibitem{crone}
-Crone A.J., Baum R.L., Lidke D.J., Sather D.N.D., Bradley L.-A., Tarr A.C.
-\newblock Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features
-\newblock \emph{USGS Open File Repord 01-444. (2002)}
-
-\bibitem{dewey}
-Dewey J.W. White R.A., Hern\'{a}ndez D.A.
-\newblock Seismicity and tectonics of El Salvador
-\newblock \emph{Chapter 27 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 367-378. (2004)}
 
@@
 
-\bibitem{weber}
-Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thorn\'{e} M.
-\newblock Mapa geol\'{o}gico de Republica de El Salvador
-\newblock escala 1 : 100 000 (6 sheets).
-\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany. }
+\bibitem{crone}
+Crone A.J., Baum R.L., Lidke D.J., Sather D.N.D., Bradley L.-A., Tarr A.C.
+\newblock Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features
+\newblock \emph{USGS Open File Repord 01-444. (2002)}
 

### 2015-06-04 paper.tex
04 June 2015 10:25

@@
 \label{sec:intr}
-El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala see Fig.
-\ref{fig:mass01}.
+El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala (see Fig \ref{fig:mass01}).
 El Salvador borders an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
@@
 %Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
+
+\section{Study area}
+\label{sec:studyarea}
+The Metropolitan Area of San Salvador (MASS), is formed by 14 municipalities among them there is San Salvador, the capital of the country.
+It has 587 km2 and according the most recent census \cite{minecon} it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
+According geography MASS is extended over a flat erosional surface (650-760 m a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
+MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig \ref{fig:mass01}).
+Human settlement is not only restricted to the plain, but spreads up to surrounding heights and volcano flanks.
+
+All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
+The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
+These are deposits derived mainly from Ilopango caldera eruptions where they present more than 50 m of thickness \cite{schmidt1975}.
+Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
+Chavez et al.
+2014a identifies high and moderate erosion hazard in majority of MASS area.
+The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) (Hernández 2004) present very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
+during rainy seasons), which results in high instability susceptibility (Chavez et al.
+2014b and Rolo et al.
+2004).
+Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercurses are often close to vertical and can reach highs of more than 10 m.
+Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
+As Bommer \& Rodriguez (2002) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
+Hernández (2004) carry out a detailed description of this process in TBJ, where these instabilities are very common.
+In study area fault trends are characterized by steep dip angles (650-900).
+The main fault system is characterized by an east-west trend; this trend is responsible of the steep northern slope of the El Balsamo Range.
+The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting \cite{schmidt1975}.
+However, all the mentioned fault families appear active.
+Thus the several fault systems have developed at different times, but been repeatedly activated (Rymer 1987).
+Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence \cite{schmidt1975}.
+Last eruption of San Salvador volcano was 1917.
+The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
+However a fraction of MASS is located under the proximal volcanic hazard zone according Sofield D.
+(2004).
+In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS (Major et al.
+2004).
+On the other hand one of the most destructive eruption in in the world was 430 A.D.
+TBJ eruption produced by the Ilopango Caldera.
+According Dull (2004), that eruption produced total devastation in whole MASS area.
 
@@
 \section{Acknowledgment}   
-The authors are indebted to M.SC. Giovanni Molina from MARN who provided the data and useful information about landslide modelling techniques.
+The authors are indebted with MARN who provided the data and GIS software such as ILWIS and ARCGIS.
 
@@
 \bibitem{weber}
-Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thorn\'{e} M.
+Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thom\'{e} M.
+\newblock Mapa geol\'{o}gico de Republica de El Salvador
+\newblock escala 1 : 100 000 (6 sheets).
+\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany. }
+
+\bibitem{weber}
+
 \newblock Mapa geol\'{o}gico de Republica de El Salvador
@@
 
+\bibitem{akgun2012}
+Akgun, Aykut
+\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
+\newblock \emph{Landslides},
+  (11):\penalty0 9, 1, 93--106, 2012
+\newblock Springer.
+
+\bibitem{gaskill}
+Gaskill, Jacob and Zuber, Brian and Nordman, Erik
+\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
+\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
+\newblock URL
+  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
+
 %\bibitem[Melchiorre et~al.(2011)Melchiorre, Abella, van Westen, and
@@
 
+\bibitem{ballabio2012support}
+Ballabio, Cristiano and Sterlacchini, Simone
+\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
+\newblock \emph{Mathematical geosciences},
+  (11):\penalty0 1, 47--70, 2012.
+\newblock Springer.
+
+\bibitem{tien2012landslide}
+Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
+\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
+\newblock \emph{Mathematical Problems in Engineering},
+  (11):\penalty0 2012, 2012.
+\newblock Hindawi Publishing Corporation.
+
+\bibitem{van2006landslide}
+Van Westen, CJ and Van Asch, Th WJ and Soeters, R
+\newblock Landslide hazard and risk zonation why is it still so difficult?
+\newblock \emph{Bulletin of Engineering geology and the Environment}.
+(65):\penalty0 2, 167--184, 2006
+\newblock Springer.
+
+%%%%%%%%%%%%%%  Study Area %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibitem{minecon}
+Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos
+\newblock VI Censo de Población y V de Vivienda
+\newblock \emph{2007-2008}.
+\penalty0 Available from http://goo.gl/yvjzPy
+
+\bibitem{schmidt1975}
+Schmidt-Thom\'{e} M.
+\newblock The geology in San Salvador area (El Salvador, Central America), a basis for city development and planning
+\newblock \emph{Geol. Jb.}.
+\penalty0 13, 207-228, 1975.
+
+%Rymer M.J. (1987). The San Salvador Earthquake of October 10, 1986 – Geologic Aspects Earthquake Spectra, %3(3), 435-463.
+
+%Sofield D.
+(2004) Eruptive history and volcanic hazards of Volcan San Salvador.
+Chapter 11 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J.
+and Major J.J.
+147-158.
+%
+%
+%
+%
+%
+%Chávez J.A., Sebesta J., Kopecky L., López R. (2014a). Application of Geomorphologic Knowledge for Erosion Hazard Mapping. Natural Hazards. 71:1323–1354. DOI 10.1007/s11069-013-0948-8
+%
+%Chávez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). Application of Constitutive Models in the Volcanic Tephra “Tierra Blanca Joven”. Ingeniería 24 (2).53-78. ISSN: 2215-2652.
+%
+%Dull R.A.
+(2004) Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption.
+Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J.
+and Major J.J.
+237-244.
+%
+%Hernández W.E.
+(2004).
+Características Geomecánicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
+MSc Thesis.
+Universidad Politécnica de Madrid – Universidad Politécnica de El Salvador [cited 2015 May 31].
+Available from http://portafolio.snet.gob.sv/digitalizacion/pdf/spa/doc00079/doc00079.htm
+%
+%Major J.J.
+Chilling S.P., Pullinguer C.R., Escobar C.D.
+(2004).
+Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador.
+Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J.
+and Major J.J.
+89-108.
+%
+%Ministerio de Economia- Dirección General de Estadística y Censos (2008) VI Censo de Población y V de Vivienda .
+[cited 2015 May 31].
+Available from http://www.censos.gob.sv/util/datos/Resultados\%20VI%20Censo%20de%20Poblaci%C3%B3n%20V%20de%20Vivienda%202007.pdfthe
+%Rymer M.J. (1987). The San Salvador Earthquake of October 10, 1986 – Geologic Aspects Earthquake Spectra, 3(3), 435-463.
+%
+%Rolo R., Bommer J.J., Houghton B.F., Vallance J.W., Berdousis P., Mavrommati C., Morphy W.
+(2004).
+Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits.
+Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J.
+and Major J.J.
+55-67.
+%
+%Schmidt-Thomé M. (1975). The geology in San Salvador area (El Salvador, Central America), a basis for city development and planning. Geol. Jb., 13, 207-228.
+%Sofield D.
+(2004) Eruptive history and volcanic hazards of Volcan San Salvador.
+Chapter 11 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J.
+and Major J.J.
+147-158.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibitem{McNelis2005}
@@
 
-\bibitem{ballabio2012support}
-Ballabio, Cristiano and Sterlacchini, Simone
-\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
-\newblock \emph{Mathematical geosciences},
-  (11):\penalty0 1, 47--70, 2012.
-\newblock Springer.
-
-\bibitem{tien2012landslide}
-Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
-\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
-\newblock \emph{Mathematical Problems in Engineering},
-  (11):\penalty0 2012, 2012.
-\newblock Hindawi Publishing Corporation.
-
-\bibitem{akgun2012}
-Akgun, Aykut
-\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
-\newblock \emph{Landslides},
-  (11):\penalty0 9, 1, 93--106, 2012
-\newblock Springer.
-
-\bibitem{gaskill}
-Gaskill, Jacob and Zuber, Brian and Nordman, Erik
-\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
-\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
-\newblock URL
-  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
-
-\bibitem{van2006landslide}
-Van Westen, CJ and Van Asch, Th WJ and Soeters, R
-\newblock Landslide hazard and risk zonation why is it still so difficult?
-\newblock \emph{Bulletin of Engineering geology and the Environment}.
-(65):\penalty0 2, 167--184, 2006
-\newblock Springer.
-
 \end{thebibliography}

### 2015-06-04 paper.tex
04 June 2015 16:24

--- 2015-06-04 paper.tex
@@
 
-It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} ) , neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251} and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
+It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008} ) , neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251} and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
@@
 %Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
+
+\section{Study area}
+\label{sec:studyarea}
+The Metropolitan Area of San Salvador (MASS), is formed by 14 municipalities among them there is San Salvador, the capital of the country.
+It has 587 km2 and according to the most recent census (\cite{minecon}) it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
+According to geography MASS is extended over a flat erosional surface (650-760 m a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
+MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig \ref{fig:mass01}).
+Human settlement is not only restricted to the plain, but spreads up to surrounding heights and volcano flanks.
+
+All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age (\cite{schmidt1975}).
+The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in majority of MASS with an average thickness of 4 m (\cite{schmidt1975}).
+These are deposits derived mainly from Ilopango caldera eruptions where they present more than 50 m of thickness (\cite{schmidt1975}).
+Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking (\cite{schmidt1975}).
+(\cite{chavez2014a}) identifies high and moderate erosion hazard in majority of MASS area.
+The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) (\cite{hernan2004}) present very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
+during rainy seasons), which results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
+Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercurses are often close to vertical and can reach highs of more than 10 m.
+Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
+As (\cite{bommer}) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
+(\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
+In study area fault trends are characterized by steep dip angles (650-900).
+The main fault system is characterized by an east-west trend; this trend is responsible of the steep northern slope of the El Balsamo Range.
+The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting (\cite{schmidt1975}).
+However, all the mentioned fault families appear active.
+Thus the several fault systems have developed at different times, but been repeatedly activated (\cite{rymer1987}).
+Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence (\cite{schmidt1975}).
+Last eruption of San Salvador volcano was 1917.
+The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
+However a fraction of MASS is located under the proximal volcanic hazard zone according to (\cite{sofield2004}).
+In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS (\cite{major2004}).
+On the other hand one of the most destructive eruption in in the world was 430 A.D.
+TBJ eruption produced by the Ilopango Caldera.
+According to (\cite{dull2004}), that eruption produced total devastation in whole MASS area.
 
@@
 As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it showed a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
-With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were imported to Geotiff raster format.
+With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were imported to Geotiff raster format with the purpose of using this raster map in ArcGIS to generate the landslide hazard map for MASS.
 
@@
 
-The map of landslide hazards is showed in the figure \ref{fig:img02}.
-
- \begin{center}
-  \begin{figure}[H]
-   \centering
-   \includegraphics[scale=0.40]{img02}
-   \caption{\small{Map of landslide hazards}}
-   \label{fig:img02}
-  \end{figure}
- \end{center}
+%The map of landslide hazards is showed in the figure \ref{fig:img02}.
+%
+% \begin{center}
+%  \begin{figure}[H]
+%   \centering
+%   \includegraphics[scale=0.40]{img02}
+%   \caption{\small{Map of landslide hazards}}
+%   \label{fig:img02}
+%  \end{figure}
+% \end{center}
 
@@
 
+%%% Alex's Discussion
+
+The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
+Final map of landslide probability of occurrence (see Fig \ref{fig:mass02} ) generated by kriging method is the result of multidisciplinary work which implied an intense geological analysis (i.e.
+MARN inventory of more than 4000 landslides) together with the use of sophisticated statistical techniques.
+This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on.
+
+\begin{center}
+%  \begin{figure}[H]
+  \begin{figure}
+   \centering
+   \includegraphics[scale=0.75]{MASS_mapa_2}
+   \caption{\small{Landslide hazard map MASS}}
+   \label{fig:mass02}
+  \end{figure}
+ \end{center}
+
+High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.(\cite{major2004}) identified in San Salvador volcano that lahars as voluminous as 2 million of m3 can affect large zones of urban areas.
+Southern areas of MASS also implies a high risk because large landslides, similar to Las Colinas landslide which involved a total volume of around 150,000 m3 (\cite{evans}), can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
+
+The present hazard landslide map is consistent with former landslide hazard maps carried out in the region using approaches conceptually different.
+(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
+The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where (\cite{fernan2008}) identifies a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presents a hazard slightly lower.
+As landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincides with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by (\cite{chavez2014a}).
+There are similarities with susceptibility hazard maps at national scale generated through logistic regression method (\cite{garcia2008}), through artificial neural network method (\cite{garcia2010}) and Mora-Vahrson method (\cite{snet2004}).
+However the high landslide areas are more extended in these national maps than the present study.
+These differences could be explained by the working scale, our map is more detailed because is at regional scale.
+Other possible explanation can be related to the data, present work was built using a more extended landslide catalog and more updated data (e.g.
+seismic hazard from \cite{beni2012}) than former works.
+
+Rock falls were not included in the catalog; these were very common during 2001 earthquakes in El Balsamo Range (\cite{jibson}).
+On the other hand, the MASS seismic microzonation of seismic site effects will improve the estimation of peak ground acceleration.
+The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface, additionally, the geometry of the ground surface also may produce amplification (topographic effects) (\cite{aki1993}).
+These effects can be important in soft soils close to incised rivers and also in San Salvador volcano, Balsamo ranges and hills.
+(\cite{crosta2005}) identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
+All these variables can improve the predictive ability of the model and surely the likelihood of landslides.
+
 %%%%  Mencionar abajo las limitaciones computacionales y 
@@
 
-The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
+%The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
 The map of landslide hazard \ref{fig:img02} was generated by kriging method and can be used by non-experts in the landslide phenomenon for many purposes such as territorial planning, prevention and mitigation of natural dissasters and so on.
-
-Other important variables could not be obtained such as landslide types (Rockfalls, Topples, Slides, etc) and temporal information which can improve the predictive ability of the model.
+%
+%Other important variables could not be obtained such as landslide types (Rockfalls, Topples, Slides, etc) and temporal information which can improve the predictive ability of the model.
 
 \section{Acknowledgment}   
-The authors are indebted to M.SC. Giovanni Molina from MARN who provided the data and useful information about landslide modelling techniques.
+The authors are indebted with MARN who provided the data and GIS software such as ILWIS and ARCGIS.
 
@@
 \bibitem{weber}
-Weber H.S., Wiesemann G., Lorenz  W., Scmith-Thorn\'{e} M.
+Weber H.S., Wiesemann G., Lorenz  W., Schmidt-Thom\'{e} M.
 \newblock Mapa geol\'{o}gico de Republica de El Salvador
@@
 
+\bibitem{akgun2012}
+Akgun, Aykut
+\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
+\newblock \emph{Landslides},
+  (11):\penalty0 9, 1, 93--106, 2012
+\newblock Springer.
+
+\bibitem{gaskill}
+Gaskill, Jacob and Zuber, Brian and Nordman, Erik
+\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
+\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
+\newblock URL
+  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
+
+\bibitem{garcia2008}
+García-Rodríguez M.J., Malpica J.A., Benito B., Díaz M.
+\newblock  Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression.
+\newblock \emph{Geomorphology}
+\penalty0 95, 172-191, 2008.
+
+\bibitem{garcia2010}
+García-Rodríguez M.J., Malpica J.A.
+\newblock Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model.
+\newblock \emph{Nat. Hazards Earth Syst. Sci.}
+\penalty0 10, 1307–1315, 2010. 
+\newblock doi:10.5194/nhess-10-1307-2010.
+
 %\bibitem[Melchiorre et~al.(2011)Melchiorre, Abella, van Westen, and
@@
 
+\bibitem{ballabio2012support}
+Ballabio, Cristiano and Sterlacchini, Simone
+\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
+\newblock \emph{Mathematical geosciences},
+  (11):\penalty0 1, 47--70, 2012.
+\newblock Springer.
+
+\bibitem{tien2012landslide}
+Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
+\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
+\newblock \emph{Mathematical Problems in Engineering},
+  (11):\penalty0 2012, 2012.
+\newblock Hindawi Publishing Corporation.
+
+\bibitem{van2006landslide}
+Van Westen, CJ and Van Asch, Th WJ and Soeters, R
+\newblock Landslide hazard and risk zonation why is it still so difficult?
+\newblock \emph{Bulletin of Engineering geology and the Environment}.
+(65):\penalty0 2, 167--184, 2006
+\newblock Springer.
+
+%%%%%%%%%%%%%%  Study Area %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibitem{minecon}
+Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos
+\newblock VI Censo de Población y V de Vivienda
+\newblock \emph{2007-2008}.
+\penalty0 Available from http://goo.gl/yvjzPy
+
+\bibitem{schmidt1975}
+Schmidt-Thom\'{e} M.
+\newblock The geology in San Salvador area (El Salvador, Central America), a basis for city development and planning.
+\newblock \emph{Geol. Jb.}.
+\penalty0 13, 207-228, 1975.
+
+\bibitem{chavez2014a}
+Ch\'{a}vez J.A., Sebesta J., Kopecky L., L\'{o}pez R.
+\newblock Application of Geomorphologic Knowledge for Erosion Hazard Mapping
+\newblock \emph{Natural Hazards}.
+\penalty0 71,1323–1354, 2014.
+\newblock DOI 10.1007/s11069-013-0948-8.
+
+\bibitem{hernan2004}
+Hern\'{a}ndez W.E.
+\newblock Características Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
+\newblock MSc Thesis. Universidad Politécnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
+\penalty0 2004
+
+\bibitem{chavez2014b}
+Chávez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). 
+\newblock Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''.
+\newblock \emph{Ingeniería.}
+\penalty0  24 (2).53-78.
+\newblock  ISSN: 2215-2652.
+
+\bibitem{rolo2004}
+Rolo R., Bommer J.J., Houghton B.F., Vallance J.W., Berdousis P., Mavrommati C., Morphy W.
+\newblock Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits.
+\newblock \emph{Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\penalty0  55-67, 2004.
+
+\bibitem{rymer1987}
+Rymer M.J. 
+\newblock The San Salvador Earthquake of October 10, 1986.
+\newblock \emph{Geologic Aspects Earthquake Spectra.}
+\penalty0 3(3), 435-463, 1987.
+
+\bibitem{dull2004}
+Dull R.A.
+\newblock Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption.
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\penalty0 237-244., 2004.
+
+\bibitem{major2004}
+Major J.J. Chilling S.P., Pullinguer C.R., Escobar C.D.
+\newblock Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador.
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\penalty0 89-108, 2004.
+
+\bibitem{sofield2004}
+Sofield D.
+\newblock Eruptive history and volcanic hazards of Volcan San Salvador. 
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\penalty0 147-158, 2004.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%   Landslide inventory and data sources of input variables                        %%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibitem{beni2012}
+Benito M.B., Lindholm C., Camacho E., Climent Á., Marroquín G., Molina E.,Rojas W., Escobar J.J., Talavera E., Alvarado G.E. and Torres Y.
+\newblock A New Evaluation of Seismic Hazard for the Central America Region. 
+\newblock \emph{Bulletin of the Seismological Society of America}
+\penalty0 102 (2), 504-523. 2012.
+\newblock  doi: 10.788/0120110015
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibitem{McNelis2005}
@@
 
-\bibitem{ballabio2012support}
-Ballabio, Cristiano and Sterlacchini, Simone
-\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
-\newblock \emph{Mathematical geosciences},
-  (11):\penalty0 1, 47--70, 2012.
-\newblock Springer.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%  Discussion  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibitem{tien2012landslide}
-Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
-\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
-\newblock \emph{Mathematical Problems in Engineering},
-  (11):\penalty0 2012, 2012.
-\newblock Hindawi Publishing Corporation.
+\bibitem{fernan2008}
+Fernandez-Lavado C., Sanchez A., Amenos M., Barrio J.
+\newblock Caracterización de la susceptibilidad y de la amenaza por movimientos de ladera del Área Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet).
+\newblock \emph{Project IPGARAMSS framework. Geólogos del Mundo. San Salvador, El Salvador.}
+\penalty0 2008.
 
-\bibitem{akgun2012}
-Akgun, Aykut
-\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
-\newblock \emph{Landslides},
-  (11):\penalty0 9, 1, 93--106, 2012
-\newblock Springer.
+\bibitem{snet2004}
+SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales
+\newblock Memoria Técnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador.
+\newblock \emph{Ministerio de Ambiente y Recursos Naturales}
+\penalty0 [cited 2015 June 04]. Map available from http://www.snet.gob.sv/ver/geologia/susceptibilidad+actual/
 
-\bibitem{gaskill}
-Gaskill, Jacob and Zuber, Brian and Nordman, Erik
-\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
-\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
-\newblock URL
-  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
+\bibitem{aki1993}
+Aki, K. 
+\newblock Local site effects on weak and strong ground motion. In F. Lund (ed.) New Horizons in Strong Motion: Seismic Studies and Engineering Practice.
+\newblock \emph{Tectonophysics}
+\penalty0 218, 93-111, 1993.
 
-\bibitem{van2006landslide}
-Van Westen, CJ and Van Asch, Th WJ and Soeters, R
-\newblock Landslide hazard and risk zonation why is it still so difficult?
-\newblock \emph{Bulletin of Engineering geology and the Environment}.
-(65):\penalty0 2, 167--184, 2006
-\newblock Springer.
+\bibitem{crosta2005}
+Crosta G.B., Imposimato S., Rodderman, Chiesa S.m, Moia F. 
+\newblock Small fast-moving flow-like landslides in volcanic deposits: The 2001 Las Colinas Landslide (El Salvador). 
+\newblock \emph{Engineering Geology.}
+\penalty0 79, 185-214, 2005.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-06-05 paper.tex
04 June 2015 22:23

@@
 In the dry season there is very less rainfall but during rainy seasons heavy showers take place.
-El Salvador's interior regions remain dry throughout the year.
 Periodically El Salvador is affected by tropical storms and occasionally by hurricanes.
@@
    \centering
-   \includegraphics[scale=0.75]{MASS_mapa_1}
-   \caption{\small{Maps from El Salvador}}
+   \includegraphics[scale=0.70]{MASS_mapa_1}
+   \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Area Metropolitana de San Salvador (MASS) and topography of MASS.}}
    \label{fig:mass01}
@@
 The first was carried out, based on fieldwork after the 2001 eartquakes in El Salvador.
-The last stage is complete with a visual inventory of places where there were landslides in visible satellite image IRSC (India) sensor of the same year.
+The another stage was completed with a visual inventory of places where there were landslides which were visible in a image of satellite image from IRS-C sensor (Indian) in the same year.
 
-from photographic analysis on the study area, using aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
+%from photographic analysis on the study area, using aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
 
@@
 
-Once that the white areas were georeferenced, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence.
-In addition to the landslide information the following data sources of input variables was given by MARN:
+Once that the landslide inventory was finished, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence.
+In addition to the landslide information the following data sources of input variables was provided by MARN:
+
 \begin{enumerate}
 \item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.
+The physical properties of slope-forming materials, such as strength and permeability, are related to the lithology factor, which therefore should affect the likelihood of slope failure (\cite{dai2002}).
+This variables was obtained in accordance with the project of national land use plan in El Salvador.
 
-\item {\bf Slope:} derived from digital elevation model MARN
+\item {\bf Slope:} Slope gradient is an important component and a
+preparatory cause of landsliding (\cite{garcia2008}). It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mts.
 
-\item {\bf Geology:} Description of the geology of the area from the map German Geological Mission (scale 1:100,000).
+\item {\bf Geology:} Description of the geology of the area from the map German Geological Mission (scale 1:100,000) (\cite{weber}).
 
-\item {\bf Rainfall intensity:} Maximum rainfall recorded in the geographical area.
+\item {\bf Rainfall intensity:} From the precipitation database compiled by the
+SNET's weather stations for the period 1970–2001, maximum precipitations were obtained, and then was applied interpolation kriging to them.
 
-\item {\bf Peak ground accelaration:} Maximum ground acceleration expressed in Gal for a return period of 500 years, this is the least that has detailed information.
-This information was obtained from RSIS II project.
+\item {\bf Peak ground accelaration:} Maximum ground acceleration expressed in Gal for a return period of 500 years.
+This data was obtained from the evaluation of seismic Hazard in Central America carried out under the framework of RSIS II project (\cite{beni2012}).
 
 \item {\bf Road distance:} Distance in kilometers to the nearest road.
+Road map was obtained from digitalized national cartography from Centro Nacional de Registros de la República de El Salvador (CNR).
 
-\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from German Geological Mission (scale 1:100,000).
+\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from according digitalized geological map of El Salvador (scale 1:100,000) (\cite{weber}).
 
@@
 \hline
-Número de neuronas &    Train set    &   Validation set &  Test set \\
+Number of neurons &    Train set    &   Validation set &  Test set \\
 \hline
@@
 
-To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging and validation of this results.
+To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging, validation of this results and .
 
-In order to achieve the above steps a R scrit was developed which can be downloaded in the following address:
+In order to achieve the above steps a R script was developed which can be downloaded in the following address:
 
@@
 As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it showed a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
-With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were imported to Geotiff raster format with the purpose of using this raster map in ArcGIS to generate the landslide hazard map for MASS.
+With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were exported to Geotiff raster format.
+Finally Geographic Information System (ArcGIS\textregistered \  of ESRI) was used to design the final map (Figure \ref{fig:mass02}).
+This map (Fig.
+\ref{fig:mass02}) represents the landslide probability of occurrences in MASS.
+According to Fig.
+\ref{fig:mass02} higher probability of landslide occurrence, reaching probability of occurrence values around 0.8, are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
+Areas with lower probability but still important, are located in southern and western side of Nejapa Hill, in north-east of the study area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill and, in general in southern side of MASS.
 
@@
 This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on.
-
 \begin{center}
@@
    \centering
-   \includegraphics[scale=0.75]{MASS_mapa_2}
-   \caption{\small{Landslide hazard map MASS}}
+   \includegraphics[scale=0.70]{MASS_mapa_2}
+   \caption{\small{Landslide hazard map MASS where is shown the landslide probability of occurrence.}}
    \label{fig:mass02}
@@
  \end{center}
-
 High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.(\cite{major2004}) identified in San Salvador volcano that lahars as voluminous as 2 million of m3 can affect large zones of urban areas.
@@
 As landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincides with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by (\cite{chavez2014a}).
-There are similarities with susceptibility hazard maps at national scale generated through logistic regression method (\cite{garcia2008}), through artificial neural network method (\cite{garcia2010}) and Mora-Vahrson method (\cite{snet2004}).
+There are similarities with susceptibility hazard maps at national scale generated through logistic regression method (\cite{garcia2008}), through artificial neural network method (\cite{garcia2010}) and through Mora-Vahrson method (\cite{snet2004}).
 However the high landslide areas are more extended in these national maps than the present study.
@@
 Other possible explanation can be related to the data, present work was built using a more extended landslide catalog and more updated data (e.g.
-seismic hazard from \cite{beni2012}) than former works.
+seismic hazard evaluation from \cite{beni2012}) than former works.
 
@@
 \section{Acknowledgment}   
-The authors are indebted with MARN who provided the data and GIS software such as ILWIS and ARCGIS.
+The authors are indebted with MARN who provided the data and Geogrphic Information System software such as ILWIS and ArcGIS\textregistered \  of ESRI.
 
@@
 \newblock escala 1 : 100 000 (6 sheets).
-\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany. }
+\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany.
+}
+\penalty0 (1978).
 
@@
 \newblock \emph{Engineering Geology}.
-(63):\penalty0 1889-220, 2002
+(63):\penalty0 1889-220, (2002).
 
@@
 
+\bibitem{dai2002}
+Dai, F. C. and Lee, C. F.
+\newblock Landslide characteristics and slope instability modeling using GIS, Lantau Island, Hong Kong.
+\newblock \emph{Geomorphology}
+\penalty0 42, 213–228, 2002.
+
 \bibitem{beni2012}

### 2015-06-05 resources/kriging/kriging.R
04 June 2015 22:31

@@ -1,0 +1,262 @@
+### Loading package 
+
+
+library(maptools)
+library(sp)
+library(lattice)
+library(ggmap)
+library(proj4)
+library(rgdal)
+library(scales)
+library(RgoogleMaps)
+library(RColorBrewer)
+library(gstat)
+library(raster)
+
+### The file DeslizamientosAMSS contains the projection system 
+
+
+###########################################################
+###########################################################
+###########################################################
+
+
+
+
+deslizamientos <- readOGR(".","DeslizamientosAMSS")
+
+print(proj4string(deslizamientos))
+
+coord.ref.sys <- proj4string(deslizamientos)
+
+
+datos <- read.csv(file="data.csv", header=TRUE); 
+
+
+coordinates(datos) <- c("long", "lat")
+
+# Proj4 string from the original shape files 
+#
+#"+proj=lcc +lat_1=13.31666666 +lat_2=14.25 +lat_0=13.78333333333333 +lon_0=-89 +x_0=500000 +y_0=295809.184 +datum=NAD27 +units=m +no_defs +ellps=clrk66 +nadgrids=@conus,@alaska,@ntv2_0.gsb,@ntv1_can.dat"
+proj4string(datos) <- CRS(coord.ref.sys)
+
+
+datos <- sp::spTransform(datos, CRS("+proj=longlat +datum=WGS84"))
+
+
+datos2 <- data.frame(prob=datos$prob, cat=datos$cat)
+datos2 <- cbind(datos2, datos@coords)
+
+### Ploting the map without the points 
+
+map <- get_map(location = c( -89.2 , 13.75 ), zoom = 11, maptype = "roadmap")
+
+p <- ggmap(map)
+plot(p)
+
+
+### Ploting the map with the points 
+
+p <- p + geom_point(aes(x=datos2$long, y = datos2$lat), 
+                    data = datos2, alpha = 0.5, 
+                    color = "darkred", size = 3)
+
+plot(p)
+
+
+###########################################################
+
+a <- data.frame(x=datos2$long, y=datos2$lat, z=datos2$prob)
+
+
+indices <- sample(1:978252,1500)
+
+e <- a[indices,];
+
+
+coordinates(e) <- c("x", "y")
+
+pal = brewer.pal(5,"OrRd")
+
+
+spplot(e, "z", colorkey = FALSE, 
+       col.regions = pal, ylab = "Probability of landslide occurrence", 
+       scales = list(draw=T))
+
+
+##############################################
+##############################################
[…]

### 2015-06-05 paper.tex
04 June 2015 22:35

@@
 
-First of all one thousand fifty georeferenced point with their probability of ocurrence which was calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the model.
+\url{https://goo.gl/3N8n99}
+
+First of all one thousand fifty georeferenced point with their probability of ocurrence which was calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
 The Exploratory analysis showed the presence of spatial correlation in the data, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect.

### 2015-06-05 paper.tex
05 June 2015 6:24

@@
 \usepackage{hyperref}
+\usepackage{textcomp}
 
@@
 \label{sec:intr}
-El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala (see Fig \ref{fig:mass01}).
+El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala (see Fig.
+\ref{fig:mass01}).
 El Salvador borders an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
@@
 According to geography MASS is extended over a flat erosional surface (650-760 m a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
-MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig \ref{fig:mass01}).
+MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig.
+\ref{fig:mass01}).
 Human settlement is not only restricted to the plain, but spreads up to surrounding heights and volcano flanks.
@@
 Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking (\cite{schmidt1975}).
+Chávez et al.
 (\cite{chavez2014a}) identifies high and moderate erosion hazard in majority of MASS area.
@@
 Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
-As (\cite{bommer}) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
-(\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
-In study area fault trends are characterized by steep dip angles (650-900).
+As Bommer \& Rodriguez (\cite{bommer}) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
+Hernández (\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
+In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
 The main fault system is characterized by an east-west trend; this trend is responsible of the steep northern slope of the El Balsamo Range.
@@
 The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
-However a fraction of MASS is located under the proximal volcanic hazard zone according to (\cite{sofield2004}).
+However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield (\cite{sofield2004}).
 In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS (\cite{major2004}).
-On the other hand one of the most destructive eruption in in the world was 430 A.D.
+On the other hand one of the most destructive eruption in the world history was 430 A.D.
 TBJ eruption produced by the Ilopango Caldera.
-According to (\cite{dull2004}), that eruption produced total devastation in whole MASS area.
+According to Dull (\cite{dull2004}), that eruption produced total devastation in whole MASS area.
 
@@
 \begin{equation}
-x*_{k,i} = \frac{x_{k,i} - \mu }{\sigma}
+x*_{i} = \frac{x_{i} - \mu }{\sigma}
+\label{eq:scaling}
 \end{equation}
 
-Where $ \mu $ and $\sigma$  is respectively the mean and the standard deviation for the ith input variable applied to the kth case.
+In the equation (\ref{eq:scaling}) $x*_{i}$ is the new variable transformed with $ \mu $ and $\sigma$ are, respectively the mean and the standard deviation for the ith input variable.
 
-The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software specifically developed for this purpose, was used to obtain
-a good estimation of the parameters of the model.
+The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software (\cite{rproject}) specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
 
@@
 
-In order to make spatial predictions using ordinary kriging, an R script was developed which can be accessed in the following web address:
+In order to make spatial predictions using ordinary kriging, a R script was developed which can be accessed in the following web address:
+
+\url{https://goo.gl/3N8n99}
 
@@
 The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
-Final map of landslide probability of occurrence (see Fig \ref{fig:mass02} ) generated by kriging method is the result of multidisciplinary work which implied an intense geological analysis (i.e.
-MARN inventory of more than 4000 landslides) together with the use of sophisticated statistical techniques.
+Final map of landslide probability of occurrence (see Fig.
+\ref{fig:mass02} ) generated by kriging method is the result of multidisciplinary work which implied an intense geological analysis (i.e.
+MARN inventory of 4792 landslides) together with the use of sophisticated statistical techniques.
 This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on.
@@
  \end{center}
-High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.(\cite{major2004}) identified in San Salvador volcano that lahars as voluminous as 2 million of m3 can affect large zones of urban areas.
+High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.
+Major et al.(\cite{major2004}) identified in San Salvador volcano that lahars as voluminous as 2 million of $mts^{3}$ can affect large zones of urban areas.
 Southern areas of MASS also implies a high risk because large landslides, similar to Las Colinas landslide which involved a total volume of around 150,000 m3 (\cite{evans}), can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
@@
 The present hazard landslide map is consistent with former landslide hazard maps carried out in the region using approaches conceptually different.
-(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
+Fernández-Lavado et al.(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
 The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where (\cite{fernan2008}) identifies a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presents a hazard slightly lower.
@@
 Other possible explanation can be related to the data, present work was built using a more extended landslide catalog and more updated data (e.g.
-seismic hazard evaluation from \cite{beni2012}) than former works.
+seismic hazard evaluation from Benito et al.\cite{beni2012}) than former works.
 
@@
 These effects can be important in soft soils close to incised rivers and also in San Salvador volcano, Balsamo ranges and hills.
-(\cite{crosta2005}) identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
+Crosta et al.(\cite{crosta2005}) identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
 All these variables can improve the predictive ability of the model and surely the likelihood of landslides.
@@
 
+\bibitem{FAQANN}
+Warren S. Sarle
+\newblock URL
+  \url{ftp://ftp.sas.com/pub/neural/FAQ.html#questions}.
+  \newblock Accessed 31 May, 2015.
+
 \bibitem{McNelis2005}
@@
 
-\bibitem{FAQANN}
-Warren S. Sarle
-\newblock URL
-  \url{ftp://ftp.sas.com/pub/neural/FAQ.html#questions}.
-  \newblock Accessed 31 May, 2015.
+\bibitem{rproject}
+R Core Team
+\newblock R: A Language and Environment for Statistical Computing.
+\newblock \emph{R Foundation for Statistical Computing.}
+\penalty0 Vienna, Austria, 2014.
 

### 2015-06-05 paper.tex
05 June 2015 6:52
05 June 2015 16:34

@@
 \fancyhead{}
-\fancyhead[RE]{\thepage \hfill {\sc a. rib\'{o} -- g. molina -- r. r\'{i}os  }}
+\fancyhead[RE]{\thepage \hfill {\sc r. r\'{i}os -- a. rib\'{o} -- r. mej\'{i}a -- g. molina }}
 \fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
@@
 \newline
-Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador}
+Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra del \'{a}rea Metropolitana de San Salvador, El Salvador}
 
@@
 \begin{resumen}
-Esta contribución describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para San Salvador, departamento de El Salvador.
+Esta contribuci\'{o}n describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para el \'{A}rea Metropolitana de San Salvador, departamento de El Salvador.
 El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
 En esta evaluaci\'{o}n de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
-Redes Neuronales Artificiales (RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los parámetros del modelo.
+Redes Neuronales Artificiales (RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los par\'{a}metros del modelo.
 Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificaci\'{o}n abajo del 70\%.
 Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo kriging proveniente del enfoque geoestad\'{i}stico.
-Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinación de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigaci\'{o}n puede ayudar a la mitigaci\'{o}n de deslizamientos de tierra en El Salvador.
+Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinaci\'{o}n de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigaci\'{o}n puede ayudar a la mitigaci\'{o}n de deslizamientos de tierra en El Salvador.
 \end{resumen}
 
-\PC deslizamiento de tierra, evaluación de riesgo, El Salvador, RNA, geoestadística.
+\PC deslizamiento de tierra, evaluaci\'{o}n de riesgo, El Salvador, RNA, geoestad\'{i}stica.
 
@@
 assessment model for San Salvador, department in El Salvador.
-The analysis started with an aerial photointerpretation from  MARN (Ministry of Environment and Natural Resources of El Salvador)  with a total amount of 939407 georeferenced points to produce a landslide inventory.
+The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym)  with a total amount of 939407 georeferenced points to produce a landslide inventory.
 In this
 landslide assessment we have used 4792 events previously photo-interpretaded
-and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground accelaration, slope angle, road and fault distance.
+and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road and fault distance.
 Artificial Neural Networks (ANN) were applied for the assessment of susceptibility to
@@
 
-\KW landslide, hazard assessment, El Salvador, ANN, geostatistics.
+\KW landslide, hazard assessment, El Salvador, ANN, geostatistics, Artificial Neural Networks, kriging.
 
@@
 \label{sec:intr}
-El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 kilometers westward from the Gulf of Fonseca to the border with Guatemala (see Fig.
+El Salvador, one of the smallest and most crowded nations in Central America, extends in Pacific coast about 240 km westward from the Gulf of Fonseca to the border with Guatemala (see Fig.
 \ref{fig:mass01}).
@@
 These ranges present several highly active volcanoes.
-The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic crops are located in the northern ranges, in the border with Honduras (\cite{weber}).
+The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic rocks are located in the northern ranges, in the border with Honduras (\cite{weber}).
 Some of the most recent volcanic layers are formed by poor consolidated ashes and tuffs highly erodible (\cite{bommer}).
@@
 
-Like in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poor consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
+As in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poor consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
 This problem is exacerbated by the extreme deforestation and the consequent high level of rates of erosion.
-Poverty, overpopulation and uncontrolled urbanization that characterizes the Salvadoran human settlements converts El Salvador in a country with high landslide risks.
-One example of this high risk is the devastating effect of the Las Colinas landslide triggered by a major earthquake (Mw 7.6) occurred on January of the 13, 2001  in Santa Tecla, a major city located close to San Salvador  the Salvadoran capital (\cite{evans}).
-A huge amount of soil mass (about 200,000 m3) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
-Together with this event this earthquake triggered several landslides along the country, especially in the Metropolitan Area of San Salvador (MASS) (\cite{jibson}).
-Other example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 (\cite{crone}).
+Poverty, overpopulation and uncontrolled urbanization characterize to the Salvadoran human settlements, which makes to El Salvador a country with high landslide risks.
+An example of this high risk was the devastating effect is Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital(\cite{evans}).
+A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
+Together with this event also several landslides ocurred along the country, especially in the Metropolitan Area of San Salvador (MASS) (\cite{jibson}).
+Another example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 (\cite{crone}).
 
 Due to the above it is necessary to implement mechanisms that allow us to quantify the hazard of a given geographic area to landslides, usually this is done with development of susceptibility maps which present in a graphical way the zones more susceptible to landslides and represent a practical tool for urban planning.
-It was proposed an Artificial Neural Network model (ANN) which are a family of statistical learning models inspired by biological neural networks.
+It was proposed an Artificial Neural Network model (ANN) which is a family of statistical learning models inspired by biological neural networks.
 The model proposed is used to estimate the susceptibility to landslide.
@@
    \includegraphics[scale=0.70]{MASS_mapa_1}
-   \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Area Metropolitana de San Salvador (MASS) and topography of MASS.}}
+   \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Metropolitan Area of San Salvador (MASS) and its topography.}}
    \label{fig:mass01}
@@
 Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking (\cite{schmidt1975}).
-Chávez et al.
+Ch\'{a}vez et al.
 (\cite{chavez2014a}) identifies high and moderate erosion hazard in majority of MASS area.
@@
 As Bommer \& Rodriguez (\cite{bommer}) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
-Hernández (\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
+Hern\'{a}ndez (\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
 In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
@@
 \item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.
-The physical properties of slope-forming materials, such as strength and permeability, are related to the lithology factor, which therefore should affect the likelihood of slope failure (\cite{dai2002}).
-This variables was obtained in accordance with the project of national land use plan in El Salvador.
+This variable was obtained in the project of national land use plan in El Salvador.
+It is unpublished geomorphologic cartography in digital format provided by MARN.
+
+%The physical properties of slope-forming materials, such as strength and permeability, are related to the lithology factor, which therefore should affect the likelihood of slope failure (\cite{dai2002}).
 
@@
 \item {\bf Road distance:} Distance in kilometers to the nearest road.
-Road map was obtained from digitalized national cartography from Centro Nacional de Registros de la República de El Salvador (CNR).
+Road map was obtained from digitalized national cartography from Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
 
@@
 The present hazard landslide map is consistent with former landslide hazard maps carried out in the region using approaches conceptually different.
-Fernández-Lavado et al.(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
+Fern\'{a}ndez-Lavado et al.(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
 The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where (\cite{fernan2008}) identifies a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presents a hazard slightly lower.
@@
 \bibitem{garcia2008}
-García-Rodríguez M.J., Malpica J.A., Benito B., Díaz M.
+Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A., Benito B., D\'{i}az M.
 \newblock  Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression.
@@
 \bibitem{garcia2010}
-García-Rodríguez M.J., Malpica J.A.
+Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A.
 \newblock Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model.
@@
 \newblock Evaluation of prediction capability, robustness, and sensitivity in
-  non-linear landslide susceptibility models, guantánamo, cuba.
+  non-linear landslide susceptibility models, guant\'{a}namo, cuba.
 \newblock \emph{Computers {\&} Geosciences}, 37\penalty0 (4):\penalty0 410 --
@@
 Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos
-\newblock VI Censo de Población y V de Vivienda
+\newblock VI Censo de Poblaci\'{o}n y V de Vivienda
 \newblock \emph{2007-2008}.
@@
 Hern\'{a}ndez W.E.
-\newblock Características Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
-\newblock MSc Thesis. Universidad Politécnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
+\newblock Caracter\'{i}sticas Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
+\newblock MSc Thesis. Universidad Polit\'{e}cnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
 \penalty0 2004
@@
 \bibitem{chavez2014b}
-Chávez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). 
+Ch\'{a}vez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). 
 \newblock Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''.
-\newblock \emph{Ingeniería.}
+\newblock \emph{Ingenier\'{i}a.}
 \penalty0  24 (2).53-78.
@@
 \newblock Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits.
-\newblock \emph{Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\newblock \emph{Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
 \penalty0  55-67, 2004.
@@
 \newblock Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption.
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
 \penalty0 237-244., 2004.
@@
 \newblock Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador.
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
 \penalty0 89-108, 2004.
@@
 \newblock Eruptive history and volcanic hazards of Volcan San Salvador. 
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., López D.L., Carr M.J. and Major J.J.}
+\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
 \penalty0 147-158, 2004.
@@
 
-\bibitem{dai2002}
-Dai, F. C. and Lee, C. F.
-\newblock Landslide characteristics and slope instability modeling using GIS, Lantau Island, Hong Kong.
-\newblock \emph{Geomorphology}
-\penalty0 42, 213–228, 2002.
+%\bibitem{dai2002}
+%Dai, F. C. and Lee, C. F.
+%\newblock Landslide characteristics and slope instability modeling using GIS, Lantau Island, Hong Kong.
+%\newblock \emph{Geomorphology}
+%\penalty0 42, 213–228, 2002.
 
 \bibitem{beni2012}
-Benito M.B., Lindholm C., Camacho E., Climent Á., Marroquín G., Molina E.,Rojas W., Escobar J.J., Talavera E., Alvarado G.E. and Torres Y.
+Benito M.B., Lindholm C., Camacho E., Climent \'{A}., Marroqu\'{i}n G., Molina E.,Rojas W., Escobar J.J., Talavera E., Alvarado G.E. and Torres Y.
 \newblock A New Evaluation of Seismic Hazard for the Central America Region. 
@@
 Fernandez-Lavado C., Sanchez A., Amenos M., Barrio J.
-\newblock Caracterización de la susceptibilidad y de la amenaza por movimientos de ladera del Área Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet).
-\newblock \emph{Project IPGARAMSS framework. Geólogos del Mundo. San Salvador, El Salvador.}
+\newblock Caracterizaci\'{o}n de la susceptibilidad y de la amenaza por movimientos de ladera del \'{A}rea Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet).
+\newblock \emph{Project IPGARAMSS framework. Ge\'{o}logos del Mundo. San Salvador, El Salvador.}
 \penalty0 2008.
@@
 SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales
-\newblock Memoria Técnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador.
+\newblock Memoria T\'{e}cnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador.
 \newblock \emph{Ministerio de Ambiente y Recursos Naturales}

### 2015-06-06 paper.tex

@@
 \label{sec:studyarea}
-The Metropolitan Area of San Salvador (MASS), is formed by 14 municipalities among them there is San Salvador, the capital of the country.
-It has 587 km2 and according to the most recent census (\cite{minecon}) it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
-According to geography MASS is extended over a flat erosional surface (650-760 m a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
+MASS, is formed by 14 municipalities among them it is located San Salvador, the capital of the country.
+It has 587 $km^{2}$ and according to the most recent census (\cite{minecon}) it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
+According to geography MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
 MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig.
@@
 during rainy seasons), which results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
-Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercurses are often close to vertical and can reach highs of more than 10 m.
+Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach highs of more than 10 m.
 Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
-As Bommer \& Rodriguez (\cite{bommer}) identify in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
-Hern\'{a}ndez (\cite{hernan2004}) carry out a detailed description of this process in TBJ, where these instabilities are very common.
+As Bommer \& Rodriguez (\cite{bommer}) identified in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
+Hern\'{a}ndez (\cite{hernan2004}) carried out a detailed description of this process in TBJ, where these instabilities are very common.
 In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
@@
 In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS (\cite{major2004}).
-On the other hand one of the most destructive eruption in the world history was 430 A.D.
+On the other hand one of the most destructive eruptions in the world history was 430 A.D.
 TBJ eruption produced by the Ilopango Caldera.
@@
 The Landslide inventory was developed by MARN and it was conducted in two stages.
-The first was carried out, based on fieldwork after the 2001 eartquakes in El Salvador.
-The another stage was completed with a visual inventory of places where there were landslides which were visible in a image of satellite image from IRS-C sensor (Indian) in the same year.
+The first was carried out, based on fieldwork after the 2001 earthquakes in El Salvador.
+The second stage consisted of a visual inventory of places where there were landslides identified through satellite image from IRS-C sensor (Indian) in the same year.
 
@@
 
-Once that the landslide inventory was finished, a percentage of 0.5\% of the total points georeferenced shows landslide ocurrence.
+Once the landslide inventory was finished, a percentage of 0.5\% of the total points georeferenced showed landslide occurrence.
 In addition to the landslide information the following data sources of input variables was provided by MARN:
@@
 \item {\bf Slope:} Slope gradient is an important component and a
-preparatory cause of landsliding (\cite{garcia2008}). It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mts.
+preparatory cause of landsliding (\cite{garcia2008}). It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mt.
 
-\item {\bf Geology:} Description of the geology of the area from the map German Geological Mission (scale 1:100,000) (\cite{weber}).
+\item {\bf Geology:} Description of the geology of the area according digitalized geological map of  El Salvador (scale 1:100,000) (\cite{weber}).
 
 \item {\bf Rainfall intensity:} From the precipitation database compiled by the
-SNET's weather stations for the period 1970–2001, maximum precipitations were obtained, and then was applied interpolation kriging to them.
+MARN's weather stations for the period 1970–2001, maximum precipitations were obtained, 
+and then, a contour map was generated through kriging interpolation method.
 
@@
 \item {\bf Road distance:} Distance in kilometers to the nearest road.
-Road map was obtained from digitalized national cartography from Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
+Road map was obtained from digitalized national cartography created by Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
 
@@
 \section{Artificial Neural Network model for discrete choice}
-The logistic regression is a special case of neural network whose output variable is
-discrete, logistic regression represents a neural network with 
-a neuron in the hidden layer. The following adaptation of a multilayeredfeedforward artificial neural network known as  
-MLP (Multilayer Perceptron) may be used for modeling binary classification model, where $x's$ are the observed values in the input variables, $w's$ and $\lambda's$ are the parameters of the model, $ p_{i} $ is the predicting probability for a network with $ k^{*} $ input characteristics and $ j^{*} $ neurons:
+Logistic regression represents a neural network with 
+a neuron in the hidden layer and whose output is dichotomous.
+The following adapted form of the Multilayer Perceptron (MLP) may be used for modeling binary classification problems.
+In the equation (\ref{eq:ann1}) $x_{k,i}$ are the observed values in the ith input variables belonging to the kth case.
+The expressions $w_{j,k}$ and $\lambda_{j}$ showed in the equations (\ref{eq:ann1}) and (\ref{eq:ann3}) are the parameters of the model.
 
@@
 n_{j,i} = w_{j,0} + \sum_{k=1}^{k^{*}} w_{j,k}x_{k,i}
+\label{eq:ann1}
 \end{equation}
@@
 N_{j,i} = \frac{1}{1+\exp^{-n_{j,i}}}
+\label{eq:ann2}
 \end{equation}
@@
 p_{i} = \sum_{j=1}^{j^{*}} \lambda_{j} N_{j,i}
+\label{eq:ann3}
 \end{equation}
@@
 \sum_{j=1}^{j^{*}} \lambda_{j} = 1 , \lambda_{j} \ge 0
+\label{eq:ann4}
 \end{equation}
 
-In the context of the research problem $p_{i} $ and the number $ k^{*} $ represent 
-probability of landslide ocurrence and the number of input variables or causes associated with landslide ocurrence respectively.
+In the equation (\ref{eq:ann3}) $p_{i}$ is the the predicting probability for a network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
+In the context of the present research, $p_{i} $ represents the probability of landslide ocurrence.
 
@@
 \begin{equation}
-x*_{i} = \frac{x_{i} - \mu }{\sigma}
+z = \frac{x - \bar{x} }{\sigma_{x}}
 \label{eq:scaling}
@@
 
-In the equation (\ref{eq:scaling}) $x*_{i}$ is the new variable transformed with $ \mu $ and $\sigma$ are, respectively the mean and the standard deviation for the ith input variable.
+In the equation (\ref{eq:scaling}) $z$ is the new variable transformed, $ \bar{x} $ and $\sigma_{x}$ are, respectively the mean and the standard deviation of the input variable to transform.
 
@@
 
-Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim function of the R statistical software, to obtain a better estimation of the parameters of the model.
+Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim routine of the R statistical software, to obtain a better estimation of the parameters of the model.
 
 \section{Spatial Prediction}
+
+\subsection*{Estimating spatial correlation}
+
 In standard statistical problems, correlation can be estimated from a scatterplot, when several data pairs ${x, y}$ are available.
@@
 To estimate spatial correlation
-from observational data, we therefore need to make stationarity assumptions
+from observational data, it is necessary to make stationarity assumptions
 before we can make any progress. One commonly used form of stationarity
 is intrinsic stationarity, which assumes that the process that generated the
-samples is a random function $Z(s)$ composed of a mean and residual:
+samples is a random function $Z(s)$ composed of a mean and residual \cite{bivand2008applied}:
 
@@
 
-It is a weighted average of the sample values, and $ \sum_{i=1}^{n} w_{i} = 1 $ to ensure unbiasedness. The $w_{i}$'s are the weights that will be estimated.
-
-Kriging minimizes the mean squared error of prediction
+It is a weighted average of the sample values, and $ \sum_{i=1}^{n} w_{i} = 1 $ to ensure unbiasedness.
+The $w_{i}$'s are the weights that will be estimated.
+Kriging minimizes the mean squared error of prediction \cite{nicolas2015}.
 
@@
 
-In order to make spatial predictions using ordinary kriging, a R script was developed which can be accessed in the following web address:
-
-\url{https://goo.gl/3N8n99}
+%In order to make spatial predictions using ordinary kriging, a R script was developed which can be accessed in the following web address: 
+%
+%\url{https://goo.gl/3N8n99}
 
@@
 
-In order to achieve the above steps a R script was developed which can be downloaded in the following address:
+In order to achieve the above steps a R script was developed. This script can be downloaded in:
 
@@
 
+\bibitem{bivand2008applied}
+Bivand, Roger S and Pebesma, Edzer J and G{\'o}mez-Rubio, Virgilio and Pebesma, Edzer Jan
+\newblock Applied spatial data analysis with R
+\newblock \emph{volume 747248717}
+\penalty0 Springer, 2014.
+
+\bibitem{nicolas2015}
+Nicolas Christou.
+\newblock Ordinary kriging in terms of the covariance function
+\newblock \emph{University of California, Los Angeles}
+\penalty0 [cited 2015 June 04]. Available from http://goo.gl/0J1RkO
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-06-06 paper.tex
06 June 2015 11:00

@@
 
-%\newpage
-
 \selectlanguage{spanish}
@@
 Therefore El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
-There is two main sources of seismic activity, the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs (\cite{dewey}).
+There is two main sources of seismic activity, the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs \cite{dewey}.
 Due this tectonic and volcanic activity El Salvador has rugged relief.
@@
 These ranges present several highly active volcanoes.
-The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic rocks are located in the northern ranges, in the border with Honduras (\cite{weber}).
-Some of the most recent volcanic layers are formed by poor consolidated ashes and tuffs highly erodible (\cite{bommer}).
+The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic rocks are located in the northern ranges, in the border with Honduras \cite{weber}.
+Some of the most recent volcanic layers are formed by poor consolidated ashes and tuffs highly erodible \cite{bommer}.
 
@@
 Poverty, overpopulation and uncontrolled urbanization characterize to the Salvadoran human settlements, which makes to El Salvador a country with high landslide risks.
-An example of this high risk was the devastating effect is Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital(\cite{evans}).
+An example of this high risk was the devastating effect is Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital\cite{evans}.
 A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
-Together with this event also several landslides ocurred along the country, especially in the Metropolitan Area of San Salvador (MASS) (\cite{jibson}).
-Another example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 (\cite{crone}).
+Together with this event also several landslides ocurred along the country, especially in the Metropolitan Area of San Salvador (MASS) \cite{jibson}.
+Another example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 \cite{crone}.
 
@@
  \begin{center}
-%  \begin{figure}[H]
   \begin{figure}
@@
 \label{sec:brief}
-Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
+Since the pioneering work \cite{Carrara1983403}, several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
 
-It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008} ) , neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251} and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
+It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008} ) , neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327} and \cite{Yesilnacar2005251})  and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
-According to (\cite{van2006landslide}) the magnitude of a possible
+According to \cite{van2006landslide} the magnitude of a possible
 slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event.
 Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for detect complex non-linear relationships in large datasets, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
-
-%There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})
-
-%Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
 
@@
 MASS, is formed by 14 municipalities among them it is located San Salvador, the capital of the country.
-It has 587 $km^{2}$ and according to the most recent census (\cite{minecon}) it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
+It has 587 $km^{2}$ and according to the most recent census \cite{minecon} it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
 According to geography MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
@@
 
-All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age (\cite{schmidt1975}).
-The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in majority of MASS with an average thickness of 4 m (\cite{schmidt1975}).
-These are deposits derived mainly from Ilopango caldera eruptions where they present more than 50 m of thickness (\cite{schmidt1975}).
-Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking (\cite{schmidt1975}).
+All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
+The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
+These are deposits derived mainly from Ilopango caldera eruptions where they present more than 50 m of thickness \cite{schmidt1975}.
+Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
 Ch\'{a}vez et al.
-(\cite{chavez2014a}) identifies high and moderate erosion hazard in majority of MASS area.
-The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) (\cite{hernan2004}) present very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
+\cite{chavez2014a} identified high and moderate erosion hazard in majority of MASS area.
+The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) \cite{hernan2004} present very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
 during rainy seasons), which results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
@@
 Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
-As Bommer \& Rodriguez (\cite{bommer}) identified in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
-Hern\'{a}ndez (\cite{hernan2004}) carried out a detailed description of this process in TBJ, where these instabilities are very common.
+As Bommer \& Rodriguez \cite{bommer} identified in Central America, although such slopes may remain stable for years, they may become unstable, abruptly and totally under the action of heavy rainfall or seismic shaking.
+Hern\'{a}ndez \cite{hernan2004} carried out a detailed description of this process in TBJ, where these instabilities are very common.
 In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
 The main fault system is characterized by an east-west trend; this trend is responsible of the steep northern slope of the El Balsamo Range.
-The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting (\cite{schmidt1975}).
+The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting \cite{schmidt1975}.
 However, all the mentioned fault families appear active.
-Thus the several fault systems have developed at different times, but been repeatedly activated (\cite{rymer1987}).
-Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence (\cite{schmidt1975}).
+Thus the several fault systems have developed at different times, but been repeatedly activated \cite{rymer1987}.
+Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence \cite{schmidt1975}.
 Last eruption of San Salvador volcano was 1917.
 The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
-However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield (\cite{sofield2004}).
-In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS (\cite{major2004}).
+However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield \cite{sofield2004}.
+In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS \cite{major2004}.
 On the other hand one of the most destructive eruptions in the world history was 430 A.D.
 TBJ eruption produced by the Ilopango Caldera.
-According to Dull (\cite{dull2004}), that eruption produced total devastation in whole MASS area.
+According to Dull \cite{dull2004}, that eruption produced total devastation in whole MASS area.
 
@@
 The second stage consisted of a visual inventory of places where there were landslides identified through satellite image from IRS-C sensor (Indian) in the same year.
-
-%from photographic analysis on the study area, using aerial photo from MARN which is presented in the Figure \ref{fig:img01}, where white areas represent regions of landslide occurrence which were processed using the software ILWIS.
-
-% \begin{center}
-%  \begin{figure}[H]
-%   \centering
-%   \includegraphics[scale=0.40]{img01}
-%   \caption{\small{Aerial photo of MASS}}
-%   \label{fig:img01}
-%  \end{figure}
-% \end{center}
 
@@
 
-%The physical properties of slope-forming materials, such as strength and permeability, are related to the lithology factor, which therefore should affect the likelihood of slope failure (\cite{dai2002}).
+\item {\bf Slope:} Slope gradient is an important component and a
+preparatory cause of landsliding \cite{garcia2008}. It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mt.
 
-\item {\bf Slope:} Slope gradient is an important component and a
-preparatory cause of landsliding (\cite{garcia2008}). It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mt.
-
-\item {\bf Geology:} Description of the geology of the area according digitalized geological map of  El Salvador (scale 1:100,000) (\cite{weber}).
+\item {\bf Geology:} Description of the geology of the area according digitalized geological map of  El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 \item {\bf Peak ground accelaration:} Maximum ground acceleration expressed in Gal for a return period of 500 years.
-This data was obtained from the evaluation of seismic Hazard in Central America carried out under the framework of RSIS II project (\cite{beni2012}).
+This data was obtained from the evaluation of seismic Hazard in Central America carried out under the framework of RSIS II project \cite{beni2012}.
 
@@
 
-\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from according digitalized geological map of El Salvador (scale 1:100,000) (\cite{weber}).
+\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from according digitalized geological map of El Salvador (scale 1:100,000) \cite{weber}.
 
 \end{enumerate}
-
-%%% We must comment page 12 - 14 from my Master Thesis 
-%%% Valorizar si lo de Redes Neuronales y Predicción Espacial lo ponemos en métodos y materiales
 
@@
 Before estimating the parameters of the neural network model, it is necessary standardize the input variables.
-In particular for classification problems is more suitable to scale inputs to $[-1,1]$ rather than $[0,1]$ (\cite{FAQANN}).
+In particular for classification problems is more suitable to scale inputs to $[-1,1]$ rather than $[0,1]$ \cite{FAQANN}.
 The following scaling was applied to each input variable:
@@
 
-The method used for estimating the parameters of the model was an Hybrid Method (\cite{McNelis2005}): Firstly heuristic genetic algorithm using a package developed in the R statistical software (\cite{rproject}) specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
+The method used for estimating the parameters of the model was an Hybrid Method \cite{McNelis2005}.
+Firstly heuristic genetic algorithm using a package developed in the R statistical software \cite{rproject} specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
 
@@
 The data were randomly divided into three sub-samples, the first was used for the
-estimation of the parameters of the neural network (training set), the second was used for
-choosing the model with more generalization capability (validation set) and the last was
+estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set) and the last was
 used to evaluate how well the model generalize outside of the data set used for estimation (test set).
 
-To determine the number of neurons in the hidden layer was used the method of trial and error, starting with few neurons and increasing progressively the number of neurons in the hidden layer.
+To determine the number of neurons in the hidden layer, the method of trial and error was used, starting with few neurons and increasing progressively the number of neurons in the hidden layer.
 Table \ref{annresults}
@@
 
-The model with 17 neurons in the hidden layer was chosen, after that a logistic regression model was fitted as a basis of comparison.
-Table \ref{logisticresults} presents the logistic regression fits, clearly the logistic regression's performance was lower than the worst neural network model.
+The model with 17 neurons in the hidden layer was chosen because it presents the best performance in the validation set.
+After that a logistic regression model was fitted as a basis of comparison.
+In the Table \ref{logisticresults} is presented logistic regression model results.
+Clearly, neural network model chosen has better performance than logistic regression model.
 
@@
 
-To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging, validation of this results and .
+To generate the map of landslide hazards, the following steps were followed based on geostatistics methodology: Exploratory analysis, Variogram modelling and Spatial prediction using ordinary kriging, validation, and exporting the spatial predictions to raster format.
 
-In order to achieve the above steps a R script was developed. This script can be downloaded in:
+In order to achieve the above steps, an R script was developed. This script can be downloaded in:
 
@@
 
-First of all one thousand fifty georeferenced point with their probability of ocurrence which was calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
-The Exploratory analysis showed the presence of spatial correlation in the data, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect.
+First of all one thousand fifty georeferenced points with their probability of occurrence calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
+The Exploratory analysis showed the presence of spatial correlation, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect.
 
-As regards the estimation of the variogram, the spherical, gaussian and exponential models were fitted but the validation of these models on data that were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since that it showed a $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
-With the exponential model were made spatial predictions on a grid of 1500 $\times$ 1500 and after that, the spatial predictions were exported to Geotiff raster format.
+Regarding variogram estimation the spherical, gaussian and exponential models were proposed.
+The validation of these models on data were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since it had an $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
+Using exponential model, spatial predictions were calculated on a grid of 1500 $\times$ 1500 and exported to Geotiff raster format.
 Finally Geographic Information System (ArcGIS\textregistered \  of ESRI) was used to design the final map (Figure \ref{fig:mass02}).
@@
 According to Fig.
-\ref{fig:mass02} higher probability of landslide occurrence, reaching probability of occurrence values around 0.8, are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
+\ref{fig:mass02} higher probability of landslide occurrence are around 0.8, and are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
 Areas with lower probability but still important, are located in southern and western side of Nejapa Hill, in north-east of the study area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill and, in general in southern side of MASS.
@@
 The study started with the construction of a landslide inventory and analysis of the causal factors related to the occurrences of landslide.
-The problem of modelling landslide generated by different causes is very complex and for this reason the study proved the efficacy of the neural network model with a percentage of correct classification around 80\% against other models such as logistic regression with a percentage of correct classification under 70\%.
+The problem of modeling landslide is very complex and for this reason the study proved the efficacy of the neural network model with a percentage of correct classification around 80\% against other models such as logistic regression with a percentage of correct classification under 70\%.
 
-In the process of estimating the weights of the model an heuristic technique was used to obtain a better solution after that a local search was used.
-It is better than use only backpropagation algorithm or another local search method to estimate weights since that when these are used there is a strong danger of getting stuck in a local minimum rather than a global minimum for a vector of weights.
-
-The problem with the neural network approach is that is difficult to estimate the weights of the model due to intensive computation involved in the present study the estimation of a neural network model takes between 4 and 10 hours for this reason we could not assess the statistical significance of the input variables in the neural network processes using boostrapping.
-For all of the above parallel computing must be used rather than serial computing in estimating weights of neural networks models.
+In the process of estimating the weights of the model, an heuristic technique was used to obtain a better solution after that a local search was used.
+The difficulty of this approach is due to intensive computation involved in the estimation of a neural network model takes between 4 and 10 hours.
+For this reason the statistical significance of the input variables could not be assessed by means boostrapping  (a statistical resampling technique).
+For all of the above parallel computing must be used rather than serial computing to estimate weights of a neural networks models.
 
@@
 
-The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
+The results obtained through geostatistical methodology met the assumptions for kriging method application.
 Final map of landslide probability of occurrence (see Fig.
-\ref{fig:mass02} ) generated by kriging method is the result of multidisciplinary work which implied an intense geological analysis (i.e.
+\ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e.
 MARN inventory of 4792 landslides) together with the use of sophisticated statistical techniques.
@@
    \centering
-   \includegraphics[scale=0.70]{MASS_mapa_2}
-   \caption{\small{Landslide hazard map MASS where is shown the landslide probability of occurrence.}}
+   \includegraphics[scale=0.73]{MASS_mapa_2}
+   \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}
    \label{fig:mass02}
@@
 High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.
-Major et al.(\cite{major2004}) identified in San Salvador volcano that lahars as voluminous as 2 million of $mts^{3}$ can affect large zones of urban areas.
-Southern areas of MASS also implies a high risk because large landslides, similar to Las Colinas landslide which involved a total volume of around 150,000 m3 (\cite{evans}), can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
+Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $mts^{3}$ that can affect large zones of urban areas.
+Southern areas of MASS also implies a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 m3 \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
 
 The present hazard landslide map is consistent with former landslide hazard maps carried out in the region using approaches conceptually different.
-Fern\'{a}ndez-Lavado et al.(\cite{fernan2008}) presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
-The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where (\cite{fernan2008}) identifies a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presents a hazard slightly lower.
-As landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincides with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by (\cite{chavez2014a}).
-There are similarities with susceptibility hazard maps at national scale generated through logistic regression method (\cite{garcia2008}), through artificial neural network method (\cite{garcia2010}) and through Mora-Vahrson method (\cite{snet2004}).
+Fern\'{a}ndez-Lavado et al.\cite{fernan2008} presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
+The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where Fern\'{a}ndez-Lavado et al.
+\cite{fernan2008} identified a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presented a hazard slightly lower.
+As landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincides with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by Ch\'{a}vez et al.
+\cite{chavez2014a}.
+There are similarities with susceptibility hazard maps at national scale generated through logistic regression method \cite{garcia2008}, through artificial neural network method \cite{garcia2010} and through Mora-Vahrson method \cite{snet2004}.
 However the high landslide areas are more extended in these national maps than the present study.
@@
 Other possible explanation can be related to the data, present work was built using a more extended landslide catalog and more updated data (e.g.
-seismic hazard evaluation from Benito et al.\cite{beni2012}) than former works.
+seismic hazard evaluation from Benito et al.
+cite{beni2012} than former works.
 
-Rock falls were not included in the catalog; these were very common during 2001 earthquakes in El Balsamo Range (\cite{jibson}).
+Rock falls were not included in the catalog; these were very common during 2001 earthquakes in El Balsamo Range \cite{jibson}.
 On the other hand, the MASS seismic microzonation of seismic site effects will improve the estimation of peak ground acceleration.
-The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface, additionally, the geometry of the ground surface also may produce amplification (topographic effects) (\cite{aki1993}).
+The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface, additionally, the geometry of the ground surface also may produce amplification (topographic effects) \cite{aki1993}.
 These effects can be important in soft soils close to incised rivers and also in San Salvador volcano, Balsamo ranges and hills.
-Crosta et al.(\cite{crosta2005}) identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
+Crosta et al.
+\cite{crosta2005} identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
 All these variables can improve the predictive ability of the model and surely the likelihood of landslides.
 
-%%%%  Mencionar abajo las limitaciones computacionales y 
-%%%% que no se pudo tomar una muestra mas grande que 1500 
-%%%% para el kriging relacionar con lo del big data que puede ser 
-%%%% linea de investigación
-
-%The results obtained in the geostatistics methodology showed that the spatial the data satisfies the conditions for applying kriging method.
-The map of landslide hazard \ref{fig:img02} was generated by kriging method and can be used by non-experts in the landslide phenomenon for many purposes such as territorial planning, prevention and mitigation of natural dissasters and so on.
-%
-%Other important variables could not be obtained such as landslide types (Rockfalls, Topples, Slides, etc) and temporal information which can improve the predictive ability of the model.
-
 \section{Acknowledgment}   
-The authors are indebted with MARN who provided the data and Geogrphic Information System software such as ILWIS and ArcGIS\textregistered \  of ESRI.
+The authors are indebted with MARN who provided the data and Geographic Information System software such as ILWIS and ArcGIS\textregistered \  of ESRI.
 
@@
 
-%\bibitem[Carrara(1983)]{Carrara1983403}
 \bibitem{Carrara1983403}
@@
 \newblock \emph{Journal of the International Association for Mathematical
-  Geology}, 15\penalty0 (3):\penalty0 403--426, 1983.
+  Geology.}, 15\penalty0 (3):\penalty0 403--426, 1983.
 \newblock ISSN 0020-5958.
-%\newblock \doi{10.1007/BF01031290}.
-\newblock URL \url{http://dx.doi.org/10.1007/BF01031290}.
 
-%\bibitem[Capparelli and P.~Versace(2013)]{hessd-10-12643-2013}
 \bibitem{hessd-10-12643-2013}
@@
   (10):\penalty0 12643--12662, 2013.
-%\newblock \doi{10.5194/hessd-10-12643-2013}.
-\newblock URL
-  \url{http://www.hydrol-earth-syst-sci-discuss.net/10/12643/2013/}.
 
-%\bibitem[Pradhan et~al.(2010)Pradhan, Oh, and
-%  Buchroithner]{doi:10.1080/19475705.2010.498151}
 \bibitem{doi:10.1080/19475705.2010.498151}
@@
   199--223, 2010.
-%\newblock \doi{10.1080/19475705.2010.498151}.
-\newblock URL
-  \url{http://www.tandfonline.com/doi/abs/10.1080/19475705.2010.498151}.
 
-%\bibitem[Neuhäuser et~al.(2012)Neuhäuser, Damm, and Terhorst]{Neu2012511}
 \bibitem{Neu2012511}
-Bettina Neuhäuser, Bodo Damm, and Birgit Terhorst.
+Bettina Neuh\"auser, Bodo Damm, and Birgit Terhorst.
 \newblock Gis-based assessment of landslide susceptibility on the base of the
@@
 \newblock ISSN 1612-510X.
-%\newblock \doi{10.1007/s10346-011-0305-5}.
-\newblock URL \url{http://dx.doi.org/10.1007/s10346-011-0305-5}.
 
-%\bibitem[Bernknopf and Shapiro(1988)]{Bern198839}
 \bibitem{Bern198839}
@@
 
-%\bibitem[Chung and Fabbri(2003)]{Chung2003451}
 \bibitem{Chung2003451}
@@
 \newblock ISSN 0921-030X.
-%\newblock \doi{10.1023/B:NHAZ.0000007172.62651.2b}.
-\newblock URL \url{http://dx.doi.org/10.1023/B\%3ANHAZ.0000007172.62651.2b}.
+\newblock doi:{10.1023/B:NHAZ.0000007172.62651.2b}.
 
-%\bibitem[Lee et~al.(2004)Lee, Choi, and Min]{doi:10.1080/01431160310001618734}
 \bibitem{doi:10.1080/01431160310001618734}
@@
   (11):\penalty0 2037--2052, 2004.
-%\newblock \doi{10.1080/01431160310001618734}.
-\newblock URL
-  \url{http://www.tandfonline.com/doi/abs/10.1080/01431160310001618734}.
 
@@
 \newblock \emph{Landslides},
-  (11):\penalty0 9, 1, 93--106, 2012
+  (11):\penalty0 9, 1, 93--106, 2012.
 \newblock Springer.
@@
 \newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
-\newblock URL
-  \url{http://www.imagin.org/awards/sppc/2015/papers/jacob_gaskill_paper.pdf}.
 
@@
 
-%\bibitem[Melchiorre et~al.(2011)Melchiorre, Abella, van Westen, and
-%  Matteucci]{Melchiorre2011410}
 \bibitem{Melchiorre2011410}
@@
 \newblock ISSN 0098-3004.
-%\newblock \doi{http://dx.doi.org/10.1016/j.cageo.2010.10.004}.
-\newblock URL
-  \url{http://www.sciencedirect.com/science/article/pii/S0098300410003286}.
 
-%\bibitem[Zeng-wang(2001)]{Zeng2001374}
 \bibitem{Zeng2001374}
@@
 \newblock ISSN 1009-637X.
-%\newblock \doi{10.1007/BF02892323}.
-\newblock URL \url{http://dx.doi.org/10.1007/BF02892323}.
+\newblock doi:{10.1007/BF02892323}.
 
-%\bibitem[Erm(2005)]{Ermini2005327}
 \bibitem{Ermini2005327}
@@
 \newblock ISSN 0169-555X
-%\newblock \doi{http://dx.doi.org/10.1016/j.geomorph.2004.09.025}.
-\newblock URL \url{http://www.sciencedirect.com/science/article/pii/S0169555X04002272}.
+\newblock doi:10.1016/j.geomorph.2004.09.025.
 
@@
 \newblock ISSN 0013-7952,
-%\newblock \doi{10.1080/01431160310001618734}.
-\newblock URL
-  \url{http://www.sciencedirect.com/science/article/pii/S0013795205000384}.
+\newblock doi:10.1080/01431160310001618734.
 
@@
 
-%%%%%%%%%%%%%%  Study Area %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibitem{minecon}
@@
 \penalty0 71,1323–1354, 2014.
-\newblock DOI 10.1007/s11069-013-0948-8.
+\newblock doi:10.1007/s11069-013-0948-8.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%   Landslide inventory and data sources of input variables                        %%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\bibitem{dai2002}
-%Dai, F. C. and Lee, C. F.
-%\newblock Landslide characteristics and slope instability modeling using GIS, Lantau Island, Hong Kong.
-%\newblock \emph{Geomorphology}
-%\penalty0 42, 213–228, 2002.
-
 \bibitem{beni2012}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibitem{FAQANN}
 Warren S. Sarle
-\newblock URL
-  \url{ftp://ftp.sas.com/pub/neural/FAQ.html#questions}.
-  \newblock Accessed 31 May, 2015.
+\newblock  [cited 2014 January 10]. Available from http://goo.gl/k8fKhM
 
@@
 \newblock ISBN 9780124859678,
-%\newblock \doi{http://dx.doi.org/10.1016/B978-012485967-8.50003-8}.
-\newblock URL
-  \url{http://www.sciencedirect.com/science/article/pii/B9780124859678500038}.
+\newblock doi:10.1016/B978-012485967-8.50003-8.
 
@@
 \penalty0 [cited 2015 June 04]. Available from http://goo.gl/0J1RkO
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%  Discussion  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{thebibliography}

### 2015-06-06 paper.tex
06 June 2015 11:05

@@
 
-%In order to make spatial predictions using ordinary kriging, a R script was developed which can be accessed in the following web address: 
-%
-%\url{https://goo.gl/3N8n99}
-
 \section{Results}
-%\subsection*{Data Partition}
 The data were randomly divided into three sub-samples, the first was used for the
@@
 
-% Falta poner que despues de pasarlo al geotiff se utilizo el software 
-% ILWIS o el que se tuvo que usar y que posteriormente se genero el 
-% map of landslide hazard mostrado en la figura  
-% valorizar si se pone el codigo fuente
-
-%The map of landslide hazards is showed in the figure \ref{fig:img02}.
-%
-% \begin{center}
-%  \begin{figure}[H]
-%   \centering
-%   \includegraphics[scale=0.40]{img02}
-%   \caption{\small{Map of landslide hazards}}
-%   \label{fig:img02}
-%  \end{figure}
-% \end{center}
-
 \section{Discussion and conclusions}
@@
 
-%%% Alex's Discussion
-
 The results obtained through geostatistical methodology met the assumptions for kriging method application.
@@
 \begin{center}
-%  \begin{figure}[H]
   \begin{figure}

### 2015-06-08 paper.tex
07 June 2015 20:24

@@
 Esta contribuci\'{o}n describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para el \'{A}rea Metropolitana de San Salvador, departamento de El Salvador.
-El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) con un total de 939407 puntos georeferenciados con el fin de producir un inventario de deslizamiento.
-En esta evaluaci\'{o}n de los deslizamientos se uso 4792 eventos previamente foto-interpretados y 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
+El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) en donde 4792 deslizamientos fueron identificados y georeferenciados junto con 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
 Redes Neuronales Artificiales (RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los par\'{a}metros del modelo.
@@
 assessment model for San Salvador, department in El Salvador.
-The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym)  with a total amount of 939407 georeferenced points to produce a landslide inventory.
-In this
-landslide assessment we have used 4792 events previously photo-interpretaded
-and 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road and fault distance.
+The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym) where 4792 landslides were identified and georeferenced
+along with 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road and fault distance.
 Artificial Neural Networks (ANN) were applied for the assessment of susceptibility to
@@
 \label{sec:landsinvet}
-The Landslide inventory was developed by MARN and it was conducted in two stages.
+The Landslide inventory was developed by Ministry of Environment and Natural Resources (MARN Spanish acronym) and it was conducted in two stages.
 The first was carried out, based on fieldwork after the 2001 earthquakes in El Salvador.
@@
 
-Once the landslide inventory was finished, a percentage of 0.5\% of the total points georeferenced showed landslide occurrence.
+Once the landslide inventory was finished, 4792 landslides were identified which represent the 0.5\% of the total points georeferenced.
 In addition to the landslide information the following data sources of input variables was provided by MARN:
@@
 \item {\bf Slope:} Slope gradient is an important component and a
-preparatory cause of landsliding \cite{garcia2008}. It was calculated from digital elevation model (DEM) provided by MARN with a resolution of 10 mt.
+preparatory cause of landsliding \cite{garcia2008}. It was calculated from digital elevation model (DEM) provided by MARN (scale 1:100,000).
 
@@
 High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.
-Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $mts^{3}$ that can affect large zones of urban areas.
+Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $m^{3}$ that can affect large zones of urban areas.
 Southern areas of MASS also implies a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 m3 \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
@@
 seismic hazard evaluation from Benito et al.
-cite{beni2012} than former works.
+\cite{beni2012} than former works.
 

### 2015-06-08 paper.tex
08 June 2015 16:14

@@
 El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) en donde 4792 deslizamientos fueron identificados y georeferenciados junto con 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
-Redes Neuronales Artificiales (RNA) fueron usadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los par\'{a}metros del modelo.
-Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior que el de RNA con un porcentaje de correcta clasificaci\'{o}n abajo del 70\%.
+Redes Neuronales Artificiales (RNA) fueron utilizadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los par\'{a}metros del modelo.
+Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior.
 Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo kriging proveniente del enfoque geoestad\'{i}stico.
@@
 The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym) where 4792 landslides were identified and georeferenced
-along with 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road and fault distance.
-Artificial Neural Networks (ANN) were applied for the assessment of susceptibility to
-landslides, achieving more than 80\% of landslide were properly classified using
+along with 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road, and fault distance.
+Artificial Neural Networks (ANN) were for utilized to assess the susceptibility to
+landslides, achieving results where more than 80\% of landslide were properly classified using
 in-sample and out of sample criteria. Logistic regression was used as base of
-comparison, obtaining this model a performance lower than ANNs with a percentage of correct classification under 70\%. To complete the analysis we have
+comparison. Logistic regression obtained a performance lower. To complete the analysis we have
 performed interpolation of the points using kriging method from geostatistical
@@
 Therefore El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
-There is two main sources of seismic activity, the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs \cite{dewey}.
+There are two main sources of seismic activity: the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs \cite{dewey}.
 Due this tectonic and volcanic activity El Salvador has rugged relief.
-The main ranges cross the country with a rough west-east trend, parallel to the coast, these are separated from each other by faults and grabens.
+The main ranges cross the country with a rough west-east trend, parallel to the coastline.
+These are separated from each other by faults and grabens.
 These ranges present several highly active volcanoes.
-The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks, only sparse outcrops of sedimentary and plutonic rocks are located in the northern ranges, in the border with Honduras \cite{weber}.
-Some of the most recent volcanic layers are formed by poor consolidated ashes and tuffs highly erodible \cite{bommer}.
+The surface geology in El Salvador is almost entirely volcanic, dominated by upper Tertiary to Holocene volcanic rocks.
+Only sparse outcrops of sedimentary and plutonic rocks are located in the northern ranges, in the border with Honduras \cite{weber}.
+Some of the most recent volcanic layers are formed by poorly consolidated ashes and highly erodible tuffs \cite{bommer}.
 
-Throughout the year the country experiences a tropical climate with two seasons, a dry season (November to April) and wet season (May - October).
+Throughout the year the country experiences a tropical climate with two seasons, a dry season (November to April) and wet seasons (May - October).
 The climate of El Salvador is generally warm.
-In the dry season there is very less rainfall but during rainy seasons heavy showers take place.
+In the dry season there is very little rainfall but during rainy seasons heavy showers take place.
 Periodically El Salvador is affected by tropical storms and occasionally by hurricanes.
 
-As in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poor consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
+As in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poorly consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
 This problem is exacerbated by the extreme deforestation and the consequent high level of rates of erosion.
-Poverty, overpopulation and uncontrolled urbanization characterize to the Salvadoran human settlements, which makes to El Salvador a country with high landslide risks.
-An example of this high risk was the devastating effect is Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital\cite{evans}.
+Poverty, overpopulation and uncontrolled urbanization characterize the Salvadoran human settlements, which makes El Salvador a country with high landslide risks.
+An example of this high risk was the devastating effect of Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital\cite{evans}.
 A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
@@
 
-Due to the above it is necessary to implement mechanisms that allow us to quantify the hazard of a given geographic area to landslides, usually this is done with development of susceptibility maps which present in a graphical way the zones more susceptible to landslides and represent a practical tool for urban planning.
-It was proposed an Artificial Neural Network model (ANN) which is a family of statistical learning models inspired by biological neural networks.
+Due to the above, it is necessary to implement mechanisms that allow us to quantify the hazard of a given geographic area to landslides.
+Usually this is done with development of susceptibility maps which present in a graphical way the zones more susceptible to landslides and represent a practical tool for urban planning.
+We propose an Artificial Neural Network model (ANN), which is a family of statistical learning models inspired by biological neural networks.
 The model proposed is used to estimate the susceptibility to landslide.
@@
 \label{sec:brief}
-Since the pioneering work \cite{Carrara1983403}, several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
+Since the pioneering work shown in \cite{Carrara1983403}, several mathematical and statistical models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}) and probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
 
-It has been used popular classification models such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008} ) , neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327} and \cite{Yesilnacar2005251})  and support vector machine (\cite{ballabio2012support} and \cite{tien2012landslide}).
+Popular classification models have been used such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008}) , neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327} and \cite{Yesilnacar2005251})  and support vector machines (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
-According to \cite{van2006landslide} the magnitude of a possible
+According to \cite{van2006landslide}, the magnitude of a possible
 slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event.
-Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for detect complex non-linear relationships in large datasets, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
+Because of these complex relationships between the dependent variable and causal factors, and since neural networks are particularly useful for complex non-linear relationships in large datasets, despite the disadvantages such as greater computational burden.
 
@@
 \label{sec:studyarea}
-MASS, is formed by 14 municipalities among them it is located San Salvador, the capital of the country.
+MASS is formed by 14 municipalities among them is located San Salvador, the capital of the country.
 It has 587 $km^{2}$ and according to the most recent census \cite{minecon} it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
-According to geography MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
-MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and with Mariona Hills (refer to Fig.
+MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
+MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and Mariona Hills (refer to Fig.
 \ref{fig:mass01}).
-Human settlement is not only restricted to the plain, but spreads up to surrounding heights and volcano flanks.
+Human settlement is not restricted to the plain, spreads up to surrounding heights and volcano flanks.
 
@@
 Ch\'{a}vez et al.
-\cite{chavez2014a} identified high and moderate erosion hazard in majority of MASS area.
-The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) \cite{hernan2004} present very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
-during rainy seasons), which results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
+\cite{chavez2014a} identified high and moderate erosion hazard in the majority of MASS area.
+The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) \cite{hernan2004} presents very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
+during rainy seasons), results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
 Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach highs of more than 10 m.
@@
 In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
-The main fault system is characterized by an east-west trend; this trend is responsible of the steep northern slope of the El Balsamo Range.
+The main fault system is characterized by an east-west trend; this trend is responsible the steep northern slope of the El Balsamo Range.
 The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting \cite{schmidt1975}.
@@
 Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence \cite{schmidt1975}.
-Last eruption of San Salvador volcano was 1917.
+Last eruption of San Salvador volcano was in 1917.
 The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
 However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield \cite{sofield2004}.
-In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side present a high lahar hazard that threats MASS \cite{major2004}.
+In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side presents a high lahar hazard that threats MASS \cite{major2004}.
 On the other hand one of the most destructive eruptions in the world history was 430 A.D.
@@
 The first was carried out, based on fieldwork after the 2001 earthquakes in El Salvador.
-The second stage consisted of a visual inventory of places where there were landslides identified through satellite image from IRS-C sensor (Indian) in the same year.
+The second stage consisted of a visual inventory of places where identified through satellite image from IRS-C sensor (Indian) in the same year.
 
-Once the landslide inventory was finished, 4792 landslides were identified which represent the 0.5\% of the total points georeferenced.
-In addition to the landslide information the following data sources of input variables was provided by MARN:
+Once the landslide inventory was finished, 4792 landslides were identified, 0.5\% of the total points georeferenced.
+In addition to the landslide information, the following data sources of input variables was provided by MARN:
 
 \begin{enumerate}
-\item {\bf Geomorphology:} refers to landforms that result from lithospheric dynamics of geographic area.
+\item {\bf Geomorphology:} it means landforms that result from lithospheric dynamics of geographic area.
 This variable was obtained in the project of national land use plan in El Salvador.
@@
 
-\item {\bf Geology:} Description of the geology of the area according digitalized geological map of  El Salvador (scale 1:100,000) \cite{weber}.
+\item {\bf Geology:} Description of the geology of the area, geological map of  El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 
-\item {\bf Road distance:} Distance in kilometers to the nearest road.
-Road map was obtained from digitalized national cartography created by Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
+\item {\bf Road distance:} Distance in kilometers to the nearest road. Road map was obtained from national cartography created by Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
 
-\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from according digitalized geological map of El Salvador (scale 1:100,000) \cite{weber}.
+\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from geological map of El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 Logistic regression represents a neural network with 
-a neuron in the hidden layer and whose output is dichotomous.
+a neuron in the hidden layer whose output is dichotomous.
 The following adapted form of the Multilayer Perceptron (MLP) may be used for modeling binary classification problems.
@@
 
-Before estimating the parameters of the neural network model, it is necessary standardize the input variables.
+Before estimating the parameters of the neural network model, it is necessary to standardize the input variables.
 In particular for classification problems is more suitable to scale inputs to $[-1,1]$ rather than $[0,1]$ \cite{FAQANN}.
@@
 
-In the equation (\ref{eq:scaling}) $z$ is the new variable transformed, $ \bar{x} $ and $\sigma_{x}$ are, respectively the mean and the standard deviation of the input variable to transform.
+In the equation (\ref{eq:scaling}) $z$ is the new variable transformed, $ \bar{x} $ and $\sigma_{x}$ the mean and the standard deviation of the input variable to transform.
 
 The method used for estimating the parameters of the model was an Hybrid Method \cite{McNelis2005}.
-Firstly heuristic genetic algorithm using a package developed in the R statistical software \cite{rproject} specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
-
-The R package can be accessed from the following web address:
+Using a package developed in the R statistical software \cite{rproject} specifically developed to obtain a good estimation of the parameters of the neural network model .
+The R package can be accessed from the following Web address:
 
 \url{https://goo.gl/PHaaG2}
-
-Once a good estimate was obtained, this was occupied as the initial values for the conjugate gradient method implemented in the optim routine of the R statistical software, to obtain a better estimation of the parameters of the model.
 
@@
 In standard statistical problems, correlation can be estimated from a scatterplot, when several data pairs ${x, y}$ are available.
-The spatial correlation between two observations of a variable $z(s)$ at locations $s_{1}$ and $s_{2}$ cannot be estimated, as only a single pair is available.
+The spatial correlation between two observations of a variable $z(s)$ at locations $s_{1}$ and $s_{2}$ cannot be estimated, only a single pair is available.
 To estimate spatial correlation
@@
 The $w_{i}$'s are the weights that will be estimated.
-Kriging minimizes the mean squared error of prediction \cite{nicolas2015}.
+Kriging minimizes the expression (\ref{eq:meankrige}) which is the mean squared error of prediction \cite{nicolas2015}.
 
 \begin{equation}
-min \ \sigma_{e}^{2} = E\left[Z(s_{0}) - \hat{Z(s_{0})}\right]^{2}
+ E\left[Z(s_{0}) - \hat{Z(s_{0})}\right]^{2}
+\label{eq:meankrige}
 \end{equation}
@@
 \section{Results}
-The data were randomly divided into three sub-samples, the first was used for the
-estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set) and the last was
-used to evaluate how well the model generalize outside of the data set used for estimation (test set).
+The data were randomly divided into three sub-samples. The first was used for the
+estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set), and the last was
+used to evaluate how well the model is able to generalize data not used in the estimation process (test set).
 
@@
 \begin{table}[H]
-\caption{Summary of classification accuracy on the training, validation and test sets for neural network models  }
+\caption{Summary of classification accuracy on the training, validation, and test sets for neural network models  }
 \label{annresults}

### 2015-06-09 paper.tex
09 June 2015 12:56 Finally Version

@@
 
-Throughout the year the country experiences a tropical climate with two seasons, a dry season (November to April) and wet seasons (May - October).
+Throughout the year the country experiences a tropical climate with two seasons: a dry season (November to April) and wet season (May - October).
 The climate of El Salvador is generally warm.
@@
 \label{sec:brief}
-Since the pioneering work shown in \cite{Carrara1983403}, several mathematical and statistical models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}) and probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).
+Since the pioneering work shown in \cite{Carrara1983403}, several mathematical and statistical models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151}, and \cite{Neu2012511}) and probabilistic models (\cite{Bern198839}, \cite{Chung2003451}, and \cite{doi:10.1080/01431160310001618734}).
 
-Popular classification models have been used such as logistic regression (\cite{akgun2012} and \cite{gaskill} and \cite{garcia2008}) , neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327} and \cite{Yesilnacar2005251})  and support vector machines (\cite{ballabio2012support} and \cite{tien2012landslide}).
+Popular classification models have been used such as logistic regression (\cite{akgun2012}, \cite{gaskill}, and \cite{garcia2008}), neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}, and \cite{Yesilnacar2005251}), and support vector machines (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
@@
 slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event.
-Because of these complex relationships between the dependent variable and causal factors, and since neural networks are particularly useful for complex non-linear relationships in large datasets, despite the disadvantages such as greater computational burden.
+Because of these complex relationships between the dependent variable and causal factors, and since neural networks are particularly useful for detecting complex non-linear relationships in large datasets, we chose this kind of model, despite the disadvantages such as greater computational burden and tendency to overfit.
 
@@
 It has 587 $km^{2}$ and according to the most recent census \cite{minecon} it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
-MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
+Geographically, MASS is extended over a flat erosional surface (650-760 m.a.s.l.), gently sloping to the east towards Ilopango Caldera also known as Ilopango Lake.
 MASS is bordered to the south by the Balsamo Range and San Jacinto Hill, to the west by San Salvador volcano and Mariona Hills (refer to Fig.
 \ref{fig:mass01}).
-Human settlement is not restricted to the plain, spreads up to surrounding heights and volcano flanks.
+Human settlement is not restricted to the plain and it spreads up to surrounding heights and volcano flanks.
 
 All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
-The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
-These are deposits derived mainly from Ilopango caldera eruptions where they present more than 50 m of thickness \cite{schmidt1975}.
+The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in the majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
+These are deposits derived mainly from Ilopango caldera eruptions where they are more than 50 m of thick \cite{schmidt1975}.
 Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
@@
 The more recent layer Tierra Blanca, known as Tierra Blanca Joven (TBJ) \cite{hernan2004} presents very poor geotechnical properties, especially when there is an increment of soil moisture (i.e.
-during rainy seasons), results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
-Several incised rivers and ravines cross MASS area, due the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach highs of more than 10 m.
+during rainy seasons).
+This results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
+Several incised rivers and ravines cross MASS area.
+Due to the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach highs of over 10 m.
 Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
@@
 Hern\'{a}ndez \cite{hernan2004} carried out a detailed description of this process in TBJ, where these instabilities are very common.
-In study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
-The main fault system is characterized by an east-west trend; this trend is responsible the steep northern slope of the El Balsamo Range.
+In the study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
+The main fault system is characterized by an east-west trend; this trend is responsible for the steep northern slope of the El Balsamo Range.
 The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting \cite{schmidt1975}.
@@
 Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence \cite{schmidt1975}.
-Last eruption of San Salvador volcano was in 1917.
+The Last eruption of San Salvador volcano was in 1917.
 The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
@@
 The first was carried out, based on fieldwork after the 2001 earthquakes in El Salvador.
-The second stage consisted of a visual inventory of places where identified through satellite image from IRS-C sensor (Indian) in the same year.
+The second stage consisted of a visual inventory of places where landslides were identified through satellite image from IRS-C sensor (Indian) in the same year.
 
@@
 \begin{enumerate}
-\item {\bf Geomorphology:} it means landforms that result from lithospheric dynamics of geographic area.
+\item {\bf Geomorphology:} Refers to landforms that result from lithospheric dynamics of geographic area.
 This variable was obtained in the project of national land use plan in El Salvador.
@@
 
-\item {\bf Geology:} Description of the geology of the area, geological map of  El Salvador (scale 1:100,000) \cite{weber}.
+\item {\bf Geology:} Description of the geology of the area according to digital geological map of  El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 
-\item {\bf Road distance:} Distance in kilometers to the nearest road. Road map was obtained from national cartography created by Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
+\item {\bf Road distance:} Distance in kilometers to the nearest road. Road map was obtained from digital national map created by Centro Nacional de Registros de la Rep\'{u}blica de El Salvador (CNR).
 
-\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from geological map of El Salvador (scale 1:100,000) \cite{weber}.
+\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from the according digital geological map of El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 Logistic regression represents a neural network with 
-a neuron in the hidden layer whose output is dichotomous.
+a neuron in the hidden layer, whose output is dichotomous.
 The following adapted form of the Multilayer Perceptron (MLP) may be used for modeling binary classification problems.
-In the equation (\ref{eq:ann1}) $x_{k,i}$ are the observed values in the ith input variables belonging to the kth case.
+In the equation (\ref{eq:ann1}) $x_{k,i}$ are the observed values in the $i$th input variables belonging to the $k$th case.
 The expressions $w_{j,k}$ and $\lambda_{j}$ showed in the equations (\ref{eq:ann1}) and (\ref{eq:ann3}) are the parameters of the model.
@@
 In the equation (\ref{eq:ann3}) $p_{i}$ is the the predicting probability for a network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
-In the context of the present research, $p_{i} $ represents the probability of landslide ocurrence.
+In the context of the present paper, $p_{i} $ represents the probability of landslide ocurrence.
 
@@
 
-In the equation (\ref{eq:scaling}) $z$ is the new variable transformed, $ \bar{x} $ and $\sigma_{x}$ the mean and the standard deviation of the input variable to transform.
+In the equation (\ref{eq:scaling}) $z$ is the new variable transformed. $ \bar{x} $ and $\sigma_{x}$ are the mean and the standard deviation of the input variable to transform, respectively.
 
 The method used for estimating the parameters of the model was an Hybrid Method \cite{McNelis2005}.
-Using a package developed in the R statistical software \cite{rproject} specifically developed to obtain a good estimation of the parameters of the neural network model .
+Firstly, a heuristic genetic algorithm, using a package developed in the R statistical software \cite{rproject} specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
 The R package can be accessed from the following Web address:
@@
 \url{https://goo.gl/PHaaG2}
+
+Once a good estimate was obtained, this was used as the initial guess value for the conjugate gradient method implemented in the R statistical software (optim function), to obtain a better estimation of the parameters of the model.
 
@@
 In standard statistical problems, correlation can be estimated from a scatterplot, when several data pairs ${x, y}$ are available.
-The spatial correlation between two observations of a variable $z(s)$ at locations $s_{1}$ and $s_{2}$ cannot be estimated, only a single pair is available.
+The spatial correlation between two observations of a variable $z(s)$ at locations $s_{1}$ and $s_{2}$ cannot be estimated because only a single pair is available.
 To estimate spatial correlation
@@
 \begin{equation}
- E\left[Z(s_{0}) - \hat{Z(s_{0})}\right]^{2}
+\min \sigma^{2}_{e} = E\left[Z(s_{0}) - \hat{Z(s_{0})}\right]^{2}
 \label{eq:meankrige}
@@
 \section{Results}
-The data were randomly divided into three sub-samples. The first was used for the
+The data were randomly divided into three sub-samples: The first was used for the
 estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set), and the last was
@@
 Table \ref{annresults}
-summarizes how well the models fit on the training, validation and test sets.
+summarizes how well the models fit on the training, validation, and test sets.
 
@@
 
-The model with 17 neurons in the hidden layer was chosen because it presents the best performance in the validation set.
+The model with 17 neurons in the hidden layer was chosen because it had the best performance in the validation set.
 After that a logistic regression model was fitted as a basis of comparison.
-In the Table \ref{logisticresults} is presented logistic regression model results.
-Clearly, neural network model chosen has better performance than logistic regression model.
+Table \ref{logisticresults} shows logistic regression results.
+Clearly, the neural network model chosen has better performance than the logistic regression model.
 
@@
 
-In order to achieve the above steps, an R script was developed. This script can be downloaded in:
+Developed to perform the previous steps, an R script was developed. This script can be downloaded in:
 
@@
 
-First of all one thousand fifty georeferenced points with their probability of occurrence calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
-The Exploratory analysis showed the presence of spatial correlation, this was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance, also the data did not show the presence of anisotropic effect.
+First of all, one thousand fifty georeferenced points with their probability of occurrence calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
+The Exploratory analysis showed the presence of spatial correlation.
+This was done making scatter plot of pairs $Z(s_{i})$ and  $Z(s_{j})$, grouped according to their separation distance.
+Furthermore, the data did not show the presence of anisotropic effect.
 
-Regarding variogram estimation the spherical, gaussian and exponential models were proposed.
-The validation of these models on data were not taken into account in the process of estimating the variogram showed that the best model was the exponential, since it had an $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian respectively.
+Regarding variogram estimation, the spherical, gaussian and exponential models were proposed.
+Using cross-validation methodology, the best model was the exponential, since it had an $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian, respectively.
 Using exponential model, spatial predictions were calculated on a grid of 1500 $\times$ 1500 and exported to Geotiff raster format.
-Finally Geographic Information System (ArcGIS\textregistered \  of ESRI) was used to design the final map (Figure \ref{fig:mass02}).
+Finally, Geographic Information System (ArcGIS\textregistered \  of ESRI) was used to design the final map (Figure \ref{fig:mass02}).
 This map (Fig.
@@
 According to Fig.
-\ref{fig:mass02} higher probability of landslide occurrence are around 0.8, and are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
-Areas with lower probability but still important, are located in southern and western side of Nejapa Hill, in north-east of the study area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill and, in general in southern side of MASS.
+\ref{fig:mass02} higher probability of landslide occurrence are around 0.8.
+These are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
+Areas with lower probability, but still important, are located in southern and western side of Nejapa Hill, in north-east of the studied area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill, and in general in southern side of MASS.
 
@@
 
-In the process of estimating the weights of the model, an heuristic technique was used to obtain a better solution after that a local search was used.
-The difficulty of this approach is due to intensive computation involved in the estimation of a neural network model takes between 4 and 10 hours.
-For this reason the statistical significance of the input variables could not be assessed by means boostrapping  (a statistical resampling technique).
-For all of the above parallel computing must be used rather than serial computing to estimate weights of a neural networks models.
+In the process of estimating the weights of the model, a heuristic technique was used to obtain a better solution after a local search was used.
+The difficulty of this approach is due to the intensive computation involved in the estimation of a neural network model, which takes between 4 and 10 hours.
+For this reason the statistical significance of the input variables could not be assessed by means of bootstrapping (a statistical resampling technique).
+For all of the above, parallel computing must be used rather than serial computing to estimate weights of the neural networks models.
 
@@
 \ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e.
-MARN inventory of 4792 landslides) together with the use of sophisticated statistical techniques.
+MARN inventory of 4792 landslides), together with the use of sophisticated statistical techniques.
 This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on.
@@
  \end{center}
-High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials.
+High probability of landslide occurrence in Picacho slope implies very high risk due to the proximity of urban areas and due to the large volume of mobilized materials.
 Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $m^{3}$ that can affect large zones of urban areas.
-Southern areas of MASS also implies a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 m3 \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
+Southern areas of MASS also have a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
 
@@
 Fern\'{a}ndez-Lavado et al.\cite{fernan2008} presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
-The only differences are located mainly in the Nejapa Hill, San Jacinto Hill where Fern\'{a}ndez-Lavado et al.
+The only differences are located mainly in the Nejapa Hill and San Jacinto Hill where Fern\'{a}ndez-Lavado et al.
 \cite{fernan2008} identified a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presented a hazard slightly lower.
-As landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincides with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by Ch\'{a}vez et al.
+Since landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincide with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by Ch\'{a}vez et al.
 \cite{chavez2014a}.
-There are similarities with susceptibility hazard maps at national scale generated through logistic regression method \cite{garcia2008}, through artificial neural network method \cite{garcia2010} and through Mora-Vahrson method \cite{snet2004}.
+There are similarities with susceptibility hazard maps at national scale generated through logistic regression method \cite{garcia2008}, through artificial neural network method \cite{garcia2010}, and through Mora-Vahrson method \cite{snet2004}.
 However the high landslide areas are more extended in these national maps than the present study.
-These differences could be explained by the working scale, our map is more detailed because is at regional scale.
-Other possible explanation can be related to the data, present work was built using a more extended landslide catalog and more updated data (e.g.
+These differences could be explained by the working scale.
+Our map is more detailed because is at regional scale.
+Other possible explanation can be related to the data.
+Present work was built using a more extended landslide catalog and more up-to-date data (e.g.
 seismic hazard evaluation from Benito et al.
-\cite{beni2012} than former works.
+\cite{beni2012}) than former works.
 
@@
 On the other hand, the MASS seismic microzonation of seismic site effects will improve the estimation of peak ground acceleration.
-The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface, additionally, the geometry of the ground surface also may produce amplification (topographic effects) \cite{aki1993}.
+The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface.
+Additionally, the geometry of the ground surface also may produce amplification (topographic effects) \cite{aki1993}.
 These effects can be important in soft soils close to incised rivers and also in San Salvador volcano, Balsamo ranges and hills.
@@
 \cite{crosta2005} identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
-All these variables can improve the predictive ability of the model and surely the likelihood of landslides.
+All these variables can improve the predictive ability of the model and the likelihood of landslides.
 
 \section{Acknowledgment}   
-The authors are indebted with MARN who provided the data and Geographic Information System software such as ILWIS and ArcGIS\textregistered \  of ESRI.
+The authors are indebted with MARN for providing the data and Geographic Information System software such as ILWIS and ArcGIS\textregistered \  of ESRI.
 

### 2015-09-11 paper.tex

@@
-\documentclass[11pt,twoside]{rmta2010esp}% For English, use rmta2010eng.cls instead of rmta2010esp.cls
+\documentclass[11pt,twoside]{rmta2010eng}% For English, use rmta2010eng.cls instead of rmta2010esp.cls
 %\pagestyle{myheadings} 
@@
 \fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
-\paginas{1}{10} % Numeros de pgina, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
+\paginas{1}{10} % Numeros de pagina, la version final la pone el editor; Page numbers, the Editor puts the final numbers
 \usepackage{amsmath}
@@
 \usepackage{textcomp}
+\usepackage[T1]{fontenc} % Setting Times New Roman font 
+\usepackage{mathptmx}    % Setting Times New Roman font
+
+\usepackage{geometry}
+ \geometry{
+ a4paper,
+ textwidth=15cm, 
+ textheight=21cm
+ }
 
@@
 \affil[4]{Ministry of Environment and Natural Resources of El Salvador.}
+
+\date{}
 
@@
    \centering
-   \includegraphics[scale=0.70]{MASS_mapa_1}
+   \includegraphics[scale=0.70]{MASS_map_1.eps}
    \caption{\small{Location of El Salvador in Central America, map of El Salvador with location of the Metropolitan Area of San Salvador (MASS) and its topography.}}
@@
    \centering
-   \includegraphics[scale=0.73]{MASS_mapa_2}
+   \includegraphics[scale=0.73]{MASS_map_2.eps}
    \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}

### 2015-09-28 paper.tex

@@
 \ref{fig:mass01}).
-El Salvador borders an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
+El Salvador has an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
 Therefore El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
@@
 
-Popular classification models have been used such as logistic regression (\cite{akgun2012}, \cite{gaskill}, and \cite{garcia2008}), neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}, and \cite{Yesilnacar2005251}), and support vector machines (\cite{ballabio2012support} and \cite{tien2012landslide}).
+Popular classification models have been used, such as logistic regression (\cite{akgun2012}, \cite{gaskill}, and \cite{garcia2008}), neural networks (\cite{garcia2010}, \cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}, and \cite{Yesilnacar2005251}), and support vector machines (\cite{ballabio2012support} and \cite{tien2012landslide}).
 
@@
 \label{sec:studyarea}
-MASS is formed by 14 municipalities among them is located San Salvador, the capital of the country.
+MASS is formed by 14 municipalities among them is San Salvador, the capital of the country.
 It has 587 $km^{2}$ and according to the most recent census \cite{minecon} it has 1,566,629 inhabitans with a density of population of 2669 hab/km2.
@@
 
-All rocks exposed in MASS have volcanic origin and consists of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
+All rocks exposed in MASS have volcanic origin and consist of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
 The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in the majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
-These are deposits derived mainly from Ilopango caldera eruptions where they are more than 50 m of thick \cite{schmidt1975}.
+These are deposits derived mainly from Ilopango caldera eruptions with more than 50 m of thick \cite{schmidt1975}.
 Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
@@
 However, all the mentioned fault families appear active.
-Thus the several fault systems have developed at different times, but been repeatedly activated \cite{rymer1987}.
+Thus the several fault systems were formed at different times, but were repeatedly reactivated \cite{rymer1987}.
 Finally there are also several ringlike faults that can be related to subsurface collapse due to volcanic tectonic subsidence \cite{schmidt1975}.
-The Last eruption of San Salvador volcano was in 1917.
+The last eruption of San Salvador volcano was in 1917.
 The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
 However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield \cite{sofield2004}.
-In the steep slopes  San Salvador volcano, especially of Picacho, the highest peak of the volcano, located in the eastern side presents a high lahar hazard that threats MASS \cite{major2004}.
+In the steep slopes of San Salvador volcano, especially at Picacho, the highest peak which is located in the eastern side, there is a high lahar hazard that threatens MASS \cite{major2004}.
 On the other hand one of the most destructive eruptions in the world history was 430 A.D.
-TBJ eruption produced by the Ilopango Caldera.
-According to Dull \cite{dull2004}, that eruption produced total devastation in whole MASS area.
+The TBJ eruption was produced by the Ilopango Caldera and  according to Dull \cite{dull2004}, yielded total devastation in whole MASS area.
 
@@
 
-In the equation (\ref{eq:ann3}) $p_{i}$ is the the predicting probability for a network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
-In the context of the present paper, $p_{i} $ represents the probability of landslide ocurrence.
+In the equation (\ref{eq:ann3}) $p_{i}$ is the output of a neural network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
+In the context of the present study, $p_{i} $ represents the probability of landslide ocurrence.
 
@@
 The method used for estimating the parameters of the model was an Hybrid Method \cite{McNelis2005}.
-Firstly, a heuristic genetic algorithm, using a package developed in the R statistical software \cite{rproject} specifically developed for this purpose, was used to obtain a good estimation of the parameters of the model.
+Firstly, a genetic algorithm was implemented in a package developed in the R statistical software \cite{rproject} to obtain a good estimation of the parameters of the model.
 The R package can be accessed from the following Web address:
@@
 
-Once a good estimate was obtained, this was used as the initial guess value for the conjugate gradient method implemented in the R statistical software (optim function), to obtain a better estimation of the parameters of the model.
+After obtaining a good estimate by genetic algorithms, this was used as initial guess value for the conjugate gradient method implemented in the R statistical software (optim function), to obtain a better estimation of the parameters of the model.
 
@@
 is intrinsic stationarity, which assumes that the process that generated the
-samples is a random function $Z(s)$ composed of a mean and residual \cite{bivand2008applied}:
+samples is a random function $Z(s)$ composed of a mean and residual \cite{bivand2008applied} as follows:
 
@@
 These are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
-Areas with lower probability, but still important, are located in southern and western side of Nejapa Hill, in north-east of the studied area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill, and in general in southern side of MASS.
+Areas with lower probability are located in southern and western side of Nejapa Hill, in north-east of the studied area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill, and in general in southern side of MASS.
 
@@
  \end{center}
-High probability of landslide occurrence in Picacho slope implies very high risk due to the proximity of urban areas and due to the large volume of mobilized materials.
+High probability of landslide occurrence in Picacho slope implies very high risk due to the proximity of urban areas and the large volume of mobilized materials.
 Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $m^{3}$ that can affect large zones of urban areas.
-Southern areas of MASS also have a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
+Southern areas of MASS also have a high risk of landslides that is similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}.
+A similar risk exists in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
 
@@
 \cite{chavez2014a}.
-There are similarities with susceptibility hazard maps at national scale generated through logistic regression method \cite{garcia2008}, through artificial neural network method \cite{garcia2010}, and through Mora-Vahrson method \cite{snet2004}.
+There are similarities with susceptibility hazard maps at national scale generated through logistic regression \cite{garcia2008}, artificial neural network \cite{garcia2010}, and Mora-Vahrson \cite{snet2004}.
 However the high landslide areas are more extended in these national maps than the present study.
@@
 Rock falls were not included in the catalog; these were very common during 2001 earthquakes in El Balsamo Range \cite{jibson}.
-On the other hand, the MASS seismic microzonation of seismic site effects will improve the estimation of peak ground acceleration.
+On the other hand, the seismic microzonation of MASS will improve the estimation of peak ground acceleration.
 The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface.

### 2015-09-29 paper.tex

@@
 Esta contribuci\'{o}n describe la creaci\'{o}n de un modelo de evaluaci\'{o}n de deslizamiento de tierra para el \'{A}rea Metropolitana de San Salvador, departamento de El Salvador.
-El an\'{a}lisis inicio con la obtenci\'{o}n de una foto \'{a}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) en donde 4792 deslizamientos fueron identificados y georeferenciados junto con 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
+El an\'{a}lisis inicio con la obtenci\'{o}n de una foto a\'{e}rea del MARN (Ministerio de Medio Ambiente y Recursos Naturales) en donde 4792 deslizamientos fueron identificados y georeferenciados junto con 7 factores condicionantes incluyendo: geomorfolog\'{i}a, geolog\'{i}a, precipitaciones m\'{a}ximas, aceleraciones s\'{i}smicas, pendiente del terreno, distancia a carretera y falla geol\'{o}gica.
 Redes Neuronales Artificiales (RNA) fueron utilizadas para la evaluaci\'{o}n de la susceptibilidad a deslizamiento de tierra, logrando que m\'{a}s del 80\% de deslizamientos fueran apropiadamente clasificados usando un criterio dentro y fuera de la muestra con la que se estimaron los par\'{a}metros del modelo.
 Regresi\'{o}n Log\'{i}stica fue usada como base de comparaci\'{o}n, obteniendo este modelo un rendimiento inferior.
-Para completar el an\'{a}lisis se realizo la interpolaci\'{o}n de puntos usando el m\'{e}todo kriging proveniente del enfoque geoestad\'{i}stico.
+Para completar el an\'{a}lisis se realiz\'{o} la interpolaci\'{o}n de puntos usando el m\'{e}todo kriging proveniente del enfoque geoestad\'{i}stico.
 Finalmente, los resultados muestran que es posible obtener un mapa de riesgo a deslizamiento de tierra, haciendo uso de una combinaci\'{o}n de RNA y t\'{e}cnicas geoestad\'{i}sticas con lo cual la presente investigaci\'{o}n puede ayudar a la mitigaci\'{o}n de deslizamientos de tierra en El Salvador.
@@
 This contribution describes the creation of a landslide hazard
-assessment model for San Salvador, department in El Salvador.
-The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym) where 4792 landslides were identified and georeferenced
-along with 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, road, and fault distance.
-Artificial Neural Networks (ANN) were for utilized to assess the susceptibility to
+assessment model for San Salvador, a department in El Salvador.
+The analysis started with an aerial photointerpretation from Ministry of Environment and Natural Resources of El Salvador (MARN Spanish acronym), where 4792 landslides were identified and georeferenced
+along with 7 conditioning factors including: geomorphology, geology, rainfall intensity, peak ground acceleration, slope angle, distance to road, and distance to geological fault.
+Artificial Neural Networks (ANN) were utilized to assess the susceptibility to
 landslides, achieving results where more than 80\% of landslide were properly classified using
 in-sample and out of sample criteria. Logistic regression was used as base of
-comparison. Logistic regression obtained a performance lower. To complete the analysis we have
-performed interpolation of the points using kriging method from geostatistical
-approach. Finally, the results show that is possible to derive a landslide hazard map, making use of a combination of ANNs and geostatistical techniques
-wherewith the present study can help landslide mitigation in El Salvador.
+comparison. Logistic regression obtained a lower performance. To complete the analysis we have
+performed interpolation of the points using the kriging method from geostatistical
+approach.
+Finally, the results show that is possible to derive a landslide hazard map, making use of a combination of ANNs and geostatistical techniques, thus the present study can help landslide mitigation in El Salvador.
 \end{abstract}
@@
 El Salvador has an active subduction boundary between Cocos and Caribbean plates located 30 km offshore.
-Therefore El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
-There are two main sources of seismic activity: the upper interface thrust that coincides with the location of the recent volcanoes and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs \cite{dewey}.
-Due this tectonic and volcanic activity El Salvador has rugged relief.
+Therefore, El Salvador is affected with high seismicity and volcanic activity related to this active boundary.
+There are two main sources of seismic activity: the upper interface thrust that coincides with the location of the recent volcanoes, and the Benioff-Wadaty zones of subducted Cocos plate where deeper intraplate earthquakes occurs \cite{dewey}.
+Due to this tectonic and volcanic activity, El Salvador has rugged relief.
 The main ranges cross the country with a rough west-east trend, parallel to the coastline.
@@
 
-Throughout the year the country experiences a tropical climate with two seasons: a dry season (November to April) and wet season (May - October).
+Throughout the year, the country experiences a tropical climate with two seasons: a dry season (November to April) and wet season (May - October).
 The climate of El Salvador is generally warm.
-In the dry season there is very little rainfall but during rainy seasons heavy showers take place.
+In the dry season there is very little rainfall; but during rainy seasons, heavy showers take place.
 Periodically El Salvador is affected by tropical storms and occasionally by hurricanes.
 
-As in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poorly consolidated volcanic materials and the frequent occurrence of extreme precipitation events and intense earthquakes.
-This problem is exacerbated by the extreme deforestation and the consequent high level of rates of erosion.
+As in other parts of Central America, landslides in El Salvador constitute an important natural hazard due to prevailing steep terrain covered with poorly consolidated volcanic materials, and the frequent occurrence of extreme precipitation events and intense earthquakes.
+This problem is exacerbated by the extreme deforestation and the consequent high level rates of erosion.
 Poverty, overpopulation and uncontrolled urbanization characterize the Salvadoran human settlements, which makes El Salvador a country with high landslide risks.
-An example of this high risk was the devastating effect of Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador the Salvadoran capital\cite{evans}.
-A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of El Balsamo range and flushed many houses and produced more than 500 deaths.
-Together with this event also several landslides ocurred along the country, especially in the Metropolitan Area of San Salvador (MASS) \cite{jibson}.
+An example of this high risk was the devastating effect of Las Colinas landslides,  triggered by a major earthquake (Mw 7.6) on January 13th, 2001 in Santa Tecla, a major city located close to San Salvador, the Salvadoran capital\cite{evans}.
+A huge amount of soil mass (about 200,000 $m^{3}$) was thrown off the rim of El Balsamo range, and destroyed many houses causing more than 500 deaths.
+Together with this event, several landslides ocurred along the country, especially in the Metropolitan Area of San Salvador (MASS) \cite{jibson}.
 Another example is the large number of heavy-rainfall induced landslides occurred during Hurricane Mitch on October and November 1998 \cite{crone}.
@@
 Due to the above, it is necessary to implement mechanisms that allow us to quantify the hazard of a given geographic area to landslides.
-Usually this is done with development of susceptibility maps which present in a graphical way the zones more susceptible to landslides and represent a practical tool for urban planning.
-We propose an Artificial Neural Network model (ANN), which is a family of statistical learning models inspired by biological neural networks.
+Usually this is done with development of susceptibility maps, which present in a graphical way the zones more susceptible to landslides, and represent a practical tool for urban planning.
+We propose an Artificial Neural Network model (ANN), which is a family of statistical learning models inspired on biological neural networks.
 The model proposed is used to estimate the susceptibility to landslide.
-From the results obtained by the model, a map was derived using kriging which is a method of interpolation spatial from the geostatistical approach.
+From the results obtained by the model, a map was derived using kriging, which is a method of spatial interpolation from the geostatistical approach.
 
@@
 All rocks exposed in MASS have volcanic origin and consist of intercaled primary and reworked deposits from Late Tertiary to Holocene age \cite{schmidt1975}.
-The younger ones are known as Tierra Blanca pyroclastic ash deposits and forms a relative continuous layer in the majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
+The younger ones are known as Tierra Blanca pyroclastic ash deposits and form a relative continuous layer in the majority of MASS with an average thickness of 4 m \cite{schmidt1975}.
 These are deposits derived mainly from Ilopango caldera eruptions with more than 50 m of thick \cite{schmidt1975}.
-Tierra Blanca soils is highly susceptible to erosion, one of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
+Tierra Blanca soils are highly susceptible to erosion.
+One of the most common dangerous effects of the erosion in this area are landslides during heavy rainfall and earthquake ground shaking \cite{schmidt1975}.
 Ch\'{a}vez et al.
@@
 during rainy seasons).
-This results in high instability susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
+This results in high instability and susceptibility (\cite{chavez2014b} and \cite{rolo2004}).
 Several incised rivers and ravines cross MASS area.
-Due to the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach highs of over 10 m.
+Due to the large erosion rates of the area, natural slopes of these watercourses are often close to vertical and can reach heights of over 10 m.
 Taking into account this property of volcanic soils, usually vertical slopes are cut to urban and road construction.
@@
 Hern\'{a}ndez \cite{hernan2004} carried out a detailed description of this process in TBJ, where these instabilities are very common.
-In the study area fault trends are characterized by steep dip angles (65\textdegree - 90\textdegree).
+In the study area fault trends are characterized by steep angles (65\textdegree - 90\textdegree).
 The main fault system is characterized by an east-west trend; this trend is responsible for the steep northern slope of the El Balsamo Range.
@@
 The last eruption of San Salvador volcano was in 1917.
-The majority of the magma's total volume (97\%) extruded from several vents in the Northwest flank of the volcano, outside of MASS.
-However a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield \cite{sofield2004}.
+The majority of the magma's total volume (97\%) extruded from several vents in the northwest flank of the volcano, outside of MASS.
+However, a fraction of MASS is located under the proximal volcanic hazard zone according to Sofield \cite{sofield2004}.
 In the steep slopes of San Salvador volcano, especially at Picacho, the highest peak which is located in the eastern side, there is a high lahar hazard that threatens MASS \cite{major2004}.
-On the other hand one of the most destructive eruptions in the world history was 430 A.D.
+In addition to that one of the most destructive eruptions in the world history was 430 A.D.
 The TBJ eruption was produced by the Ilopango Caldera and  according to Dull \cite{dull2004}, yielded total devastation in whole MASS area.
@@
 \label{sec:landsinvet}
-The Landslide inventory was developed by Ministry of Environment and Natural Resources (MARN Spanish acronym) and it was conducted in two stages.
-The first was carried out, based on fieldwork after the 2001 earthquakes in El Salvador.
+The Landslide inventory was developed by the Ministry of Environment and Natural Resources (MARN Spanish acronym) and it was conducted in two stages.
+The first was carried out based on fieldwork after the 2001 earthquakes in El Salvador.
 The second stage consisted of a visual inventory of places where landslides were identified through satellite image from IRS-C sensor (Indian) in the same year.
@@
 
-\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from the according digital geological map of El Salvador (scale 1:100,000) \cite{weber}.
+\item {\bf Fault distance:} Distance in kilometers to the nearest fault. This information was obtained from the digital geological map of El Salvador (scale 1:100,000) \cite{weber}.
 
@@
 The following adapted form of the Multilayer Perceptron (MLP) may be used for modeling binary classification problems.
-In the equation (\ref{eq:ann1}) $x_{k,i}$ are the observed values in the $i$th input variables belonging to the $k$th case.
-The expressions $w_{j,k}$ and $\lambda_{j}$ showed in the equations (\ref{eq:ann1}) and (\ref{eq:ann3}) are the parameters of the model.
+In equation (\ref{eq:ann1}) $x_{k,i}$ are the observed values in the $i$th input variables belonging to the $k$th case.
+The expressions $w_{j,k}$ and $\lambda_{j}$ showed in equations (\ref{eq:ann1}) and (\ref{eq:ann3}) are the parameters of the model.
 
@@
 
-In the equation (\ref{eq:ann3}) $p_{i}$ is the output of a neural network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
+In equation (\ref{eq:ann3}) $p_{i}$ is the output of a neural network with $ k^{*} $ input characteristics and $ j^{*} $ neurons.
 In the context of the present study, $p_{i} $ represents the probability of landslide ocurrence.
@@
 
-In the equation (\ref{eq:scaling}) $z$ is the new variable transformed. $ \bar{x} $ and $\sigma_{x}$ are the mean and the standard deviation of the input variable to transform, respectively.
+In equation (\ref{eq:scaling}) $z$ is the new variable transformed. $ \bar{x} $ and $\sigma_{x}$ are the mean and the standard deviation of the input variable to transform, respectively.
 
-The method used for estimating the parameters of the model was an Hybrid Method \cite{McNelis2005}.
+The method used for estimating the parameters of the model was a hybrid method \cite{McNelis2005}.
 Firstly, a genetic algorithm was implemented in a package developed in the R statistical software \cite{rproject} to obtain a good estimation of the parameters of the model.
@@
 
-After obtaining a good estimate by genetic algorithms, this was used as initial guess value for the conjugate gradient method implemented in the R statistical software (optim function), to obtain a better estimation of the parameters of the model.
+After obtaining a good estimate by genetic algorithms, this was used as an initial guess value for the conjugate gradient method implemented in the R statistical software (optim function), to obtain a better estimation of the parameters of the model.
 
@@
 
-To determine the number of neurons in the hidden layer, the method of trial and error was used, starting with few neurons and increasing progressively the number of neurons in the hidden layer.
+To determine the number of neurons in the hidden layer, the method of trial and error was used, starting with few neurons and progressively increasing the number of neurons in the hidden layer.
 Table \ref{annresults}
@@
 The model with 17 neurons in the hidden layer was chosen because it had the best performance in the validation set.
-After that a logistic regression model was fitted as a basis of comparison.
+After that, a logistic regression model was fitted as a basis of comparison.
 Table \ref{logisticresults} shows logistic regression results.
@@
 
-First of all, one thousand fifty georeferenced points with their probability of occurrence calculated using neural network, were selected randomly for the map generation process leaving the others for validation of the kriging model.
+First of all, one thousand and fifty georeferenced points with their probability of occurrence calculated using neural network were selected randomly for the map generation process, leaving the others for validation of the kriging model.
 The Exploratory analysis showed the presence of spatial correlation.
@@
 Using cross-validation methodology, the best model was the exponential, since it had an $ R^{2} = 0.42 $ against $ R^{2} = 0.40 $ and $ R^{2} = 0.39 $ of the models spherical and gaussian, respectively.
-Using exponential model, spatial predictions were calculated on a grid of 1500 $\times$ 1500 and exported to Geotiff raster format.
+Using the exponential model, spatial predictions were calculated on a grid of 1500 $\times$ 1500 and exported to Geotiff raster format.
 Finally, Geographic Information System (ArcGIS\textregistered \  of ESRI) was used to design the final map (Figure \ref{fig:mass02}).
@@
 According to Fig.
-\ref{fig:mass02} higher probability of landslide occurrence are around 0.8.
+\ref{fig:mass02}, higher probability of landslide occurrence are around 0.8.
 These are located in the northern slopes of Balsamo Range (western side of MASS), in the eastern slope of San Salvador volcano and Picacho,  along the extension of Mariona Hills  and in the southeastern side, between Ilopango lake and San Jacinto Hill.
-Areas with lower probability are located in southern and western side of Nejapa Hill, in north-east of the studied area, in northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill, and in general in southern side of MASS.
+Areas with lower probability are located in southern and western side of Nejapa Hill, in the north-east of the studied area, in the northern banks of Ilopango lake, in northeast slope of San Salvador Volcano, in the surrounding areas of San Jacinto Hill, and in general in southern side of MASS.
 
@@
 The study started with the construction of a landslide inventory and analysis of the causal factors related to the occurrences of landslide.
-The problem of modeling landslide is very complex and for this reason the study proved the efficacy of the neural network model with a percentage of correct classification around 80\% against other models such as logistic regression with a percentage of correct classification under 70\%.
+The problem of modeling landslide is very complex, and for this reason the study proved the efficacy of the neural network model with a percentage of correct classification of around 80\% against other models such as logistic regression with a percentage of correct classification under 70\%.
 
@@
 The difficulty of this approach is due to the intensive computation involved in the estimation of a neural network model, which takes between 4 and 10 hours.
-For this reason the statistical significance of the input variables could not be assessed by means of bootstrapping (a statistical resampling technique).
+For this reason, the statistical significance of the input variables could not be assessed by means of bootstrapping (a statistical resampling technique).
 For all of the above, parallel computing must be used rather than serial computing to estimate weights of the neural networks models.
@@
 The results obtained through geostatistical methodology met the assumptions for kriging method application.
-Final map of landslide probability of occurrence (see Fig.
-\ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e.
+A final map of landslide probability of occurrence (see Fig.
+\ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work, which implied an intense geological analysis (i.e.
 MARN inventory of 4792 landslides), together with the use of sophisticated statistical techniques.
-This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on.
+This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation, and so on.
 \begin{center}
@@
 Southern areas of MASS also have a high risk of landslides that is similar to Las Colinas landslide which involved a total volume of around 200,000 $m^{3}$ \cite{evans}.
-A similar risk exists in northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
+A similar risk exists in the northern slope of Balsamo range and San Jacinto Hill, affecting very crowded urban areas.
 
 The present hazard landslide map is consistent with former landslide hazard maps carried out in the region using approaches conceptually different.
-Fern\'{a}ndez-Lavado et al.\cite{fernan2008} presented a landslide hazard GIS map of MASS generated through bivariate statistical method considering several conditioning factors showing similar hazard areas.
+Fern\'{a}ndez-Lavado et al.\cite{fernan2008} presented a landslide hazard GIS map of MASS generated through a bivariate statistical method considering several conditioning factors showing similar hazard areas.
 The only differences are located mainly in the Nejapa Hill and San Jacinto Hill where Fern\'{a}ndez-Lavado et al.
-\cite{fernan2008} identified a slightly higher hazard and the area between San Jacinto Hill and Ilopango Lake where the former study presented a hazard slightly lower.
+\cite{fernan2008} identified a slightly higher hazard, and the area between San Jacinto Hill and Ilopango Lake where the former study presented a hazard slightly lower.
 Since landslides are an erosional phenomenon, the highest probability areas of landslide occurrence coincide with the areas with highest hazard of erosion in the erosion hazard map of MASS proposed by Ch\'{a}vez et al.
@@
 These differences could be explained by the working scale.
-Our map is more detailed because is at regional scale.
 Other possible explanation can be related to the data.
-Present work was built using a more extended landslide catalog and more up-to-date data (e.g.
+This present work was built using a more extended landslide catalog and more up-to-date data (e.g.
 seismic hazard evaluation from Benito et al.
-\cite{beni2012}) than former works.
+\cite{beni2012}) than former works, so that this map is more detailed because it is at regional scale.
 
@@
 On the other hand, the seismic microzonation of MASS will improve the estimation of peak ground acceleration.
-The local geologic conditions are responsible for the modifications (amplification, frequency content and duration) experimented by seismic motions just before reaching the ground surface.
+The local geologic conditions are responsible for the modifications (amplification, frequency content, and duration) experimented by seismic motions just before reaching the ground surface.
 Additionally, the geometry of the ground surface also may produce amplification (topographic effects) \cite{aki1993}.
@@
 Crosta et al.
-\cite{crosta2005} identified an amplification factor of 1.3-1.4 in the Las Colinas failure area (Balsamo Ranges).
+\cite{crosta2005} identified an amplification factor of 1.3-1.4 in Las Colinas failure area (Balsamo Ranges).
 All these variables can improve the predictive ability of the model and the likelihood of landslides.

### 2015-10-22 paper.tex
22 Oct 2015 15:51

@@
 \bibitem{dewey} 
-Dewey J.W. White R.A., Hern\'{a}ndez D.A.
-\newblock Seismicity and tectonics of El Salvador
-\newblock \emph{Chapter 27 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 367-378. (2004)}
+Dewey, J.W.; White, R.A.: Hern\'{a}ndez, D.A. (2004)
+``Seismicity and tectonics of El Salvador",
+{\it Geological Society of America Special Papers} {\bf 375}: 367--378.
 
 \bibitem{weber}  
-Weber H.S., Wiesemann G., Lorenz  W., Schmidt-Thom\'{e} M.
-\newblock Mapa geol\'{o}gico de Republica de El Salvador
-\newblock escala 1 : 100 000 (6 sheets).
-\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany.
-}
-\penalty0 (1978).
+Weber, H.S.; Wiesemann, G.; Lorenz, W.: Schmidt-Thom\'{e}, M. (1978)
+``Mapa geol\'{o}gico de la Republica de El Salvador'',
+Preprint, Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany.
 
 \bibitem{bommer}
-Bommer J.J., Rodriguez C.E.
-\newblock Earthquake-induced landslides in Central Am\'{e}rica
-\newblock \emph{Engineering Geology}.
-(63):\penalty0 1889-220, (2002).
+Bommer, J.J.: Rodriguez, C.E. (2002)
+``Earthquake-induced landslides in Central Am\'{e}rica", 
+{\it Engineering Geology} {\bf 63}(3): 189--220.
 
 \bibitem{evans}  
-Evans S.G. Bent A.L.
-\newblock Las Colinas landslide, Santa Tecla:  A higly destructive flowslide triggered by January 13, 2001, El Salvador earthquake.
-\newblock \emph{Chapter 3 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 25-37. (2004)}
+Evans, S.G: Bent, A.L. (2004) 
+``Las Colinas landslide, Santa Tecla:  A higly destructive flowslide triggered by January 13, 2001, El Salvador earthquake", 
+{\it Geological Society of America Special Papers} {\bf 375}: 25--37.
 
 \bibitem{jibson}  
-Jibson R.W., Crone A.J., Harp E.L., Baum R.L., Major J.J., Pullinguer C.R., Escobar D., Martinez M., Smith M.E. 
-\newblock Landslides triggered by the 13 January and 13 February 2001, earthquakes.
-\newblock \emph{ Chapter 6 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 69-88. (2004)}
+Jibson, R.W.; Crone, A.J.; Harp, E.L.; Baum, R.L.; Major, J.J.; Pullinguer, C.R.; Escobar, D.; Martinez, M: Smith, M.E. (2004) 
+``Landslides triggered by the 13 January and 13 February 2001, earthquakes", 
+{\it Geological Society of America Special Papers} {\bf 375}: 69--88.
 
 \bibitem{crone}  
-Crone A.J., Baum R.L., Lidke D.J., Sather D.N.D., Bradley L.-A., Tarr A.C.
-\newblock Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features
-\newblock \emph{USGS Open File Repord 01-444. (2002)}
+Crone, A.J.; Baum, R.L.; Lidke, D.J.; Sather, D.N.D.; Bradley, L.A.: Tarr, A.C. (2002)
+``Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features'',
+Preprint, USGS Open File Report 01-444.
 
 \bibitem{Carrara1983403} 
-Alberto Carrara.
-\newblock Multivariate models for landslide hazard evaluation.
-\newblock \emph{Journal of the International Association for Mathematical
-  Geology.}, 15\penalty0 (3):\penalty0 403--426, 1983.
-\newblock ISSN 0020-5958.
+Carrara, A. (1983) 
+``Multivariate models for landslide hazard evaluation", 
+{\it Journal of the International Association for Mathematical
+  Geology} {\bf 15}(3): 403--426.
 
 \bibitem{hessd-10-12643-2013}  
-G.~Capparelli and P.~P.~Versace.
-\newblock Landslide susceptibility from mathematical model in sarno area.
-\newblock \emph{Hydrology and Earth System Sciences Discussions}, 10\penalty0
-  (10):\penalty0 12643--12662, 2013.
+Capparelli, G.: Versace, P.P. (2013)
+``Landslide susceptibility from mathematical model in sarno area", 
+{\it Hydrology and Earth System Sciences Discussions} {\bf 10}(10): 12643--12662.
 
 \bibitem{doi:10.1080/19475705.2010.498151}  
-Biswajeet Pradhan, Hyun-Joo Oh, and Manfred Buchroithner.
-\newblock Weights-of-evidence model applied to landslide susceptibility mapping
-  in a tropical hilly area.
-\newblock \emph{Geomatics, Natural Hazards and Risk}, 1\penalty0 (3):\penalty0
-  199--223, 2010.
+Pradhan, B.; Oh, H.: Buchroithner, M. (2010)
+``Weights-of-evidence model applied to landslide susceptibility mapping
+  in a tropical hilly area", 
+{\it Geomatics, Natural Hazards and Risk} {\bf 1}(3): 199--223.
 
 \bibitem{Neu2012511} 
-Bettina Neuh\"auser, Bodo Damm, and Birgit Terhorst.
-\newblock Gis-based assessment of landslide susceptibility on the base of the
-  weights-of-evidence model.
-\newblock \emph{Landslides}, 9\penalty0 (4):\penalty0 511--528, 2012.
-\newblock ISSN 1612-510X.
+Neuh\"auser, B.; Damm, B.: Terhorst, B. (2012)
+``Gis-based assessment of landslide susceptibility on the base of the
+  weights-of-evidence model", 
+{\it Landslides} {\bf 9}(4): 511--528.
 
 \bibitem{Bern198839} 
-Campbell R.H. Brookshire~D.S. Bernknopf, R.L. and C.D Shapiro.
-\newblock A probabilistic approach to landslide hazard mapping in cincinnati,
-  ohio, with application for economic evaluation.
-\newblock \emph{Bulletin of the Association of Engineering Geologists},
-  XXV\penalty0 (1):\penalty0 39--56, 1988.
+Campbell, R.H.; Brookshire, D.S.; Bernknopf, R.L.: Shapiro, C.D. (1988)
+``A probabilistic approach to landslide hazard mapping in cincinnati,
+  ohio, with application for economic evaluation", 
+{\it Bulletin of the Association of Engineering Geologists} {\bf 25}(1): 39--56.
 
 \bibitem{Chung2003451}  
-Chang-JoF. Chung and AndreaG. Fabbri.
-\newblock Validation of spatial prediction models for landslide hazard mapping.
-\newblock \emph{Natural Hazards}, 30\penalty0 (3):\penalty0 451--472, 2003.
-\newblock ISSN 0921-030X.
-\newblock doi:{10.1023/B:NHAZ.0000007172.62651.2b}.
+Chung, C.J.F.: Fabbri, A. G. (2003).
+``Validation of spatial prediction models for landslide hazard mapping", 
+{\it Natural Hazards} {\bf 30}(3): 451--472.
 
 \bibitem{doi:10.1080/01431160310001618734} 
-S.~Lee, J.~Choi, and K.~Min.
-\newblock Probabilistic landslide hazard mapping using gis and remote sensing
-  data at boun, korea.
-\newblock \emph{International Journal of Remote Sensing}, 25\penalty0
-  (11):\penalty0 2037--2052, 2004.
+Lee, S.; Choi, J.: Min, K. (2004)
+``Probabilistic landslide hazard mapping using gis and remote sensing
+  data at boun, korea", 
+{\it International Journal of Remote Sensing} {\bf 25}(11): 2037--2052.
 
 \bibitem{akgun2012}  
-Akgun, Aykut
-\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
-\newblock \emph{Landslides},
-  (11):\penalty0 9, 1, 93--106, 2012.
-\newblock Springer.
+Akgun, A. (2012) 
+``A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey", 
+{\it Landslides} {\bf 9}(1): 93--106.
 
 \bibitem{gaskill} 
-Gaskill, Jacob and Zuber, Brian and Nordman, Erik
-\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
-\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.
+Gaskill, J.; Zuber, B.: Nordman, E. (2015)
+``Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression'', 
+Preprint, The 2015 IMAGIN Award, Michigan United States.
 
 \bibitem{garcia2008} 
-Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A., Benito B., D\'{i}az M.
-\newblock  Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression.
-\newblock \emph{Geomorphology}
-\penalty0 95, 172-191, 2008.
+Garc\'{i}a-Rodr\'{i}guez, M.J.; Malpica, J.A.; Benito, B.: D\'{i}az, M. (2008) 
+``Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression", 
+{\it Geomorphology} {\bf 95}(3): 172-191.
 
 \bibitem{garcia2010} 
-Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A.
-\newblock Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model.
-\newblock \emph{Nat. Hazards Earth Syst. Sci.}
-\penalty0 10, 1307–1315, 2010. 
-\newblock doi:10.5194/nhess-10-1307-2010.
+Garc\'{i}a-Rodr\'{i}guez, M.J.: Malpica, J.A. (2010)
+``Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model", 
+{\it Natural Hazards and Earth System Science} {\bf 10}(6): 1307–1315.
 
 \bibitem{Melchiorre2011410}  
-C.~Melchiorre, E.A.~Castellanos Abella, C.J. van Westen, and M.~Matteucci.
-\newblock Evaluation of prediction capability, robustness, and sensitivity in
-  non-linear landslide susceptibility models, guant\'{a}namo, cuba.
-\newblock \emph{Computers {\&} Geosciences}, 37\penalty0 (4):\penalty0 410 --
-  425, 2011.
-\newblock ISSN 0098-3004.
+Melchiorre, C.; Abella, E. C.; van Westen, C. J.: Matteucci, M. (2011)
+``Evaluation of prediction capability, robustness, and sensitivity in
+  non-linear landslide susceptibility models, guant\'{a}namo, cuba", 
+{\it Computers {\&} Geosciences} {\bf 37}(4): 410--425.
 
 \bibitem{Zeng2001374}  
-Xu~Zeng-wang.
-\newblock Gis and ann model for landslide susceptibility mapping.
-\newblock \emph{Journal of Geographical Sciences}, 11\penalty0 (3):\penalty0
-  374--381, 2001.
-\newblock ISSN 1009-637X.
-\newblock doi:{10.1007/BF02892323}.
+Zeng-wang, X. U. (2001).
+``Gis and ann model for landslide susceptibility mapping", 
+{\it Journal of Geographical Sciences} {\bf 11}(3): 374--381.
 
 \bibitem{Ermini2005327} 
-Artificial neural networks applied to landslide susceptibility assessment.
-\newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.
-\newblock ISSN 0169-555X
-\newblock doi:10.1016/j.geomorph.2004.09.025.
+Ermini, L.; Catani, F.: Casagli, N. (2005). 
+``Artificial neural networks applied to landslide susceptibility assessment", 
+{\it Geomorphology} {\bf 66}(1): 327--343.
 
 \bibitem{Yesilnacar2005251} 
-E. Yesilnacar and T. Topal.
-\newblock Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey).
-\newblock \emph{Engineering Geology}, 79\penalty0
-  (11):\penalty0 251-266, 2005.
-\newblock ISSN 0013-7952,
-\newblock doi:10.1080/01431160310001618734.
+Yesilnacar, E.: Topal, T. (2005)
+``Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey)", 
+{\it Engineering Geology} {\bf 79}(3): 251-266.
 
 \bibitem{ballabio2012support}  
-Ballabio, Cristiano and Sterlacchini, Simone
-\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
-\newblock \emph{Mathematical geosciences},
-  (11):\penalty0 1, 47--70, 2012.
-\newblock Springer.
+Ballabio, C.: Sterlacchini, S. (2012) 
+``Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy", 
+{\it Mathematical geosciences} {\bf 44}(1): 47--70.
 
 \bibitem{tien2012landslide} 
-Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
-\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
-\newblock \emph{Mathematical Problems in Engineering},
-  (11):\penalty0 2012, 2012.
-\newblock Hindawi Publishing Corporation.
+Tien Bui, D.; Pradhan, B.; Lofman, O.: Revhaug, I. (2012)
+``Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models", 
+{\it Mathematical Problems in Engineering} {\bf 2012}.
 
 \bibitem{van2006landslide}  
-Van Westen, CJ and Van Asch, Th WJ and Soeters, R
-\newblock Landslide hazard and risk zonation why is it still so difficult?
-\newblock \emph{Bulletin of Engineering geology and the Environment}.
-(65):\penalty0 2, 167--184, 2006
-\newblock Springer.
+Van Westen, C. J.; Van Asch, T. W.: Soeters, R. (2006).
+``Landslide hazard and risk zonation why is it still so difficult?", 
+{\it Bulletin of Engineering geology and the Environment} {\bf 65}(2): 167--184.
 
 \bibitem{minecon}  
-Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos
-\newblock VI Censo de Poblaci\'{o}n y V de Vivienda
-\newblock \emph{2007-2008}.
-\penalty0 Available from http://goo.gl/yvjzPy
+Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos. (2013) 
+``VI Censo de Poblaci\'{o}n y V de Vivienda'',
+in:\\ {\tt http://goo.gl/yvjzPy},\\
+consulted 23-Dec-2013, 2:30 p.m.
 
 \bibitem{schmidt1975} 
-Schmidt-Thom\'{e} M.
-\newblock The geology in San Salvador area (El Salvador, Central America), a basis for city development and planning.
-\newblock \emph{Geol. Jb.}.
-\penalty0 13, 207-228, 1975.
+Schmidt-Thom\'{e} M. (1975)
+``The geology in the San Salvador area (El Salvador, Central America), a basis for city development and planning'',
+Preprint,  Schweizerbart'sche Verlagsbuchhandlung.
 
 \bibitem{chavez2014a} 
-Ch\'{a}vez J.A., Sebesta J., Kopecky L., L\'{o}pez R.
-\newblock Application of Geomorphologic Knowledge for Erosion Hazard Mapping
-\newblock \emph{Natural Hazards}.
-\penalty0 71,1323–1354, 2014.
-\newblock doi:10.1007/s11069-013-0948-8.
+Ch\'{a}vez, J.A.; Sebesta, J.; Kopecky, L.: L\'{o}pez, R. (2014)
+``Application of Geomorphologic Knowledge for Erosion Hazard Mapping", 
+{\it Natural Hazards} {\bf 71}(3): 1323–1354.
 
 \bibitem{hernan2004} 
-Hern\'{a}ndez W.E.
-\newblock Caracter\'{i}sticas Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
-\newblock MSc Thesis. Universidad Polit\'{e}cnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
-\penalty0 2004
+Hern\'{a}ndez, W.E. (2004)
+{\it Caracter\'{i}sticas Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador}.
+MSc Thesis. Universidad Polit\'{e}cnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
 
 \bibitem{chavez2014b} 
-Ch\'{a}vez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). 
-\newblock Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''.
-\newblock \emph{Ingenier\'{i}a.}
-\penalty0  24 (2).53-78.
-\newblock  ISSN: 2215-2652.
+Ch\'{a}vez J.A.; Landaverde J.M.; Ayala O.E.: Mendoza L.E. (2014). 
+``Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''", 
+{\it Ingenier\'{i}a} {\bf 24}(2): 53-78.
 
 \bibitem{rolo2004} 
-Rolo R., Bommer J.J., Houghton B.F., Vallance J.W., Berdousis P., Mavrommati C., Morphy W.
-\newblock Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits.
-\newblock \emph{Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
-\penalty0  55-67, 2004.
+Rolo, R.; Bommer, J.J.; Houghton, B.F.; Vallance, J.W.; Berdousis, P.; Mavrommati, C.: Morphy, W. (2004)
+``Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits", 
+{\it Geological Society of America Special Papers} {\bf 375}: 55--68.
 
 \bibitem{rymer1987}  
-Rymer M.J. 
-\newblock The San Salvador Earthquake of October 10, 1986.
-\newblock \emph{Geologic Aspects Earthquake Spectra.}
-\penalty0 3(3), 435-463, 1987.
+Rymer, M.J. (1987) 
+``The San Salvador Earthquake of October 10, 1986-Geologic Aspects", 
+{\it Earthquake Spectra} {\bf 3}(3): 435-463.
 
 \bibitem{dull2004}  
-Dull R.A.
-\newblock Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption.
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
-\penalty0 237-244., 2004.
+Dull, R.A. (2004)
+``Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption", 
+{\it Geological Society of America Special Papers} {\bf 375}: 237--244.
 
 \bibitem{major2004} 
-Major J.J. Chilling S.P., Pullinguer C.R., Escobar C.D.
-\newblock Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador.
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
-\penalty0 89-108, 2004.
+Major, J.J.; Chilling, S.P.; Pullinguer, C.R.: Escobar, C.D. (2004)
+``Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador", 
+{\it Geological Society of America Special Papers} {\bf 375}: 89--108.
 
 \bibitem{sofield2004}  
-Sofield D.
-\newblock Eruptive history and volcanic hazards of Volcan San Salvador. 
-\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
-\penalty0 147-158, 2004.
+Sofield, D. (2004)
+``Eruptive history and volcanic hazards of Volcan San Salvador", 
+{\it Geological Society of America Special Papers} {\bf 375}: 147--158.
 
 \bibitem{beni2012}
-Benito M.B., Lindholm C., Camacho E., Climent \'{A}., Marroqu\'{i}n G., Molina E.,Rojas W., Escobar J.J., Talavera E., Alvarado G.E. and Torres Y.
-\newblock A New Evaluation of Seismic Hazard for the Central America Region. 
-\newblock \emph{Bulletin of the Seismological Society of America}
-\penalty0 102 (2), 504-523. 2012.
-\newblock  doi: 10.788/0120110015
+Benito, M.B.; Lindholm, C.; Camacho, E.; Climent, \'{A}.; Marroqu\'{i}n, G.; Molina, E.; Rojas, W.; Escobar, J.J.; Talavera, E.; Alvarado, G.E.: Torres, Y. (2012)
+``A New Evaluation of Seismic Hazard for the Central America Region", 
+{\it Bulletin of the Seismological Society of America} {\bf 102}(2): 504--523.
 
 \bibitem{FAQANN}
-Warren S. Sarle
-\newblock  [cited 2014 January 10]. Available from http://goo.gl/k8fKhM
+Warren, S. (2002) 
+``Neural Network FAQ'',
+in:\\ {\tt ftp://ftp.sas.com/pub/neural/FAQ.html},\\
+consulted 10-Jan-2014, 10:30 a.m.
 
 \bibitem{McNelis2005}
-Paul D. McNelis
-\newblock Estimation of a Network with Evolutionary Computation
-\newblock \emph{Academic Press},
-  (11):\penalty0 59-84, 2005.
-\newblock ISBN 9780124859678,
-\newblock doi:10.1016/B978-012485967-8.50003-8.
+McNelis, P.D. (2005)
+{\it Estimation of a Network with Evolutionary Computation}. 
+Academic Press.
 
 \bibitem{rproject}
-R Core Team
-\newblock R: A Language and Environment for Statistical Computing.
-\newblock \emph{R Foundation for Statistical Computing.}
-\penalty0 Vienna, Austria, 2014.
+R Core Team. (2014)
+{\it R: A Language and Environment for Statistical Computing}. 
+Vienna: R Foundation for Statistical Computing.
 
 \bibitem{bivand2008applied}
-Bivand, Roger S and Pebesma, Edzer J and G{\'o}mez-Rubio, Virgilio and Pebesma, Edzer Jan
-\newblock Applied spatial data analysis with R
-\newblock \emph{volume 747248717}
-\penalty0 Springer, 2014.
+Bivand, R.S.; Pebesma, E.J.; Gomez-Rubio, V.: Pebesma, E.J. (2008)
+{\it Applied spatial data analysis with R}. 
+New York: Springer.
 
 \bibitem{nicolas2015}
-Nicolas Christou.
-\newblock Ordinary kriging in terms of the covariance function
-\newblock \emph{University of California, Los Angeles}
-\penalty0 [cited 2015 June 04]. Available from http://goo.gl/0J1RkO
+Christou, N. (2013)
+``Ordinary kriging in terms of the covariance function'',
+in:\\ {\tt http://goo.gl/0J1RkO},\\
+consulted 23-Jun-2013, 5:30 p.m.
 
 \bibitem{fernan2008}
-Fernandez-Lavado C., Sanchez A., Amenos M., Barrio J.
-\newblock Caracterizaci\'{o}n de la susceptibilidad y de la amenaza por movimientos de ladera del \'{A}rea Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet).
-\newblock \emph{Project IPGARAMSS framework. Ge\'{o}logos del Mundo. San Salvador, El Salvador.}
-\penalty0 2008.
+Fernandez-Lavado, C.; Sanchez, A.; Amenos, M.: Barrio, J. (2008)
+``Caracterizaci\'{o}n de la susceptibilidad y de la amenaza por movimientos de ladera del \'{A}rea Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet)'',
+Preprint, Project IPGARAMSS framework. Ge\'{o}logos del Mundo. San Salvador, El Salvador.
 
 \bibitem{snet2004}
-SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales
-\newblock Memoria T\'{e}cnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador.
-\newblock \emph{Ministerio de Ambiente y Recursos Naturales}
-\penalty0 [cited 2015 June 04]. Map available from http://www.snet.gob.sv/ver/geologia/susceptibilidad+actual/
+SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales. (2013) 
+``Memoria T\'{e}cnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador'',
+in:\\ {\tt http://www.snet.gob.sv/ver/geologia/susceptibilidad+actual/},\\
+consulted 12-Sep-2013, 2:30 p.m.
 
 \bibitem{aki1993}
-Aki, K. 
-\newblock Local site effects on weak and strong ground motion. In F. Lund (ed.) New Horizons in Strong Motion: Seismic Studies and Engineering Practice.
-\newblock \emph{Tectonophysics}
-\penalty0 218, 93-111, 1993.
+Aki, K. (1993) 
+``Local site effects on weak and strong ground motion. In F. Lund (ed.) New Horizons in Strong Motion: Seismic Studies and Engineering Practice", 
+{\it Tectonophysics} {\bf 218}(1): 93--111.
 
 \bibitem{crosta2005}
-Crosta G.B., Imposimato S., Rodderman, Chiesa S.m, Moia F. 
-\newblock Small fast-moving flow-like landslides in volcanic deposits: The 2001 Las Colinas Landslide (El Salvador). 
-\newblock \emph{Engineering Geology.}
-\penalty0 79, 185-214, 2005.
+Crosta, G. B.; Imposimato, S.; Roddeman, D.; Chiesa, S.: Moia, F. (2005)
+``Small fast-moving flow-like landslides in volcanic deposits: the 2001 Las Colinas Landslide (El Salvador)", 
+{\it Engineering geology} {\bf 79}(3): 185--214.
 

### 2015-11-17 paper.tex

@@
 The main fault system is characterized by an east-west trend; this trend is responsible for the steep northern slope of the El Balsamo Range.
-The secondary systems are with north, northwest and northeast trends offset the main fault system and are more active in the present tectonic setting \cite{schmidt1975}.
+The other fault systems have north, northwest, and northeast trends and are more active in the present tectonic setting \cite{schmidt1975}.
 However, all the mentioned fault families appear active.
